### 2024-03-16 paper.qmd
init

---
title: "BEE Paper"
date: 2024-03-16
author:
  - name: Konrad Kopp
    email: konrad.kopp@stcatz.ox.ac.uk
    affiliation: University of Oxford
abstract: > 
  The abstract is currently pending
keywords:
  - Behavioral Economics
---

# Introduction

# Literature Review

# Data 
```{r}

# Define the cars vector with 5 values
cars <- c(1, 3, 6, 4, 9)

# Graph the cars vector with all defaults
plot(cars)
```

# Methodology

# Results

# Conclusion

# Appendix {.appendix}

## Experiment Instructions

todo

### 2024-03-16 data-analysis/model.R
init data analysis

@@ -1,0 +1,13 @@
+# Load the experiment data
+experiment_data <- read.csv("virtual-currencies-paper/data/experiment_data.csv")
+
+experiment_data$Q5a_in_pounds <- experiment_data$Q5a * 5
+experiment_data$Q5b_in_pounds <- experiment_data$Q5b / 5
+
+# Plot boxplots for columns Q5a and Q5b
+boxplot(experiment_data$Q5a_in_pounds, experiment_data$Q5b_in_pounds,
+    main = "Boxplot of Q5a and Q5b (in Pounds)",
+    names = c("Q5a", "Q5b"),
+    xlab = "Variables",
+    ylab = "Values"
+)

### 2024-04-07 data-analysis/model.R
add initial data analysis

@@ -1,13 +1,43 @@
 # Load the experiment data
 experiment_data <- read.csv("virtual-currencies-paper/data/experiment_data.csv")
 
-experiment_data$Q5a_in_pounds <- experiment_data$Q5a * 5
-experiment_data$Q5b_in_pounds <- experiment_data$Q5b / 5
+# Rename the columns to more meaningful names
+colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <- "group1_bid"
+colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <- "group2_bid"
+colnames(experiment_data)[which(names(experiment_data) == "Q6")] <- "lived_abroad"
+colnames(experiment_data)[which(names(experiment_data) == "Q7")] <- "travel_frequency"
+colnames(experiment_data)[which(names(experiment_data) == "Q8")] <- "expenditure"
 
-# Plot boxplots for columns Q5a and Q5b
-boxplot(experiment_data$Q5a_in_pounds, experiment_data$Q5b_in_pounds,
-    main = "Boxplot of Q5a and Q5b (in Pounds)",
-    names = c("Q5a", "Q5b"),
+View(experiment_data)
+
+# Convert the values of the bid columns to pounds
+experiment_data$group1_bid_in_pounds <- experiment_data$group1_bid * 5
+experiment_data$group2_bid_in_pounds <- experiment_data$group2_bid / 5
+
+# Summary statistics for the bid columns
+summary(experiment_data$group1_bid_in_pounds)
+sd(experiment_data$group1_bid_in_pounds, na.rm = TRUE)
+
+summary(experiment_data$group2_bid_in_pounds)
+sd(experiment_data$group2_bid_in_pounds, na.rm = TRUE)
+
+# Perform a t-test to compare the means of the two groups
+t.test(experiment_data$group1_bid_in_pounds, experiment_data$group2_bid_in_pounds)
+
+# Conduct a regression analysis to examine the relationship between the bid amounts and the demographic variables
+model_group1 <- lm(group1_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure, data = experiment_data)
+summary(model_group1)
+
+model_group2 <- lm(group2_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure, data = experiment_data)
+summary(model_group2)
+
+# Plot a boxplot for columns the bid columns
[…]

### 2024-04-07 paper.qmd
add spellcheck

@@
 keywords:
-  - Behavioral Economics
+  - Behavioural Economics
 ---

### 2024-04-07 paper.qmd
formatting

@@
 ```{r}
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data.csv")
 
-# Define the cars vector with 5 values
-cars <- c(1, 3, 6, 4, 9)
+# Rename the columns to more meaningful names
+colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <-
+    "group1_bid"
+colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <-
+    "group2_bid"
+colnames(experiment_data)[which(names(experiment_data) == "Q6")] <-
+    "lived_abroad"
+colnames(experiment_data)[which(names(experiment_data) == "Q7")] <-
+    "travel_frequency"
+colnames(experiment_data)[which(names(experiment_data) == "Q8")] <-
+    "expenditure"
 
-# Graph the cars vector with all defaults
-plot(cars)
+# Convert the values of the bid columns to pounds
+experiment_data$group1_bid_in_pounds <-
+    experiment_data$group1_bid * 5
+experiment_data$group2_bid_in_pounds <-
+    experiment_data$group2_bid / 5
+
+# Plot a boxplot for columns the bid columns
+boxplot(
+    experiment_data$group1_bid_in_pounds,
+    experiment_data$group2_bid_in_pounds,
+    main = "Boxplot of group 1 and group 2 bids (in Pounds)",
+    names = c("Group 1", "Group 2"),
+    xlab = "Variables",
+    ylab = "Values"
+)
 ```

### 2024-04-07 data-analysis/model.R

@@ -1,18 +1,24 @@
 # Load the experiment data
-experiment_data <- read.csv("virtual-currencies-paper/data/experiment_data.csv")
+experiment_data <-
+  read.csv("virtual-currencies-paper/data/experiment_data.csv")
 
 # Rename the columns to more meaningful names
-colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <- "group1_bid"
-colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <- "group2_bid"
-colnames(experiment_data)[which(names(experiment_data) == "Q6")] <- "lived_abroad"
-colnames(experiment_data)[which(names(experiment_data) == "Q7")] <- "travel_frequency"
-colnames(experiment_data)[which(names(experiment_data) == "Q8")] <- "expenditure"
-
-View(experiment_data)
+colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <-
+  "group1_bid"
+colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <-
+  "group2_bid"
+colnames(experiment_data)[which(names(experiment_data) == "Q6")] <-
+  "lived_abroad"
+colnames(experiment_data)[which(names(experiment_data) == "Q7")] <-
+  "travel_frequency"
+colnames(experiment_data)[which(names(experiment_data) == "Q8")] <-
+  "expenditure"
 
 # Convert the values of the bid columns to pounds
-experiment_data$group1_bid_in_pounds <- experiment_data$group1_bid * 5
-experiment_data$group2_bid_in_pounds <- experiment_data$group2_bid / 5
+experiment_data$group1_bid_in_pounds <-
+  experiment_data$group1_bid * 5
+experiment_data$group2_bid_in_pounds <-
+  experiment_data$group2_bid / 5
 
 # Summary statistics for the bid columns
 summary(experiment_data$group1_bid_in_pounds)
@@ -22,21 +28,29 @@ summary(experiment_data$group2_bid_in_pounds)
 sd(experiment_data$group2_bid_in_pounds, na.rm = TRUE)
 
 # Perform a t-test to compare the means of the two groups
-t.test(experiment_data$group1_bid_in_pounds, experiment_data$group2_bid_in_pounds)
+t.test(experiment_data$group1_bid_in_pounds,
+       experiment_data$group2_bid_in_pounds)
 
-# Conduct a regression analysis to examine the relationship between the bid amounts and the demographic variables
[…]

### 2024-04-13 data-analysis/model.R
finalise data analysis

@@ -1,3 +1,7 @@
+# Load the required libraries
+library(pwr)
+library(lsr)
+
 # Load the experiment data
 experiment_data <-
   read.csv("virtual-currencies-paper/data/experiment_data.csv")
@@ -27,23 +31,7 @@ sd(experiment_data$group1_bid_in_pounds, na.rm = TRUE)
 summary(experiment_data$group2_bid_in_pounds)
 sd(experiment_data$group2_bid_in_pounds, na.rm = TRUE)
 
-# Perform a t-test to compare the means of the two groups
-t.test(experiment_data$group1_bid_in_pounds,
-       experiment_data$group2_bid_in_pounds)
-
-# Conduct a regression analysis to examine the relationship between 
-# the bid amounts and the demographic variables
-model_group1 <-
-  lm(group1_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
-     data = experiment_data)
-summary(model_group1)
-
-model_group2 <-
-  lm(group2_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
-     data = experiment_data)
-summary(model_group2)
-
-# Plot a boxplot for columns the bid columns
+# Plot a boxplot for the bid columns
 boxplot(
   experiment_data$group1_bid_in_pounds,
   experiment_data$group2_bid_in_pounds,
@@ -53,5 +41,31 @@ boxplot(
   ylab = "Values"
 )
 
-# Robustness checks
-# TODO
+# Perform a t-test to compare the means of the two groups
+t.test(
+  experiment_data$group1_bid_in_pounds,
+  experiment_data$group2_bid_in_pounds
+)
+
+# Conduct a regression analysis to examine the relationship between
+# the bid amounts and the demographic variables
+model_group1 <-
+  lm(group1_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+    data = experiment_data
+  )
+summary(model_group1)
+
+model_group2 <-
+  lm(group2_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+    data = experiment_data
+  )
+summary(model_group2)
+
+# Conduct a power analysis to determine the power of the t test and
+# sample size required for a power of 0.8 (80%)
+effect_size <- cohensD(
+  experiment_data$group1_bid_in_pounds,
+  experiment_data$group2_bid_in_pounds
+)
[…]

### 2024-04-13 paper.qmd
outline of paper

@@
   - Behavioural Economics
+  - Face Value Effect
+  - Consumer Choice Theory
 ---
 
-# Introduction
+Introduction
 
-# Literature Review
+# Literature Review -- rename?
 
-# Data 
+face value paper: 
+- Arguably, the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency.
+Theoretically, therefore, the strength and persistence of the face value effect is likely to depend on the extent to which an individual has the opportunity or the time available to process exchange rate information and/or has experience in using a particular foreign currency.
+The last two studies show that the time available to process exchange information (study 5) and experience with a foreign currency, both measured (study 5) and manipulated (study 6), moderate the face value effect.
+- The asymmetric effect may be due to the differential difficulty in using whole numbers versus fractions or multiplying versus dividing
+- First, the reliance on face value may be a function of the ease with which the foreign money can be converted, implying that as r approaches a round number, a is likely to reduce.
+Second, a may vary with the absolute deviation of r from one, implying that as r deviates from one, the need to adjust increases implying a nonlinear relationship.
+From an effort-accuracy perspective, when r is close to one, it may not be worthwhile to adjust.
+Further, note that for currencies that are multiples of the home currency, r can range from one to , whereas for fractional currencies, r is bounded between zero and one.
+The lower bound may account for the lower likelihood of adjustment for a currency that is a fraction of the homecurrency.
+Future research should examine the asymmetric and nonlinear nature of this effect
+- Despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
+For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation.
+
+fang paper:
+- did not implement bdm because infeasible
+
+perceived value of money:
+- In particular, we extend previous research in several important ways.
+We propose a conceptualization that not only considers the nominal prices faced by consumers but also takes salient reference values into account, such as the budget consumers have available to make a purchase or the price of competing purchase options.
+By including budget constraints and reference standards, our conceptualization links nominal valuations to standard economic as well as psychophysical theory.
+We propose and test two alternative computational mechanisms by which consumers might evaluate prices in different currencies relative to such ,reference standards.
+Specifically, do consumers use the difference between reference values and prices to derive their evaluations or the ratio of the two?
+
+build on perceived value of money paper; where to extend:
+- incentive compatible mechanism
+- control for familiarity of currencies (easy on mind, easy on wallet)
+- examine the dispute between it and face value Paper
+- expand to virtual currencies (fang)
+
+# Model
+
+ratio (traditional) model:
+- formulate valuation of good as ratio to budget in home currency
+- convert valuation of good into bid currency
+
+assumptions:
+- is it rational if we always assume that the conversion will be accurate? what if this causes more mental effort than reward?
+- people can easily do those calculations in their head
+
+if we agree with assumptions, then there should be (small) differences but not systematic ones (see methodology)
+
+face value model:
+- formulate valuation of good in home currency
+- convert valuation of good into bid currency but weighted by nominal value of foreign currency
+
+$$V = Vn$$
+$$V = Vr$$
+$$V = aVn + (1 - a)Vr$$
+
+if this is the right model, then we should see group 1 overspend and group 2 underspend
+
+value of money model:
+- difference in budget and item price in foreign currency
+- insufficiently adjust for exchange rate, leading to biased assesment of real value of transaction
+
+if this is the right model, then we should see group 1 underspend and group 2 overspend
+
+# Method
+
+- explain sample
+- explain experiment and choices made
+- shortcomings/downsides:
+ - bdm was done incorrectly: does this have an impact?
+ - low sample size: could this be an issue? (power analysis)
+
+# Results and Discussion
+
+results:
+data analysis:
+- normalise bids to pounds
+- summary statistics and boxplot
+- t-test to compare means between groups
+- conduct regression to investigate relationship between bids and demographic vars
+
+outline the results: 
+- group one bid lower on average; statistically significant (but only power of 20%)
+- no statistically significant relationships between domographic vars and bids found
+
+how to explain results: value of money paper suggests this, confirms this research, face value effect stipulates differernt result but seems to be incorrect here
+
+explanations for effect:
+- model 3 is the correct one
+- anchoring: higher endowment anchors at higher endowment value (perceived value of money paper: When provided with a budget, consumers might anchor on the nominal value of that budget when evaluating transactions in foreign currencies.
+But this would not have predicted the biased evaluations in our follow-up study since the nominal budget was the same (i.e., quoted in US$) across all numerosity conditions)
+- people are worse at dividing than multiplying (or put in less effort) (or reverse)
+- people prefer using whole numbers over fractions - is this rational? mental ease?
+- sample size too small - power analysis
+
+conclusion: agree with model 3 and get rid of some of its shortcomings:
+- incentive compatible mechanism
+- control for familiarity of currencies (easy on mind, easy on wallet)
+- examine the dispute between it and face value Paper
+- expand to virtual currencies (fang)
+
+## Data 
 ```{r}
@@
 
-# Methodology
+# General Discussion
 
-# Results
-
-# Conclusion
+## Limitations, Theoretical Implications and Future Research
 
@@
 
-todo
+## Source Code

### 2024-04-13 paper.qmd
formatting
add initial references

@@
 
-Introduction
+# Introduction
 
-# Literature Review -- rename?
+Intro
 
-face value paper: 
+Literature review
+
+face value paper [@Raghubir2002]: 
 - Arguably, the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency.
@@
 
-fang paper:
+fang paper [@Fang2019]:
 - did not implement bdm because infeasible
 
-perceived value of money:
+perceived value of money [@Wertenbroch2007]:
 - In particular, we extend previous research in several important ways.
@@
 - incentive compatible mechanism
-- control for familiarity of currencies (easy on mind, easy on wallet)
+- control for familiarity of currencies (easy on mind, easy on wallet) [@Alter2008]
 - examine the dispute between it and face value Paper
@@
 
+# References
+::: {#refs}
+:::
+
 # Appendix {.appendix}

### 2024-04-14 paper.qmd
method and data analysis sections

@@
 
-- explain sample
-- explain experiment and choices made
-- shortcomings/downsides:
- - bdm was done incorrectly: does this have an impact?
- - low sample size: could this be an issue? (power analysis)
+There were 41 participants of the study, most of them current undergraduate students at the University of Oxford, but some participants were also recent graduates and postgraduate students.
+The study took place online, using Qualtrics, and students were incentivised to participate by taking part in a lottery, which will be explained in further detail below.
 
-# Results and Discussion
+## Study
 
-results:
-data analysis:
-- normalise bids to pounds
-- summary statistics and boxplot
-- t-test to compare means between groups
-- conduct regression to investigate relationship between bids and demographic vars
+The study itself was split into four parts: Consent Form, Introduction, Auction and Follow-Up Questions.
+The entire experiment instructions can be found in the [Experiment Instructions](./paper.qmd#experiment-instructions) section of the Appendix.
+The first section asked participants to read through and sign the consent form in order to ensure that they were informed about the study and what data would be collected.
+In the introductory section, the BDM mechanism was explained to participants and they were asked to complete four question that tested their understanding of the mechanism.
+The aim of this section was to ensure that participants properly understood how the mechanism worked in order to elicit their real WTP during the main part of the study.
+
+The auction was the main part of the study, with the aim of eliciting the participants' WTP on a specific item and comparing these across different currencies used.
+In this section, participants were randomly split into two groups with almost-identical instructions.
+The participants were instructed to bid on the item shown below, a tabletop airhockey table, using the virtual currency "BlueCoin".
+The auction was explained to follow the BDM mechanism and it was also stated that three participants of the experiment would be randomly selected, their auction would be simulated and they would receive the outcome.
+The only difference between the groups was the exchange rate between BlueCoin and the British Pound (£) and the endowment that the participants received in BlueCoin.
+The first group received an endowment of 10 BlueCoin where one BlueCoin equals £5 and the second group recieved an endowment of 250 BlueCoin where one BlueCoin equals £0.2.
+To complete the auction, participants were asked to respond with their bid, in BlueCoin.
+
+The final part of the experiment consisted of optional follow-up questions that were used to determine if there are any trends in bidding behaviour based on some characteristics of the participants.
+The questions asked were about whether they had previously lived in a different country than the UK, how often they tend to travel outside of the UK and what their typical expenditure is in a given month.
+The intention behind the first two questions is to use them as a proxy for experience dealing with foreign currencies, where presumably people that travel frequently or have lived in multiple countries are more experienced with currency conversion calculations.
+The final question was asked to be able to determine whether there were any systematic differences in WTP based on a participants normal expenditure.
+
+## Auction Design
+
+Since the aim of the study was to determine whether there were any systematic differences in WTP between consumers when the only differing factor is the currency used, we decided to not include a control group that bid on the item using Pounds, which was the design of some of the experiments run by RAS [@Raghubir2002].
+This allowed for a simpler design and more power given the same sample size.
+Further, unlike the studies run by RAS [@Raghubir2002] and WER [@Wertenbroch2007], we did not use a fiat currency or mix of fiat and fictional currencies, but used only one fictional currency for both groups.
+On the one hand, this simplification was due to a focus of wether the effects described in previous papers also held in similar ways for virtual currencies.
+On the other hand, it also allowed us to preclude any biases or previous experience that participants might have had towards or with certain currencies.
+In the course of this, we chose the relatively undescript name for a fictional, virtual currency: BlueCoin.
+
+Another important decision in the design of the experiment was which item to select that a majority of participants would have a non-zero WTP.
+This is important since if the majority or even the entirety of participants were to bid zero on the item, then we would only learn that this was the participants' WTP for that good, but not whether there are any systematic differences in the WTP when using different currencies.
+Hence, we selected a tabletop airhockey table, something that few enough people have so that they won't want another one, but enough people want with a non-zero WTP, especially among a student population.
+In fact, only six participants of the experiment stated a WTP of 0.
+
+In designing the main part of the experiment, we chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP.
+The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@cite].
+As mentioned above, the studies conducted by RAS [@Raghubir2002], WER [@Wertenbroch2007] (with the exception of one permutation of one of the studies) and Fang [@Fang2019] did not implement incentive-compatible methods of eliciting the participants' preferences, making this experiment and important addition to these previous studies in examining whether the effects describe still hold when a more accurate way of eliciting WTP is used.
+In order to incentivise the participants even further, we ran a lottery that paid out three randomly-chosen participants based on their actual choices made in the auction and by simulating the BDM mechanism using a random number generator.
+Due to budget constraints, we were only able to play this lottery for three people, but given that the sample size of the experiment was relatively small, the potential to receive one's outcome is likely to have helped in eliciting the participants' true WTP.
+
+Finally, given our budget, we were able to give participants an endowment of £50 each, which was around double of what the item costs to buy.
+Assuming that the item is priced roughly around the average WTP (which turned out to be correct), this endowment was chosen to leave enough room for people with higher WTP to make their bid and for us to capture this in the data.
+This is important for the goals of the experiment, since if we had, for example, chosen an endowment of £20, the majority of participants might have bid their maximum amount, hindering our ability to meaningfully compare WTP across the two groups.
+We chose relatively simple exchange rates of 5 and $1/5$ so that the exchange rate calculations would be relatively easy to make, allowing us to be more confident that differences between groups were not due to the mental effort required to do calculations but due to something else.
+
+## Limitations
+
+In setting up the experiment, we incorrectly used the BDM mechanism.
+Instead of explaining it as a sealed-bid second-price auction, the experiment instructions explained it as a sealed-bid first-price auction.
+Unlike in a second-price auction, the participants of a first price auction do not have a dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@cite].
+[@todo]
+
+Another limitation of the study is the low sample size of 41 participants, which entails lower statistical power and thus a lower likelihood of detecting a true positive when an effect actually exists.
+I will examine this in further detail in the next section, conducting a power analysis and estimating how big the sample size should have been to achieve an adequate level of power.
+
+# Results
+
+There were 41 participants, 21 in the first group and 20 in the second.
+For consistency, I will refer to the first group as the fraction group, since 0.2 BlueCoin = £1, and the second as the multiple group, since 5 BlueCoin = £1, in line with the terminology used by RAS [@Raghubir2002].
+To conduct the data analysis, I normalised the bids across both groups by converting them into pounds and computed the following summary statistics:
+
+```{r}
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data_formatted.csv")
+
+# Summary statistics for the bid columns
+summary(experiment_data$group_fraction_bid_in_pounds)
+sd(experiment_data$group_fraction_bid_in_pounds, na.rm = TRUE)
+
+summary(experiment_data$group_multiple_bid_in_pounds)
+sd(experiment_data$group_multiple_bid_in_pounds, na.rm = TRUE)
+```
+
+Further, I plotted the following boxplot, in order to visually see the difference between the groups:
+
+```{r}
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data_formatted.csv")
+
+# Plot a boxplot for the bid columns
+boxplot(
+    experiment_data$group_fraction_bid_in_pounds,
+    experiment_data$group_multiple_bid_in_pounds,
+    main = "Boxplot of fraction and multiple group bids (in Pounds)",
+    names = c("Group Fraction", "Group Multiple"),
+    xlab = "Variables",
+    ylab = "Values"
+)
+```
+
+As is obvious from the summary statistics and the boxplot, there is a difference between both groups, namely that the bids in the multiple group seem to be higher on average than those in the fraction group.
+To investigate this hypothesis, I conducted a t-test of a difference in means between the groups, specifically a Welch Two Sample t-test.
+The null hypothesis is that the difference in means is equal to 0 (or, alternatively, that the means are the same) and the alternative hypothesis is that this difference is not equal to 0 (or, alternatively, that the means are not the same):
+
+$$h_0: µ_1 = µ_2$$
+$$h_1: µ_1 ≠ µ_2$$
+
+Hence, I conducted the t-test:
+
+```{r}
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data_formatted.csv")
+
+# Perform a t-test to compare the means of the two groups
+t.test(
+    experiment_data$group_fraction_bid_in_pounds,
+    experiment_data$group_multiple_bid_in_pounds
+)
+```
+
+The t-value of -1.2323 suggests that there is a difference in the means between the groups and, since it is negative, that the mean of the fraction group is lower.
+However, the p-value is 0.2252, which is quite high.
+If we take the typical significance level of $α = 0.05$ we find that the p-value is higher than this value, and thus fail to reject the null hypothesis at the 5% significance level.
+Further, the 95% confidence interval is $[-15.401901, 3.740092]$ which includes 0, providing further evidence that the difference in means between the groups is not statistically significant.
+Thus, we must conclude that while there seems to be a difference in means based on the sample data, this difference is not statistically significant for this sample size.
+
+To investigate this further, I have conducted a power analysis in order to determine the power of the t-test, which refers to the likelihood of the test detecting a true positive when an effect actually exists [@cite].
+High power would indicate that this likelihood is high and vice versa.
+To conduct the analysis, we first need to find the effect size, or Cohen's D and then implement the power analysis.
+Further, I will also conduct an analysis that investigates how big the sample size should have been to get a power of 80%.
+
+```{r}
+# Load the required libraries
+library(pwr)
+library(lsr)
+
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data_formatted.csv")
+
+# Conduct a power analysis to determine the power of the t test and
+# sample size required for a power of 0.8 (80%)
+effect_size <- cohensD(
+    experiment_data$group_fraction_bid_in_pounds,
+    experiment_data$group_multiple_bid_in_pounds
+)
+pwr.t2n.test(n1 = 21, n2 = 20, d = effect_size, sig.level = 0.05)
+pwr.t.test(power = 0.8, d = effect_size, sig.level = 0.05)
+
+```
+
+Based on the first test with the same significance level of 0.05, we can see that the power is 0.2246363 or 22%, which means that there is only a 22% likelihood of detecting a true positive if an effect actually exists.
+In other words, the likelihood of detecting a true difference in means between the two groups, when this difference exists, is only 22%, which is far below the usual value of 80%.
+The second test takes in this power of 80% and calculates the required sample size at the observed effect size.
+The result is $n = 107$ where the sample size is $2n$ or 214.
+Hence, using a sample size of 214 and observing the same effect, this t-test would yield a power of 80% at the 5% significance level.
+
+Finally, I conducted a regression of the demographic values collected in the fourth part of the experiment on the bids of each group.
+This is done in order to determine whether there is any correlation between the demographic variables and the bid amount, which would suggest that randomisation did not occur correctly, which could have been exacerbated by the small sample size.
+The regression yields the following outcomes:
+
+```{r}
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data_formatted.csv")
+
+# Conduct a regression analysis to examine the relationship between
+# the bid amounts and the demographic variables
+model_group_fraction <-
+    lm(group_fraction_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+        data = experiment_data
+    )
+summary(model_group_fraction)
+
+model_group_multiple <-
+    lm(group_multiple_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+        data = experiment_data
+    )
+summary(model_group_multiple)
+```
+
+Based on this regression, there are no statistically significant correlations at the 5% significance level or lower.
+However, there is one correlation that is significant at the 10% significance level, namely of `expenditure£551-£700` on the multiple group.
+The coefficient of -43.487 suggests that people whose usual expenditure is between £551 and £700 per month bid lower than the group overall.
+However, given that this is only significant at the 10% level and not at any lower ones, it is likely that this correlation is due to the low sample size rather than representing a true correlation between these variables.
+
+# Discussion
 
@@
 
-## Data 
-```{r}
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data.csv")
-
-# Rename the columns to more meaningful names
-colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <-
-    "group1_bid"
-colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <-
-    "group2_bid"
-colnames(experiment_data)[which(names(experiment_data) == "Q6")] <-
-    "lived_abroad"
-colnames(experiment_data)[which(names(experiment_data) == "Q7")] <-
-    "travel_frequency"
-colnames(experiment_data)[which(names(experiment_data) == "Q8")] <-
-    "expenditure"
-
-# Convert the values of the bid columns to pounds
-experiment_data$group1_bid_in_pounds <-
-    experiment_data$group1_bid * 5
-experiment_data$group2_bid_in_pounds <-
-    experiment_data$group2_bid / 5
-
-# Plot a boxplot for columns the bid columns
-boxplot(
-    experiment_data$group1_bid_in_pounds,
-    experiment_data$group2_bid_in_pounds,
-    main = "Boxplot of group 1 and group 2 bids (in Pounds)",
-    names = c("Group 1", "Group 2"),
-    xlab = "Variables",
-    ylab = "Values"
-)
-```
-
-# General Discussion
+## Summary
 

### 2024-04-14 data-analysis/model.R

@@ -4,68 +4,50 @@ library(lsr)
 
 # Load the experiment data
 experiment_data <-
-  read.csv("virtual-currencies-paper/data/experiment_data.csv")
-
-# Rename the columns to more meaningful names
-colnames(experiment_data)[which(names(experiment_data) == "Q5a")] <-
-  "group1_bid"
-colnames(experiment_data)[which(names(experiment_data) == "Q5b")] <-
-  "group2_bid"
-colnames(experiment_data)[which(names(experiment_data) == "Q6")] <-
-  "lived_abroad"
-colnames(experiment_data)[which(names(experiment_data) == "Q7")] <-
-  "travel_frequency"
-colnames(experiment_data)[which(names(experiment_data) == "Q8")] <-
-  "expenditure"
-
-# Convert the values of the bid columns to pounds
-experiment_data$group1_bid_in_pounds <-
-  experiment_data$group1_bid * 5
-experiment_data$group2_bid_in_pounds <-
-  experiment_data$group2_bid / 5
+  read.csv("virtual-currencies-paper/data/experiment_data_formatted.csv")
 
 # Summary statistics for the bid columns
-summary(experiment_data$group1_bid_in_pounds)
-sd(experiment_data$group1_bid_in_pounds, na.rm = TRUE)
+summary(experiment_data$group_fraction_bid_in_pounds)
+sd(experiment_data$group_fraction_bid_in_pounds, na.rm = TRUE)
 
-summary(experiment_data$group2_bid_in_pounds)
-sd(experiment_data$group2_bid_in_pounds, na.rm = TRUE)
+summary(experiment_data$group_multiple_bid_in_pounds)
+sd(experiment_data$group_multiple_bid_in_pounds, na.rm = TRUE)
 
 # Plot a boxplot for the bid columns
 boxplot(
-  experiment_data$group1_bid_in_pounds,
-  experiment_data$group2_bid_in_pounds,
-  main = "Boxplot of group 1 and group 2 bids (in Pounds)",
-  names = c("Group 1", "Group 2"),
+  experiment_data$group_fraction_bid_in_pounds,
+  experiment_data$group_multiple_bid_in_pounds,
+  main = "Boxplot of fraction and multiple group bids (in Pounds)",
+  names = c("Group Fraction", "Group Multiple"),
   xlab = "Variables",
   ylab = "Values"
 )
 
 # Perform a t-test to compare the means of the two groups
 t.test(
-  experiment_data$group1_bid_in_pounds,
[…]

### 2024-04-14 paper.qmd
add model draft

@@
 # Introduction
+
+For consistency, I will refer to the first group as the fraction group, since 0.2 BlueCoin = £1, and the second as the multiple group, since 5 BlueCoin = £1, in line with the terminology used by RAS [@Raghubir2002].
 
@@
 
-# Model
+# Theoretical Framework
 
-ratio (traditional) model:
-- formulate valuation of good as ratio to budget in home currency
-- convert valuation of good into bid currency
+## Standard Model
 
-assumptions:
-- is it rational if we always assume that the conversion will be accurate? what if this causes more mental effort than reward?
-- people can easily do those calculations in their head
+Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@cite].
+Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio with the budget in order to determine what proportion of their spending power is required to purchase the good.
+To formaulate valuations of goods in a different currency, consumers would first determine the value of the good in their home currency and subsequently apply the exchange rate to get their valuation in the foreign currency.
+Hence, the model follows a two step process:
 
-if we agree with assumptions, then there should be (small) differences but not systematic ones (see methodology)
+1. Formaulate valuation of good as ratio to budget in home currency
+2. Convert the valuation into foreign currency
 
-face value model:
-- formulate valuation of good in home currency
-- convert valuation of good into bid currency but weighted by nominal value of foreign currency
+Alternatively, this can be stated using the following syntax:
 
-$$V = Vn$$
-$$V = Vr$$
-$$V = aVn + (1 - a)Vr$$
+$$V_n = f(\dfrac{x}{M_n})$$
+$$V = V_n * X = V_r$$
 
-if this is the right model, then we should see group 1 overspend and group 2 underspend
+where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_n$ is the budget in the home currency, X is the exchange rate and $f(x)$ is some function that uses a valuation relative to the budget in order to compute $V_n$.
 
-value of money model:
-- difference in budget and item price in foreign currency
-- insufficiently adjust for exchange rate, leading to biased assesment of real value of transaction
+One assumption that is implicit in this model is that a consumer will always correctly adjust their valuation ratio based on the exact exchange rate.
+However, this might not always be the most rational thing to do.
+For example, when exchange rates fluctuate it might not be worth the effort of a consumer to always use the most up-to-date exchange rate, but rather to use some approximate value.
+Further, when an individual needs to do these exchange rate calculations in their head, it might not be worth the mental effort to calculate the amount in the foreign currency perfectly, but an approximation might be fine.
+For example, it would be rational to multiply an amount in home currency by 1.2 if the real exchange rate is 1.2113248 and the effort required is significant, such as when attempting to calculate it in one's hand.
+By loosening these assumptions, the standard model is able to account for small deviations from a consumer's real valuation of a good in a foreign currency.
 
-if this is the right model, then we should see group 1 underspend and group 2 overspend
+## Face Value Effect Model
+
+RAS [@Raghubir2002] put forth a different model for how consumers formulate their valuation of a good in a foreign currency based on their studies conducted.
+Sepcficially, they pose that a consumer will first formulate a valuation of a good in their home currency, before converting that amount into the foreign currency usging the exchange rate.
+However, they argue that this calculation is biased by the nominal value of the good in the home currency (in cases where a consumer does not determine their valuation but obvserves a price, this calculation would be biased by the nominal value of the good in the foreign currency).
+This model may be formaulated as follows:
+
+1. Formulate valuation of good in home currency
+2. Convert the valuation into foreign currency
+3. Adjust using the nominal value of good in home currency
+
+Alternatively, this can be stated using the following syntax:
+
+$$V = α(V_n) + (1 - α)V_r$$
+
+where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency and α is a weighting parameter such that $α ∈[0,1]$.
+Importantly, RAS [@Raghubir2002] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $V_n$.
+
+## Perceived Value of Money Model
+
+WER [@Wertenbroch2007] build on top of RAS, but put forth a different model that they argue is more representative of the behavior of actual consumers.
+Specifically, they agree with the standard model that valuations are made in relation to salient reference points, such as a consumers' budget, and argue that the model put forth by RAS fails to account for this.
+However, they disagree with the standard model that valuations use a ratio of price to budget, but instead argue that consumers think in terms of differneces.
+Hence, instead of considering what fraction of their purchasing power is required to buy a good, consumers consider how much of their budget is left over.
+However, WER argue that consumers inadequately adjust this difference to the exchange rate and are thus biased when considering goods in different currencies since the nominal differences between price and budget will differ when considering different currencies.
+This model can be formulated as follows:
+
+1. Formaulate valuation of good as difference to budget in home currency
+2. Convert the valuation into foreign currency
+3. Adjust using the difference to budget in the foreing currency
+
+Alternatively, this can be stated using the following syntax:
+
+$$V = α(M_r - V_r) + (1 - α)V_r$$
+
+where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_r$ is the budget in the foreign currency (real) and α is a weighting parameter such that $α ∈[0,1]$.
+Importantly, WER [@Wertenbroch2007] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $M_r - V_r$.
+
+## Predictions
+
+The three different models laid out above would each generate a different prediction in the following scenario, considering fraction and multiple exchange rates (the latter in brackets): a consumer values a good at £25 and needs to express this valuation in BlueCoin.
+The exchange rate of Pounds to BlueCoin is 1 BlueCoin = £5 (1 BlueCoin = £0.2) and their budget is 10 (250) BlueCoin.
+The models above would make the following predictions:
+
+- Standard model: $V_r = 5 (125) BlueCoin$
+- Face value effect model: $V_r > 5 (< 125) BlueCoin$
+- Perceived value of money model: $V_r < 5 (> 125) BlueCoin$
+
+where $V_r$ is the valuation of the good in the foreign currency.
+
+As a result:
+
+- Standard model: $V_rf = V_rm$
+- Face value effect model: $V_rf > V_rm$
+- Perceived value of money model: $V_rf < V_rm$
+
+where $V_rf$ is the valuation of the good in the foreign currency for the fraction group and $V_rm$ is the valuation of the good in the foreign currency for the multiple group.
+
+In other words, the standard model would expect the valuations to be the same across both exchange rates, the face value effect model would expect the consumer to overspend when presented with the fraction exchange rate and the perceived value of money model would expect the consumer to underspend when presented with the fraction exchange rate.
 
@@
 The only difference between the groups was the exchange rate between BlueCoin and the British Pound (£) and the endowment that the participants received in BlueCoin.
-The first group received an endowment of 10 BlueCoin where one BlueCoin equals £5 and the second group recieved an endowment of 250 BlueCoin where one BlueCoin equals £0.2.
+The first group received an endowment of 10 BlueCoin where 1 BlueCoin equals £5 and the second group recieved an endowment of 250 BlueCoin where 1 BlueCoin equals £0.2.
 To complete the auction, participants were asked to respond with their bid, in BlueCoin.
@@
 There were 41 participants, 21 in the first group and 20 in the second.
-For consistency, I will refer to the first group as the fraction group, since 0.2 BlueCoin = £1, and the second as the multiple group, since 5 BlueCoin = £1, in line with the terminology used by RAS [@Raghubir2002].
-To conduct the data analysis, I normalised the bids across both groups by converting them into pounds and computed the following summary statistics:
+To conduct the data analysis, I have normalised the bids across both groups by converting them into pounds and computed the following summary statistics:
 

### 2024-04-14 paper.qmd
add experiment instructions and source code

@@
 
+The full experiment instructions can be found as screenshots at [https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions](https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions).
+
 ## Source Code
+
+The full source code of the paper and the data analysis can be found at [https://github.com/kopy-kat/virtual-currencies-paper](https://github.com/kopy-kat/virtual-currencies-paper).

### 2024-04-15 paper.qmd
add intro draft

@@
 
-For consistency, I will refer to the first group as the fraction group, since 0.2 BlueCoin = £1, and the second as the multiple group, since 5 BlueCoin = £1, in line with the terminology used by RAS [@Raghubir2002].
+Past experience suggests that we treat forein currencies differently to our home currency and have difficulty adjusting to them.
+Previous research, such as the "money illusion" effect suggests that individuals are biased towards the nominal (or face value) of prices.
+Past research has investigated whether a systemic effect
 
-Intro
+RAS [@Raghubir2002] examined the effect of using foreign currencies on consumption behavior and argue that there is a systematic difference in spending behavior based on the exchange rate of the foreign currency to an individuals' home currency.
+Specifically, they showed that when a foreign currency is a fraction of the home currency (e.g.
+1 unit in home currency is 0.2 units in foreign currency) consumers tend to overspend in real terms relative to their home currency.
+On the other hand, when the foreign currency is a multiple of the home currency (e.g.
+1 unit in home currency is 5 units in foreign currency) consumers tend to underspend in real terms.^[For consistency, I will use the terms fraction and multiple currencies throughout this paper as defined here.] RAS argue that this effect arises because individuals are anchored on the face value of the foreign currency which influences the exchange rate calculations from and to their home currencies.
+Hence, RAS term the result of this inadequate adjustment the face value effect.
 
-Literature review
+WER [@Wertenbroch2007] consider the findings by RAS and reiterate their conclusion that individuals inadequately calculate the values of goods between differnet currencies, leading to systematic differences in spending behavior based on the exchange rate between the foreign and home currencies.
+However, WER argue that the process of adjustment occurs differently, namely that individuals calculate their valutaions of goods based on salient reference points, such as budget constraints.
+Contrary to standard theory, WER argue that consumers care about the differnce between a valuation and their budget rather than the ratio of the two.
+In the context of foreign currencies, the nominal value of this difference will diverge, leading to systematic differences in spending behavior.
+However, the direction of this bias is the exact opposite of the one shown by RAS.
+Specifically, WER show that consumers underspend when the foreign currency is a fraction of the home currency and overspend in the opposite case.
 
-face value paper [@Raghubir2002]: 
-- Arguably, the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency.
-Theoretically, therefore, the strength and persistence of the face value effect is likely to depend on the extent to which an individual has the opportunity or the time available to process exchange rate information and/or has experience in using a particular foreign currency.
-The last two studies show that the time available to process exchange information (study 5) and experience with a foreign currency, both measured (study 5) and manipulated (study 6), moderate the face value effect.
-- The asymmetric effect may be due to the differential difficulty in using whole numbers versus fractions or multiplying versus dividing
-- First, the reliance on face value may be a function of the ease with which the foreign money can be converted, implying that as r approaches a round number, a is likely to reduce.
-Second, a may vary with the absolute deviation of r from one, implying that as r deviates from one, the need to adjust increases implying a nonlinear relationship.
-From an effort-accuracy perspective, when r is close to one, it may not be worthwhile to adjust.
-Further, note that for currencies that are multiples of the home currency, r can range from one to , whereas for fractional currencies, r is bounded between zero and one.
-The lower bound may account for the lower likelihood of adjustment for a currency that is a fraction of the homecurrency.
-Future research should examine the asymmetric and nonlinear nature of this effect
-- Despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
-For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation.
+Fang [@Fang2019] further builds on top of the research by RAS and aims to extend it to the domain of "virtual" currencies, which refers to non-fiat currencies that are digital in nature and not controlled and issued by a central bank.
+Examples of virtual currencies include video game (or in-game) currencies, rewards points, airmiles, cryptocurrencies and more to the extent that these are at least somewhat liquid.
+Investigating in-game currencies specifically, Fang shows that consumer valuations systematically deviate when using these currencies relative to the home currency.
+Fang's findings correspond with those of RAS and the face value effect.
 
-fang paper [@Fang2019]:
-- did not implement bdm because infeasible
+This paper aims to build on the aforementioned research in several important ways.
+Foremost, previous research is conclusive that there is an effect that using foreign currencies has on individuals' consumption behavior relative to using their home currencies, but is divided on the direction of this effect.
+Hence, this paper attempts to evaluate the different models posed and use a study to test which model most adequately predicts the perceived behaviour.
+Second, previous research has only assigned minor significance to using incentive-compatible mechanisms to elicit true preferences of participants.
+These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@cite].
+Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingnesses to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] RAS [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
+For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation".
+Similarly, Fang [@Fang2019] noted that implementing the BDM mechanism was infeasible for the study he conducted but that future research should focus on using something like it to elicit WTP.
+Finally, this paper aims to extend the previous literature on the effects of using virtual currencies specifically, due to their increasing rise in importance when transacting or making purchasing decisions online.
 
-perceived value of money [@Wertenbroch2007]:
-- In particular, we extend previous research in several important ways.
-We propose a conceptualization that not only considers the nominal prices faced by consumers but also takes salient reference values into account, such as the budget consumers have available to make a purchase or the price of competing purchase options.
-By including budget constraints and reference standards, our conceptualization links nominal valuations to standard economic as well as psychophysical theory.
-We propose and test two alternative computational mechanisms by which consumers might evaluate prices in different currencies relative to such ,reference standards.
-Specifically, do consumers use the difference between reference values and prices to derive their evaluations or the ratio of the two?
-
-build on perceived value of money paper; where to extend:
-- incentive compatible mechanism
-- control for familiarity of currencies (easy on mind, easy on wallet) [@Alter2008]
-- examine the dispute between it and face value Paper
-- expand to virtual currencies (fang)
+Findings of paper
 
@@
 On the other hand, it also allowed us to preclude any biases or previous experience that participants might have had towards or with certain currencies.
-In the course of this, we chose the relatively undescript name for a fictional, virtual currency: BlueCoin.
+RAS [@Raghubir2002] acknowledge that "the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency ...
+[which] is likely to depend on the extent to which an individual has the opportunity or the time available to process exchange rate information and/or has experience in using a particular foreign currency".
+To bias participants the least, we chose the relatively undescript name for a fictional, virtual currency: BlueCoin.
 
@@
 We chose relatively simple exchange rates of 5 and $1/5$ so that the exchange rate calculations would be relatively easy to make, allowing us to be more confident that differences between groups were not due to the mental effort required to do calculations but due to something else.
+RAS [@Raghubir2002] acknowledge that "the reliance on face value may be a function of the ease with which the foreign money can be converted.
+...
+Future research should examine the asymmetric and nonlinear nature of this effect".
+Since the goal of this study is to investigate that an effect exists that is not solely based on a high difficulty or large mental effort required when doing specific, difficult calculations, we aimed to make the calculations as easy as possible in order to isolate the effect of the exchange rate and nominal value of the foreign currency.
 

### 2024-04-16 paper.qmd
first draft

@@
 ---
-title: "BEE Paper"
-date: 2024-03-16
+title: "Effect of the Nominal Value of Foreign Currencies in valuing a good"
+date: 2024-04-16
 author:
@@
     email: konrad.kopp@stcatz.ox.ac.uk
-    affiliation: University of Oxford
+    affiliation: 
+      - name: University of Oxford
 abstract: > 
-  The abstract is currently pending
+  Research into the effect of using foreign currencies on consumption behaviour suggests that consumers systematically under- or overspend based on the nominal (face) value of the foreign currency.
+However, previous research is undecided on which direction this effect has, with the two most prominent models leading to different and mutually exclusive outcomes.
+This paper considers the different models and tests their predictive and explanatory accuracy using a study.
+It finds that individuals tend to underspend when the foreign currency is less numerous than (a fraction of) the home currency and overspend when the opposite is the case.
+license: "CC0"
+copyright: 
+  holder: Konrad Kopp
+  year: 2024
 keywords:
@@
 
-Past experience suggests that we treat forein currencies differently to our home currency and have difficulty adjusting to them.
+Past experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them.
 Previous research, such as the "money illusion" effect suggests that individuals are biased towards the nominal (or face value) of prices.
@@
 
-RAS [@Raghubir2002] examined the effect of using foreign currencies on consumption behavior and argue that there is a systematic difference in spending behavior based on the exchange rate of the foreign currency to an individuals' home currency.
+RAS [@Raghubir2002] examined the effect of using foreign currencies on consumption behaviour and argue that there is a systematic difference in spending behaviour based on the exchange rate of the foreign currency to an individuals' home currency.
 Specifically, they showed that when a foreign currency is a fraction of the home currency (e.g.
@@
 
-WER [@Wertenbroch2007] consider the findings by RAS and reiterate their conclusion that individuals inadequately calculate the values of goods between differnet currencies, leading to systematic differences in spending behavior based on the exchange rate between the foreign and home currencies.
-However, WER argue that the process of adjustment occurs differently, namely that individuals calculate their valutaions of goods based on salient reference points, such as budget constraints.
-Contrary to standard theory, WER argue that consumers care about the differnce between a valuation and their budget rather than the ratio of the two.
-In the context of foreign currencies, the nominal value of this difference will diverge, leading to systematic differences in spending behavior.
+WER [@Wertenbroch2007] consider the findings by RAS and reiterate their conclusion that individuals inadequately calculate the values of goods between differnet currencies, leading to systematic differences in spending behaviour based on the exchange rate between the foreign and home currencies.
+However, WER argue that the process of adjustment occurs differently, namely that individuals calculate their valuations of goods based on salient reference points, such as budget constraints.
+Contrary to standard theory, WER argue that consumers care about the difference between a valuation and their budget rather than the ratio of the two.
+In the context of foreign currencies, the nominal value of this difference will diverge, leading to systematic differences in spending behaviour.
 However, the direction of this bias is the exact opposite of the one shown by RAS.
@@
 This paper aims to build on the aforementioned research in several important ways.
-Foremost, previous research is conclusive that there is an effect that using foreign currencies has on individuals' consumption behavior relative to using their home currencies, but is divided on the direction of this effect.
+Foremost, previous research is conclusive that there is an effect that using foreign currencies has on individuals' consumption behaviour relative to using their home currencies, but is divided on the direction of this effect.
 Hence, this paper attempts to evaluate the different models posed and use a study to test which model most adequately predicts the perceived behaviour.
@@
 These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@cite].
-Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingnesses to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] RAS [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
+Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] RAS [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
 For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation".
@@
 
-Findings of paper
+First, I present the theoretical frameworks that have been outlined by previous research in a way that makes it easy to compare and contrast them.
+These frameworks are the standard model described in consumer choice theory, the model suggested by RAS and the model suggested by WER.
+Then, I consider what each of these frameworks would predict in a concrete case and show that all three models come to different and mutually exclusive conclusions.
+In order to test which of these frameworks is most accurate in predicting observed behaviour, I conduct a study in which two groups each formulate their WTP for a specific good in an incentive compatible way, with the only difference between the groups being the exchange rate of the currency used to their home currency and, as a result, the face values of their budget and bid.
+Analysing the study, I find that consumers tend to underspend when the foreign currency is a fraction and overspend when the foreign currency is a multiple, which is predicted by the module proposed by WER.
+However, due to the limited sample size of the study, this result is not statistically significant and does not have significant power.
+Finally, in the discussion, I will evaluate the implications of the findings for the theoretical frameworks outlined, consider alternative explanations for the perceived effect and argue that the model proposed by WER is the most accurate in predicting and describing consumer behaviour when using foreign currencies.
 
@@
 RAS [@Raghubir2002] put forth a different model for how consumers formulate their valuation of a good in a foreign currency based on their studies conducted.
-Sepcficially, they pose that a consumer will first formulate a valuation of a good in their home currency, before converting that amount into the foreign currency usging the exchange rate.
-However, they argue that this calculation is biased by the nominal value of the good in the home currency (in cases where a consumer does not determine their valuation but obvserves a price, this calculation would be biased by the nominal value of the good in the foreign currency).
-This model may be formaulated as follows:
+Specifically, they pose that a consumer will first formulate a valuation of a good in their home currency, before converting that amount into the foreign currency using the exchange rate.
+However, they argue that this calculation is biased by the nominal value of the good in the home currency (in cases where a consumer does not determine their valuation but observes a price, this calculation would be biased by the nominal value of the good in the foreign currency).
+This model may be formulated as follows:
 
@@
 
-WER [@Wertenbroch2007] build on top of RAS, but put forth a different model that they argue is more representative of the behavior of actual consumers.
+WER [@Wertenbroch2007] build on top of RAS, but put forth a different model that they argue is more representative of the behaviour of actual consumers.
 Specifically, they agree with the standard model that valuations are made in relation to salient reference points, such as a consumers' budget, and argue that the model put forth by RAS fails to account for this.
-However, they disagree with the standard model that valuations use a ratio of price to budget, but instead argue that consumers think in terms of differneces.
+However, they disagree with the standard model that valuations use a ratio of price to budget, but instead argue that consumers think in terms of differences.
 Hence, instead of considering what fraction of their purchasing power is required to buy a good, consumers consider how much of their budget is left over.
@@
 2. Convert the valuation into foreign currency
-3. Adjust using the difference to budget in the foreing currency
+3. Adjust using the difference to budget in the foreign currency
 
@@
 The study itself was split into four parts: Consent Form, Introduction, Auction and Follow-Up Questions.
-The entire experiment instructions can be found in the [Experiment Instructions](./paper.qmd#experiment-instructions) section of the Appendix.
+The entire experiment instructions can be found in the Experiment Instructions section of the Appendix.
 The first section asked participants to read through and sign the consent form in order to ensure that they were informed about the study and what data would be collected.
@@
 The only difference between the groups was the exchange rate between BlueCoin and the British Pound (£) and the endowment that the participants received in BlueCoin.
-The first group received an endowment of 10 BlueCoin where 1 BlueCoin equals £5 and the second group recieved an endowment of 250 BlueCoin where 1 BlueCoin equals £0.2.
+The first group received an endowment of 10 BlueCoin where 1 BlueCoin equals £5 and the second group received an endowment of 250 BlueCoin where 1 BlueCoin equals £0.2.
 To complete the auction, participants were asked to respond with their bid, in BlueCoin.
@@
 [which] is likely to depend on the extent to which an individual has the opportunity or the time available to process exchange rate information and/or has experience in using a particular foreign currency".
-To bias participants the least, we chose the relatively undescript name for a fictional, virtual currency: BlueCoin.
+To bias participants the least, we chose the relatively nondescript name for a fictional, virtual currency: BlueCoin.
 
@@
 
-# Conduct a power analysis to determine the power of the t test and
-# sample size required for a power of 0.8 (80%)
+# Calculate the effect size (Cohens D)
 effect_size <- cohensD(
@@
 )
+
+# Find the power of the t test conducted above
 pwr.t2n.test(n1 = 21, n2 = 20, d = effect_size, sig.level = 0.05)
+
+# Find the sample size required to achieve a power of 0.8 (80%)
 pwr.t.test(power = 0.8, d = effect_size, sig.level = 0.05)
@@
 model_group_fraction <-
-    lm(group_fraction_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+    lm(
+        group_fraction_bid_in_pounds ~ lived_abroad +
+            travel_frequency + expenditure,
         data = experiment_data
@@
 model_group_multiple <-
-    lm(group_multiple_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+    lm(
+        group_multiple_bid_in_pounds ~ lived_abroad +
+            travel_frequency + expenditure,
         data = experiment_data
@@
 
-outline the results: 
-- group one bid lower on average; statistically significant (but only power of 20%)
-- no statistically significant relationships between domographic vars and bids found
+The study conducted found that the fraction group bid less on average than the multiple group.
+The difference in the means across the two groups is around £6, or over 10% of the budget, signifying that this difference occurs due to a systematic difference in how each group calculated their value in the foreign currency BlueCoin.
+The only difference between the groups was the exchange rate of BlueCoin to the Pound and, as a result, the nominal values of the budget and the bids.
+This would suggest that this difference in bids occurs based on whether the foreign currency is a fraction or multiple of the home currency.
 
-how to explain results: value of money paper suggests this, confirms this research, face value effect stipulates differernt result but seems to be incorrect here
+Above, I outlined the three models for how consumers value goods in a foreign currency that have been suggested by previous research.
+The standard model would have predicted that both groups would on average bid the same, the model proposed by RAS would have predicted that the fraction group would on average bid more than the multiple group and the model proposed by WER would have predicted the opposite, namely that the fraction group would on average bid less than the multiple group.
+Hence, the third model would have made the most accurate prediction for the study conducted.
 
-explanations for effect:
-- model 3 is the correct one
-- anchoring: higher endowment anchors at higher endowment value (perceived value of money paper: When provided with a budget, consumers might anchor on the nominal value of that budget when evaluating transactions in foreign currencies.
-But this would not have predicted the biased evaluations in our follow-up study since the nominal budget was the same (i.e., quoted in US$) across all numerosity conditions)
-- people are worse at dividing than multiplying (or put in less effort) (or reverse)
-- people prefer using whole numbers over fractions - is this rational? mental ease?
-- sample size too small - power analysis
+WER [@Wertenbroch2007] argue that this systematic difference in valuations and spending behaviour occurs because consumers are biased by the nominal difference between their budget and the product valuation in the foreign currency and thus anchor on this value when converting amounts between their home currency and foreign currency.
+In the context of the study, this would entail that the fraction group calculated the difference between their budget and their bid in BlueCoin and adjusted their bid downwards based on it, since this difference will be small (< 10) in nominal terms.
+The multiple group, on the other hand, would have calculated this difference and received a larger amount of surplus for the same product valuation in real terms (25 times as large as the fraction group).
+Hence, the multiple group would have adjusted their bid upwards, leading to a higher average bid in real (and nominal) terms.
 
-conclusion: agree with model 3 and get rid of some of its shortcomings:
-- incentive compatible mechanism
-- control for familiarity of currencies (easy on mind, easy on wallet)
-- examine the dispute between it and face value Paper
-- expand to virtual currencies (fang)
+However, there might be alternative explanations that would be consistent with one or more of the other models outlined above.
+One explanation would be that consumers are biased by only the nominal value of their budget in the foreign currency and not by the difference between their budget and their valuation of a product in the foreign currency.
+While this alternative hypothesis would be hard to prove, it would not change the prediction for how the difference in product valuations across groups that use either a fraction or multiple currency.
+Indeed, it would predict the exact same result and is this consistent with the model proposed by WER, even though it differs in explaining the internal work that individuals would do to come to that conclusion.
 
-## Summary
+Another explanation might be that people are simply worse at dividing than multiplying (or the reverse), which could explain the perceived differences between the groups.
+On this explanation, even when consumers have the same valuation in real terms, one group will systematically fail to accurately convert this value into the foreign currency.
+However, this explanation is unlikely for several reasons.
+First, this claim assumes that a significant amount of people are significantly worse at performing one of the operations across all numbers.
+From experience, it seems that when considering most numbers, one of these operations is more difficult to do but it is not always the same one.
+Secondly, this assumes that people are unaware enough of their difficulties (even when they are very significant) that they do not use a calculator even when one is easily accessible, such as when completing the survey for this study online.
+For these reasons, this explanation seems unlikely to be accurate.
+
+A third contending explanation could be that individuals simply prefer whole numbers over fractions or decimals, leading consumers to make less granular valuation choices when considering a currency with a low face value.
+Because of this, there can be differences in groups of individuals if, for example, many participants choose to round down.
+For example, it could have been the case that the average valuation of the good in the fraction group was 24 but if a significant amount of participants rounded this down to the nearest whole number in BlueCoin (4), then this average valuation would now be 20.
+This explanation can be supported empirically, given that only 3 bids out of 41 were decimal numbers.
+One might also claim that this behaviour of preferring whole numbers is rational, given that it requires less mental effort, especially when multiplying and dividing these numbers.
+Further research is required to determine whether this hypothesis could explain the observed behaviour, either entirely or in conjunction with one of the models proposed above.
+
+The former two of these alternative explanations seem unlikely, but the latter seems like it could be accurate at least to some extent.
+Nonetheless, it seems like the model proposed by WER is the most accurate in predicting and explaining the perceived behaviour when formulating valuations of goods in different foreign currencies.
 
 ## Limitations, Theoretical Implications and Future Research
+
+The main limitation of the study conducted is that due to small sample size, the results are not statistically significant at the 5% level and the power of the t-test for a difference in means is only 22%.
+Hence, even though the observations line up with the model proposed by WER, it could be the case that this result is due to random chance.
+In repeating this study, it would be useful to get a sample size of at least 200 participants to roughly achieve a power of 80% and likely also statistical significance in conducting the t-test.
+The second major limitation is that the BDM mechanism was implemented incorrectly, entailing that the dominant strategy for participants was not to reveal their true valuations on the good.
+In a redo, this mistake could be fixed relatively easily by adjusting the experiment instructions.
+
+Apart from the limitations, the major theoretical implication of this paper is the finding that the model proposed by WER [@Wertenbroch2007] seems to be most accurate in predicting and explaining consumer behaviour when eliciting a WTP on a good.
+In line with these authors, this conclusion contradicts the findings of the "face value effect" by RAS [@Raghubir2002] and subsequently by Fang [@Fang2019].
+Further, this conclusion implies that, contrary to traditional consumption theory, individuals formulate their WTP in relation to the difference between their budget and the valuation of a good rather than its' ratio.
+
+Future research could build on this study and its' findings in several important ways: first, it would make sense to conduct a similar or identical study with the BDM mechanism implemented correctly and a greater sample size.
+This would allow for greater certainty that the effect observed is statistically significant and reproducible.
+Further, it would be interesting to investigate the third alternative hypothesis formulated above in order to gain a better understanding into the exact process that leads individuals to systematically under- or overspend when using foreign currencies.
 

### 2024-04-16 paper.tex
first draft

--- 2024-04-16 paper.qmd
@@
----
-title: "Effect of the Nominal Value of Foreign Currencies in valuing a good"
-date: 2024-04-16
-author:
-  - name: Konrad Kopp
-    email: konrad.kopp@stcatz.ox.ac.uk
-    affiliation: 
-      - name: University of Oxford
-abstract: > 
-  Research into the effect of using foreign currencies on consumption behaviour suggests that consumers systematically under- or overspend based on the nominal (face) value of the foreign currency.
-However, previous research is undecided on which direction this effect has, with the two most prominent models leading to different and mutually exclusive outcomes.
-This paper considers the different models and tests their predictive and explanatory accuracy using a study.
-It finds that individuals tend to underspend when the foreign currency is less numerous than (a fraction of) the home currency and overspend when the opposite is the case.
-license: "CC0"
-copyright: 
-  holder: Konrad Kopp
-  year: 2024
-keywords:
-  - Behavioural Economics
-  - Face Value Effect
-  - Consumer Choice Theory
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+]{report}
 
-# Introduction
+\usepackage{amsmath,amssymb}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\usepackage[lmargin=30mm,rmargin=30mm]{geometry}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-Past experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them.
-Previous research, such as the "money illusion" effect suggests that individuals are biased towards the nominal (or face value) of prices.
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
+  \fi
+  % set entry spacing
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+\usepackage[noblocks]{authblk}
+\renewcommand*{\Authsep}{, }
+\renewcommand*{\Authand}{, }
+\renewcommand*{\Authands}{, }
+\renewcommand\Affilfont{\small}
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{british}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\usepackage{bookmark}
+
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Effect of the Nominal Value of Foreign Currencies in valuing a good},
+  pdfauthor={Konrad Kopp},
+  pdflang={en-GB},
+  pdfkeywords={Behavioural Economics, Face Value Effect, Consumer Choice
+Theory},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
+
+\title{Effect of the Nominal Value of Foreign Currencies in valuing a
+good}
+
+  \author{Konrad Kopp}
+            \affil{%
+                  University of Oxford
+              }
+
+\date{2024-04-16}
+\begin{document}
+\maketitle
+\begin{abstract}
+Research into the effect of using foreign currencies on consumption
+behaviour suggests that consumers systematically under- or overspend
+based on the nominal (face) value of the foreign currency. However,
+previous research is undecided on which direction this effect has, with
+the two most prominent models leading to different and mutually
+exclusive outcomes. This paper considers the different models and tests
+their predictive and explanatory accuracy using a study. It finds that
+individuals tend to underspend when the foreign currency is less
+numerous than (a fraction of) the home currency and overspend when the
+opposite is the case.
+\end{abstract}
+
+\renewcommand*\contentsname{Table of contents}
+{
+\hypersetup{linkcolor=}
+\setcounter{tocdepth}{2}
+\tableofcontents
+}
+\chapter{Introduction}\label{introduction}
+
+Past experience suggests that we treat foreign currencies differently to
+our home currency and have difficulty adjusting to them. Previous
+research, such as the ``money illusion'' effect suggests that
+individuals are biased towards the nominal (or face value) of prices.
 Past research has investigated whether a systemic effect
 
-RAS [@Raghubir2002] examined the effect of using foreign currencies on consumption behaviour and argue that there is a systematic difference in spending behaviour based on the exchange rate of the foreign currency to an individuals' home currency.
-Specifically, they showed that when a foreign currency is a fraction of the home currency (e.g.
-1 unit in home currency is 0.2 units in foreign currency) consumers tend to overspend in real terms relative to their home currency.
-On the other hand, when the foreign currency is a multiple of the home currency (e.g.
-1 unit in home currency is 5 units in foreign currency) consumers tend to underspend in real terms.^[For consistency, I will use the terms fraction and multiple currencies throughout this paper as defined here.] RAS argue that this effect arises because individuals are anchored on the face value of the foreign currency which influences the exchange rate calculations from and to their home currencies.
-Hence, RAS term the result of this inadequate adjustment the face value effect.
+RAS (Raghubir and Srivastava 2002) examined the effect of using foreign
+currencies on consumption behaviour and argue that there is a systematic
+difference in spending behaviour based on the exchange rate of the
+foreign currency to an individuals' home currency. Specifically, they
+showed that when a foreign currency is a fraction of the home currency
+(e.g.~1 unit in home currency is 0.2 units in foreign currency)
+consumers tend to overspend in real terms relative to their home
+currency. On the other hand, when the foreign currency is a multiple of
+the home currency (e.g.~1 unit in home currency is 5 units in foreign
+currency) consumers tend to underspend in real terms.\footnote{For
+  consistency, I will use the terms fraction and multiple currencies
+  throughout this paper as defined here.} RAS argue that this effect
+arises because individuals are anchored on the face value of the foreign
+currency which influences the exchange rate calculations from and to
+their home currencies. Hence, RAS term the result of this inadequate
+adjustment the face value effect.
 
-WER [@Wertenbroch2007] consider the findings by RAS and reiterate their conclusion that individuals inadequately calculate the values of goods between differnet currencies, leading to systematic differences in spending behaviour based on the exchange rate between the foreign and home currencies.
-However, WER argue that the process of adjustment occurs differently, namely that individuals calculate their valuations of goods based on salient reference points, such as budget constraints.
-Contrary to standard theory, WER argue that consumers care about the difference between a valuation and their budget rather than the ratio of the two.
-In the context of foreign currencies, the nominal value of this difference will diverge, leading to systematic differences in spending behaviour.
-However, the direction of this bias is the exact opposite of the one shown by RAS.
-Specifically, WER show that consumers underspend when the foreign currency is a fraction of the home currency and overspend in the opposite case.
+WER (Wertenbroch, Soman, and Chattopadhyay 2007) consider the findings
+by RAS and reiterate their conclusion that individuals inadequately
+calculate the values of goods between differnet currencies, leading to
+systematic differences in spending behaviour based on the exchange rate
+between the foreign and home currencies. However, WER argue that the
+process of adjustment occurs differently, namely that individuals
+calculate their valuations of goods based on salient reference points,
+such as budget constraints. Contrary to standard theory, WER argue that
+consumers care about the difference between a valuation and their budget
+rather than the ratio of the two. In the context of foreign currencies,
+the nominal value of this difference will diverge, leading to systematic
+differences in spending behaviour. However, the direction of this bias
+is the exact opposite of the one shown by RAS. Specifically, WER show
+that consumers underspend when the foreign currency is a fraction of the
+home currency and overspend in the opposite case.
 
-Fang [@Fang2019] further builds on top of the research by RAS and aims to extend it to the domain of "virtual" currencies, which refers to non-fiat currencies that are digital in nature and not controlled and issued by a central bank.
-Examples of virtual currencies include video game (or in-game) currencies, rewards points, airmiles, cryptocurrencies and more to the extent that these are at least somewhat liquid.
-Investigating in-game currencies specifically, Fang shows that consumer valuations systematically deviate when using these currencies relative to the home currency.
-Fang's findings correspond with those of RAS and the face value effect.
+Fang (Fang 2019) further builds on top of the research by RAS and aims
+to extend it to the domain of ``virtual'' currencies, which refers to
+non-fiat currencies that are digital in nature and not controlled and
+issued by a central bank. Examples of virtual currencies include video
+game (or in-game) currencies, rewards points, airmiles, cryptocurrencies
+and more to the extent that these are at least somewhat liquid.
+Investigating in-game currencies specifically, Fang shows that consumer
+valuations systematically deviate when using these currencies relative
+to the home currency. Fang's findings correspond with those of RAS and
+the face value effect.
 
-This paper aims to build on the aforementioned research in several important ways.
-Foremost, previous research is conclusive that there is an effect that using foreign currencies has on individuals' consumption behaviour relative to using their home currencies, but is divided on the direction of this effect.
-Hence, this paper attempts to evaluate the different models posed and use a study to test which model most adequately predicts the perceived behaviour.
-Second, previous research has only assigned minor significance to using incentive-compatible mechanisms to elicit true preferences of participants.
-These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@cite].
-Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] RAS [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
-For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation".
-Similarly, Fang [@Fang2019] noted that implementing the BDM mechanism was infeasible for the study he conducted but that future research should focus on using something like it to elicit WTP.
-Finally, this paper aims to extend the previous literature on the effects of using virtual currencies specifically, due to their increasing rise in importance when transacting or making purchasing decisions online.
+This paper aims to build on the aforementioned research in several
+important ways. Foremost, previous research is conclusive that there is
+an effect that using foreign currencies has on individuals' consumption
+behaviour relative to using their home currencies, but is divided on the
+direction of this effect. Hence, this paper attempts to evaluate the
+different models posed and use a study to test which model most
+adequately predicts the perceived behaviour. Second, previous research
+has only assigned minor significance to using incentive-compatible
+mechanisms to elicit true preferences of participants. These mechanisms
+have been established to elicit more accurate responses from
+participants that are closer to their true preferences (\textbf{cite?}).
+Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to
+elicit participants' willingness to pay (WTP).{[}\^{} The BDM mechanism
+will be defined and explained in more detail in the Methodology section
+below.{]} RAS (Raghubir and Srivastava 2002) expressed the concern that
+``despite attempts to make the tasks as realistic as possible, the
+studies reported were laboratory experiments, and issues of
+generalizability when real money is on the line do arise. For instance,
+when people actually exchange foreign currency they may feel richer or
+poorer depending on the exchange rate, and the differences in
+perceptions of wealth may affect product valuation''. Similarly, Fang
+(Fang 2019) noted that implementing the BDM mechanism was infeasible for
+the study he conducted but that future research should focus on using
+something like it to elicit WTP. Finally, this paper aims to extend the
+previous literature on the effects of using virtual currencies
+specifically, due to their increasing rise in importance when
+transacting or making purchasing decisions online.
 
-First, I present the theoretical frameworks that have been outlined by previous research in a way that makes it easy to compare and contrast them.
-These frameworks are the standard model described in consumer choice theory, the model suggested by RAS and the model suggested by WER.
-Then, I consider what each of these frameworks would predict in a concrete case and show that all three models come to different and mutually exclusive conclusions.
-In order to test which of these frameworks is most accurate in predicting observed behaviour, I conduct a study in which two groups each formulate their WTP for a specific good in an incentive compatible way, with the only difference between the groups being the exchange rate of the currency used to their home currency and, as a result, the face values of their budget and bid.
-Analysing the study, I find that consumers tend to underspend when the foreign currency is a fraction and overspend when the foreign currency is a multiple, which is predicted by the module proposed by WER.
-However, due to the limited sample size of the study, this result is not statistically significant and does not have significant power.
-Finally, in the discussion, I will evaluate the implications of the findings for the theoretical frameworks outlined, consider alternative explanations for the perceived effect and argue that the model proposed by WER is the most accurate in predicting and describing consumer behaviour when using foreign currencies.
+First, I present the theoretical frameworks that have been outlined by
+previous research in a way that makes it easy to compare and contrast
+them. These frameworks are the standard model described in consumer
+choice theory, the model suggested by RAS and the model suggested by
+WER. Then, I consider what each of these frameworks would predict in a
+concrete case and show that all three models come to different and
+mutually exclusive conclusions. In order to test which of these
+frameworks is most accurate in predicting observed behaviour, I conduct
+a study in which two groups each formulate their WTP for a specific good
+in an incentive compatible way, with the only difference between the
+groups being the exchange rate of the currency used to their home
+currency and, as a result, the face values of their budget and bid.
+Analysing the study, I find that consumers tend to underspend when the
+foreign currency is a fraction and overspend when the foreign currency
+is a multiple, which is predicted by the module proposed by WER.
+However, due to the limited sample size of the study, this result is not
+statistically significant and does not have significant power. Finally,
+in the discussion, I will evaluate the implications of the findings for
+the theoretical frameworks outlined, consider alternative explanations
+for the perceived effect and argue that the model proposed by WER is the
+most accurate in predicting and describing consumer behaviour when using
+foreign currencies.
 
-# Theoretical Framework
+\chapter{Theoretical Framework}\label{theoretical-framework}
 
-## Standard Model
+\section{Standard Model}\label{standard-model}
 
-Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@cite].
-Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio with the budget in order to determine what proportion of their spending power is required to purchase the good.
-To formaulate valuations of goods in a different currency, consumers would first determine the value of the good in their home currency and subsequently apply the exchange rate to get their valuation in the foreign currency.
-Hence, the model follows a two step process:
+Standard consumer choice theory suggests that individuals formulate
+valuations of goods in relation to reference points, such as their
+budget (\textbf{cite?}). Specifically, standard theory poses that
+consumers evaluate their valuation for a good as a ratio with the budget
+in order to determine what proportion of their spending power is
+required to purchase the good. To formaulate valuations of goods in a
+different currency, consumers would first determine the value of the
+good in their home currency and subsequently apply the exchange rate to
+get their valuation in the foreign currency. Hence, the model follows a
+two step process:
 
-1. Formaulate valuation of good as ratio to budget in home currency
-2. Convert the valuation into foreign currency
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Formaulate valuation of good as ratio to budget in home currency
+\item
+  Convert the valuation into foreign currency
+\end{enumerate}
 
@@
 
-$$V_n = f(\dfrac{x}{M_n})$$
-$$V = V_n * X = V_r$$
+\[V_n = f(\dfrac{x}{M_n})\] \[V = V_n * X = V_r\]
 
-where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_n$ is the budget in the home currency, X is the exchange rate and $f(x)$ is some function that uses a valuation relative to the budget in order to compute $V_n$.
+where V is the valuation in the foreign currency, \(V_n\) is the
+valuation of the good in the home currency (nominal), \(V_r\) is the
+valuation of the good in the foreign currency, \(M_n\) is the budget in
+the home currency, X is the exchange rate and \(f(x)\) is some function
+that uses a valuation relative to the budget in order to compute
+\(V_n\).
 
-One assumption that is implicit in this model is that a consumer will always correctly adjust their valuation ratio based on the exact exchange rate.
-However, this might not always be the most rational thing to do.
-For example, when exchange rates fluctuate it might not be worth the effort of a consumer to always use the most up-to-date exchange rate, but rather to use some approximate value.
-Further, when an individual needs to do these exchange rate calculations in their head, it might not be worth the mental effort to calculate the amount in the foreign currency perfectly, but an approximation might be fine.
-For example, it would be rational to multiply an amount in home currency by 1.2 if the real exchange rate is 1.2113248 and the effort required is significant, such as when attempting to calculate it in one's hand.
-By loosening these assumptions, the standard model is able to account for small deviations from a consumer's real valuation of a good in a foreign currency.
+One assumption that is implicit in this model is that a consumer will
+always correctly adjust their valuation ratio based on the exact
+exchange rate. However, this might not always be the most rational thing
+to do. For example, when exchange rates fluctuate it might not be worth
+the effort of a consumer to always use the most up-to-date exchange
+rate, but rather to use some approximate value. Further, when an
+individual needs to do these exchange rate calculations in their head,
+it might not be worth the mental effort to calculate the amount in the
+foreign currency perfectly, but an approximation might be fine. For
+example, it would be rational to multiply an amount in home currency by
+1.2 if the real exchange rate is 1.2113248 and the effort required is
+significant, such as when attempting to calculate it in one's hand. By
+loosening these assumptions, the standard model is able to account for
+small deviations from a consumer's real valuation of a good in a foreign
+currency.
 
-## Face Value Effect Model
+\section{Face Value Effect Model}\label{face-value-effect-model}
 
-RAS [@Raghubir2002] put forth a different model for how consumers formulate their valuation of a good in a foreign currency based on their studies conducted.
-Specifically, they pose that a consumer will first formulate a valuation of a good in their home currency, before converting that amount into the foreign currency using the exchange rate.
-However, they argue that this calculation is biased by the nominal value of the good in the home currency (in cases where a consumer does not determine their valuation but observes a price, this calculation would be biased by the nominal value of the good in the foreign currency).
-This model may be formulated as follows:
+RAS (Raghubir and Srivastava 2002) put forth a different model for how
+consumers formulate their valuation of a good in a foreign currency
+based on their studies conducted. Specifically, they pose that a
+consumer will first formulate a valuation of a good in their home
+currency, before converting that amount into the foreign currency using
+the exchange rate. However, they argue that this calculation is biased
+by the nominal value of the good in the home currency (in cases where a
+consumer does not determine their valuation but observes a price, this
+calculation would be biased by the nominal value of the good in the
+foreign currency). This model may be formulated as follows:
 
-1. Formulate valuation of good in home currency
-2. Convert the valuation into foreign currency
-3. Adjust using the nominal value of good in home currency
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Formulate valuation of good in home currency
+\item
+  Convert the valuation into foreign currency
+\item
+  Adjust using the nominal value of good in home currency
+\end{enumerate}
 
@@
 
-$$V = α(V_n) + (1 - α)V_r$$
+\[V = α(V_n) + (1 - α)V_r\]
 
-where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency and α is a weighting parameter such that $α ∈[0,1]$.
-Importantly, RAS [@Raghubir2002] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $V_n$.
+where V is the valuation in the foreign currency, \(V_n\) is the
+valuation of the good in the home currency (nominal), \(V_r\) is the
+valuation of the good in the foreign currency and α is a weighting
+parameter such that \(α ∈[0,1]\). Importantly, RAS (Raghubir and
+Srivastava 2002) argue that \(α > 0\) and that V is hence not equal to
+\(V_r\) but is biased towards \(V_n\).
 
-## Perceived Value of Money Model
+\section{Perceived Value of Money
+Model}\label{perceived-value-of-money-model}
 
-WER [@Wertenbroch2007] build on top of RAS, but put forth a different model that they argue is more representative of the behaviour of actual consumers.
-Specifically, they agree with the standard model that valuations are made in relation to salient reference points, such as a consumers' budget, and argue that the model put forth by RAS fails to account for this.
-However, they disagree with the standard model that valuations use a ratio of price to budget, but instead argue that consumers think in terms of differences.
-Hence, instead of considering what fraction of their purchasing power is required to buy a good, consumers consider how much of their budget is left over.
-However, WER argue that consumers inadequately adjust this difference to the exchange rate and are thus biased when considering goods in different currencies since the nominal differences between price and budget will differ when considering different currencies.
-This model can be formulated as follows:
+WER (Wertenbroch, Soman, and Chattopadhyay 2007) build on top of RAS,
+but put forth a different model that they argue is more representative
+of the behaviour of actual consumers. Specifically, they agree with the
+standard model that valuations are made in relation to salient reference
+points, such as a consumers' budget, and argue that the model put forth
+by RAS fails to account for this. However, they disagree with the
+standard model that valuations use a ratio of price to budget, but
+instead argue that consumers think in terms of differences. Hence,
+instead of considering what fraction of their purchasing power is
+required to buy a good, consumers consider how much of their budget is
+left over. However, WER argue that consumers inadequately adjust this
+difference to the exchange rate and are thus biased when considering
+goods in different currencies since the nominal differences between
+price and budget will differ when considering different currencies. This
+model can be formulated as follows:
 
-1. Formaulate valuation of good as difference to budget in home currency
-2. Convert the valuation into foreign currency
-3. Adjust using the difference to budget in the foreign currency
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Formaulate valuation of good as difference to budget in home currency
+\item
+  Convert the valuation into foreign currency
+\item
+  Adjust using the difference to budget in the foreign currency
+\end{enumerate}
 
@@
 
-$$V = α(M_r - V_r) + (1 - α)V_r$$
+\[V = α(M_r - V_r) + (1 - α)V_r\]
 
-where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_r$ is the budget in the foreign currency (real) and α is a weighting parameter such that $α ∈[0,1]$.
-Importantly, WER [@Wertenbroch2007] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $M_r - V_r$.
+where V is the valuation in the foreign currency, \(V_n\) is the
+valuation of the good in the home currency (nominal), \(V_r\) is the
+valuation of the good in the foreign currency, \(M_r\) is the budget in
+the foreign currency (real) and α is a weighting parameter such that
+\(α ∈[0,1]\). Importantly, WER (Wertenbroch, Soman, and Chattopadhyay
+2007) argue that \(α > 0\) and that V is hence not equal to \(V_r\) but
+is biased towards \(M_r - V_r\).
 
-## Predictions
+\section{Predictions}\label{predictions}
 
-The three different models laid out above would each generate a different prediction in the following scenario, considering fraction and multiple exchange rates (the latter in brackets): a consumer values a good at £25 and needs to express this valuation in BlueCoin.
-The exchange rate of Pounds to BlueCoin is 1 BlueCoin = £5 (1 BlueCoin = £0.2) and their budget is 10 (250) BlueCoin.
-The models above would make the following predictions:
+The three different models laid out above would each generate a
+different prediction in the following scenario, considering fraction and
+multiple exchange rates (the latter in brackets): a consumer values a
+good at £25 and needs to express this valuation in BlueCoin. The
+exchange rate of Pounds to BlueCoin is 1 BlueCoin = £5 (1 BlueCoin =
+£0.2) and their budget is 10 (250) BlueCoin. The models above would make
+the following predictions:
 
-- Standard model: $V_r = 5 (125) BlueCoin$
-- Face value effect model: $V_r > 5 (< 125) BlueCoin$
-- Perceived value of money model: $V_r < 5 (> 125) BlueCoin$
+\begin{itemize}
+\tightlist
+\item
+  Standard model: \(V_r = 5 (125) BlueCoin\)
+\item
+  Face value effect model: \(V_r > 5 (< 125) BlueCoin\)
+\item
+  Perceived value of money model: \(V_r < 5 (> 125) BlueCoin\)
+\end{itemize}
 
-where $V_r$ is the valuation of the good in the foreign currency.
+where \(V_r\) is the valuation of the good in the foreign currency.
 
@@
 
-- Standard model: $V_rf = V_rm$
-- Face value effect model: $V_rf > V_rm$
-- Perceived value of money model: $V_rf < V_rm$
+\begin{itemize}
+\tightlist
+\item
+  Standard model: \(V_rf = V_rm\)
+\item
+  Face value effect model: \(V_rf > V_rm\)
+\item
+  Perceived value of money model: \(V_rf < V_rm\)
+\end{itemize}
 
-where $V_rf$ is the valuation of the good in the foreign currency for the fraction group and $V_rm$ is the valuation of the good in the foreign currency for the multiple group.
+where \(V_rf\) is the valuation of the good in the foreign currency for
+the fraction group and \(V_rm\) is the valuation of the good in the
+foreign currency for the multiple group.
 
-In other words, the standard model would expect the valuations to be the same across both exchange rates, the face value effect model would expect the consumer to overspend when presented with the fraction exchange rate and the perceived value of money model would expect the consumer to underspend when presented with the fraction exchange rate.
+In other words, the standard model would expect the valuations to be the
+same across both exchange rates, the face value effect model would
+expect the consumer to overspend when presented with the fraction
+exchange rate and the perceived value of money model would expect the
+consumer to underspend when presented with the fraction exchange rate.
 
-# Method
+\chapter{Method}\label{method}
 
-There were 41 participants of the study, most of them current undergraduate students at the University of Oxford, but some participants were also recent graduates and postgraduate students.
-The study took place online, using Qualtrics, and students were incentivised to participate by taking part in a lottery, which will be explained in further detail below.
+There were 41 participants of the study, most of them current
+undergraduate students at the University of Oxford, but some
+participants were also recent graduates and postgraduate students. The
+study took place online, using Qualtrics, and students were incentivised
+to participate by taking part in a lottery, which will be explained in
+further detail below.
 
-## Study
+\section{Study}\label{study}
 
-The study itself was split into four parts: Consent Form, Introduction, Auction and Follow-Up Questions.
-The entire experiment instructions can be found in the Experiment Instructions section of the Appendix.
-The first section asked participants to read through and sign the consent form in order to ensure that they were informed about the study and what data would be collected.
-In the introductory section, the BDM mechanism was explained to participants and they were asked to complete four question that tested their understanding of the mechanism.
-The aim of this section was to ensure that participants properly understood how the mechanism worked in order to elicit their real WTP during the main part of the study.
+The study itself was split into four parts: Consent Form, Introduction,
+Auction and Follow-Up Questions. The entire experiment instructions can
+be found in the Experiment Instructions section of the Appendix. The
+first section asked participants to read through and sign the consent
+form in order to ensure that they were informed about the study and what
+data would be collected. In the introductory section, the BDM mechanism
+was explained to participants and they were asked to complete four
+question that tested their understanding of the mechanism. The aim of
+this section was to ensure that participants properly understood how the
+mechanism worked in order to elicit their real WTP during the main part
+of the study.
 
-The auction was the main part of the study, with the aim of eliciting the participants' WTP on a specific item and comparing these across different currencies used.
-In this section, participants were randomly split into two groups with almost-identical instructions.
-The participants were instructed to bid on the item shown below, a tabletop airhockey table, using the virtual currency "BlueCoin".
-The auction was explained to follow the BDM mechanism and it was also stated that three participants of the experiment would be randomly selected, their auction would be simulated and they would receive the outcome.
-The only difference between the groups was the exchange rate between BlueCoin and the British Pound (£) and the endowment that the participants received in BlueCoin.
-The first group received an endowment of 10 BlueCoin where 1 BlueCoin equals £5 and the second group received an endowment of 250 BlueCoin where 1 BlueCoin equals £0.2.
-To complete the auction, participants were asked to respond with their bid, in BlueCoin.
+The auction was the main part of the study, with the aim of eliciting
+the participants' WTP on a specific item and comparing these across
+different currencies used. In this section, participants were randomly
+split into two groups with almost-identical instructions. The
+participants were instructed to bid on the item shown below, a tabletop
+airhockey table, using the virtual currency ``BlueCoin''. The auction
+was explained to follow the BDM mechanism and it was also stated that
+three participants of the experiment would be randomly selected, their
+auction would be simulated and they would receive the outcome. The only
+difference between the groups was the exchange rate between BlueCoin and
+the British Pound (£) and the endowment that the participants received
+in BlueCoin. The first group received an endowment of 10 BlueCoin where
+1 BlueCoin equals £5 and the second group received an endowment of 250
+BlueCoin where 1 BlueCoin equals £0.2. To complete the auction,
+participants were asked to respond with their bid, in BlueCoin.
 
-The final part of the experiment consisted of optional follow-up questions that were used to determine if there are any trends in bidding behaviour based on some characteristics of the participants.
-The questions asked were about whether they had previously lived in a different country than the UK, how often they tend to travel outside of the UK and what their typical expenditure is in a given month.
-The intention behind the first two questions is to use them as a proxy for experience dealing with foreign currencies, where presumably people that travel frequently or have lived in multiple countries are more experienced with currency conversion calculations.
-The final question was asked to be able to determine whether there were any systematic differences in WTP based on a participants normal expenditure.
+The final part of the experiment consisted of optional follow-up
+questions that were used to determine if there are any trends in bidding
+behaviour based on some characteristics of the participants. The
+questions asked were about whether they had previously lived in a
+different country than the UK, how often they tend to travel outside of
+the UK and what their typical expenditure is in a given month. The
+intention behind the first two questions is to use them as a proxy for
+experience dealing with foreign currencies, where presumably people that
+travel frequently or have lived in multiple countries are more
+experienced with currency conversion calculations. The final question
+was asked to be able to determine whether there were any systematic
+differences in WTP based on a participants normal expenditure.
 
-## Auction Design
+\section{Auction Design}\label{auction-design}
 
-Since the aim of the study was to determine whether there were any systematic differences in WTP between consumers when the only differing factor is the currency used, we decided to not include a control group that bid on the item using Pounds, which was the design of some of the experiments run by RAS [@Raghubir2002].
-This allowed for a simpler design and more power given the same sample size.
-Further, unlike the studies run by RAS [@Raghubir2002] and WER [@Wertenbroch2007], we did not use a fiat currency or mix of fiat and fictional currencies, but used only one fictional currency for both groups.
-On the one hand, this simplification was due to a focus of wether the effects described in previous papers also held in similar ways for virtual currencies.
-On the other hand, it also allowed us to preclude any biases or previous experience that participants might have had towards or with certain currencies.
-RAS [@Raghubir2002] acknowledge that "the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency ...
-[which] is likely to depend on the extent to which an individual has the opportunity or the time available to process exchange rate information and/or has experience in using a particular foreign currency".
-To bias participants the least, we chose the relatively nondescript name for a fictional, virtual currency: BlueCoin.
+Since the aim of the study was to determine whether there were any
+systematic differences in WTP between consumers when the only differing
+factor is the currency used, we decided to not include a control group
+that bid on the item using Pounds, which was the design of some of the
+experiments run by RAS (Raghubir and Srivastava 2002). This allowed for
+a simpler design and more power given the same sample size. Further,
+unlike the studies run by RAS (Raghubir and Srivastava 2002) and WER
+(Wertenbroch, Soman, and Chattopadhyay 2007), we did not use a fiat
+currency or mix of fiat and fictional currencies, but used only one
+fictional currency for both groups. On the one hand, this simplification
+was due to a focus of wether the effects described in previous papers
+also held in similar ways for virtual currencies. On the other hand, it
+also allowed us to preclude any biases or previous experience that
+participants might have had towards or with certain currencies. RAS
+(Raghubir and Srivastava 2002) acknowledge that ``the face value effect
+is due to the accessibility and perceptual salience of the face value of
+the foreign currency \ldots{} {[}which{]} is likely to depend on the
+extent to which an individual has the opportunity or the time available
+to process exchange rate information and/or has experience in using a
+particular foreign currency''. To bias participants the least, we chose
+the relatively nondescript name for a fictional, virtual currency:
+BlueCoin.
 
-Another important decision in the design of the experiment was which item to select that a majority of participants would have a non-zero WTP.
-This is important since if the majority or even the entirety of participants were to bid zero on the item, then we would only learn that this was the participants' WTP for that good, but not whether there are any systematic differences in the WTP when using different currencies.
-Hence, we selected a tabletop airhockey table, something that few enough people have so that they won't want another one, but enough people want with a non-zero WTP, especially among a student population.
-In fact, only six participants of the experiment stated a WTP of 0.
+Another important decision in the design of the experiment was which
+item to select that a majority of participants would have a non-zero
+WTP. This is important since if the majority or even the entirety of
+participants were to bid zero on the item, then we would only learn that
+this was the participants' WTP for that good, but not whether there are
+any systematic differences in the WTP when using different currencies.
+Hence, we selected a tabletop airhockey table, something that few enough
+people have so that they won't want another one, but enough people want
+with a non-zero WTP, especially among a student population. In fact,
+only six participants of the experiment stated a WTP of 0.
 
-In designing the main part of the experiment, we chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP.
-The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@cite].
-As mentioned above, the studies conducted by RAS [@Raghubir2002], WER [@Wertenbroch2007] (with the exception of one permutation of one of the studies) and Fang [@Fang2019] did not implement incentive-compatible methods of eliciting the participants' preferences, making this experiment and important addition to these previous studies in examining whether the effects describe still hold when a more accurate way of eliciting WTP is used.
-In order to incentivise the participants even further, we ran a lottery that paid out three randomly-chosen participants based on their actual choices made in the auction and by simulating the BDM mechanism using a random number generator.
-Due to budget constraints, we were only able to play this lottery for three people, but given that the sample size of the experiment was relatively small, the potential to receive one's outcome is likely to have helped in eliciting the participants' true WTP.
+In designing the main part of the experiment, we chose to conduct an
+auction, specifically using the BDM mechanism, in order to have an
+incentive-compatible method of eliciting the participants' WTP. The
+BDM's incentive compatibility in eliciting WTP is a well-established
+phenomenon that is superior to using participants' stated preferences
+(\textbf{cite?}). As mentioned above, the studies conducted by RAS
+(Raghubir and Srivastava 2002), WER (Wertenbroch, Soman, and
+Chattopadhyay 2007) (with the exception of one permutation of one of the
+studies) and Fang (Fang 2019) did not implement incentive-compatible
+methods of eliciting the participants' preferences, making this
+experiment and important addition to these previous studies in examining
+whether the effects describe still hold when a more accurate way of
+eliciting WTP is used. In order to incentivise the participants even
+further, we ran a lottery that paid out three randomly-chosen
+participants based on their actual choices made in the auction and by
+simulating the BDM mechanism using a random number generator. Due to
+budget constraints, we were only able to play this lottery for three
+people, but given that the sample size of the experiment was relatively
+small, the potential to receive one's outcome is likely to have helped
+in eliciting the participants' true WTP.
 
-Finally, given our budget, we were able to give participants an endowment of £50 each, which was around double of what the item costs to buy.
-Assuming that the item is priced roughly around the average WTP (which turned out to be correct), this endowment was chosen to leave enough room for people with higher WTP to make their bid and for us to capture this in the data.
-This is important for the goals of the experiment, since if we had, for example, chosen an endowment of £20, the majority of participants might have bid their maximum amount, hindering our ability to meaningfully compare WTP across the two groups.
-We chose relatively simple exchange rates of 5 and $1/5$ so that the exchange rate calculations would be relatively easy to make, allowing us to be more confident that differences between groups were not due to the mental effort required to do calculations but due to something else.
-RAS [@Raghubir2002] acknowledge that "the reliance on face value may be a function of the ease with which the foreign money can be converted.
-...
-Future research should examine the asymmetric and nonlinear nature of this effect".
-Since the goal of this study is to investigate that an effect exists that is not solely based on a high difficulty or large mental effort required when doing specific, difficult calculations, we aimed to make the calculations as easy as possible in order to isolate the effect of the exchange rate and nominal value of the foreign currency.
+Finally, given our budget, we were able to give participants an
+endowment of £50 each, which was around double of what the item costs to
+buy. Assuming that the item is priced roughly around the average WTP
+(which turned out to be correct), this endowment was chosen to leave
+enough room for people with higher WTP to make their bid and for us to
+capture this in the data. This is important for the goals of the
+experiment, since if we had, for example, chosen an endowment of £20,
+the majority of participants might have bid their maximum amount,
+hindering our ability to meaningfully compare WTP across the two groups.
+We chose relatively simple exchange rates of 5 and \(1/5\) so that the
+exchange rate calculations would be relatively easy to make, allowing us
+to be more confident that differences between groups were not due to the
+mental effort required to do calculations but due to something else. RAS
+(Raghubir and Srivastava 2002) acknowledge that ``the reliance on face
+value may be a function of the ease with which the foreign money can be
+converted. \ldots{} Future research should examine the asymmetric and
+nonlinear nature of this effect''. Since the goal of this study is to
+investigate that an effect exists that is not solely based on a high
+difficulty or large mental effort required when doing specific,
+difficult calculations, we aimed to make the calculations as easy as
+possible in order to isolate the effect of the exchange rate and nominal
+value of the foreign currency.
 
-## Limitations
+\section{Limitations}\label{limitations}
 
 In setting up the experiment, we incorrectly used the BDM mechanism.
-Instead of explaining it as a sealed-bid second-price auction, the experiment instructions explained it as a sealed-bid first-price auction.
-Unlike in a second-price auction, the participants of a first price auction do not have a dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@cite].
-[@todo]
+Instead of explaining it as a sealed-bid second-price auction, the
+experiment instructions explained it as a sealed-bid first-price
+auction. Unlike in a second-price auction, the participants of a first
+price auction do not have a dominant strategy to bid their true
+valuations, in fact there generally is no dominant strategy in such an
+auction (\textbf{cite?}). (\textbf{todo?})
 
-Another limitation of the study is the low sample size of 41 participants, which entails lower statistical power and thus a lower likelihood of detecting a true positive when an effect actually exists.
-I will examine this in further detail in the next section, conducting a power analysis and estimating how big the sample size should have been to achieve an adequate level of power.
+Another limitation of the study is the low sample size of 41
+participants, which entails lower statistical power and thus a lower
+likelihood of detecting a true positive when an effect actually exists.
+I will examine this in further detail in the next section, conducting a
+power analysis and estimating how big the sample size should have been
+to achieve an adequate level of power.
 
-# Results
+\chapter{Results}\label{results}
 
 There were 41 participants, 21 in the first group and 20 in the second.
-To conduct the data analysis, I have normalised the bids across both groups by converting them into pounds and computed the following summary statistics:
+To conduct the data analysis, I have normalised the bids across both
+groups by converting them into pounds and computed the following summary
+statistics:
 
-```{r}
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data_formatted.csv")
+\begin{verbatim}
+   Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+   0.00   10.00   20.00   19.74   32.00   50.00      20 
+\end{verbatim}
 
-# Summary statistics for the bid columns
-summary(experiment_data$group_fraction_bid_in_pounds)
-sd(experiment_data$group_fraction_bid_in_pounds, na.rm = TRUE)
+\begin{verbatim}
+[1] 15.49001
+\end{verbatim}
 
-summary(experiment_data$group_multiple_bid_in_pounds)
-sd(experiment_data$group_multiple_bid_in_pounds, na.rm = TRUE)
-```
+\begin{verbatim}
+   Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
+   0.00   16.50   27.50   25.57   35.25   50.00      21 
+\end{verbatim}
 
-Further, I plotted the following boxplot, in order to visually see the difference between the groups:
+\begin{verbatim}
+[1] 14.8083
+\end{verbatim}
 
-```{r}
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data_formatted.csv")
+Further, I plotted the following boxplot, in order to visually see the
+difference between the groups:
 
-# Plot a boxplot for the bid columns
-boxplot(
-    experiment_data$group_fraction_bid_in_pounds,
-    experiment_data$group_multiple_bid_in_pounds,
-    main = "Boxplot of fraction and multiple group bids (in Pounds)",
-    names = c("Group Fraction", "Group Multiple"),
-    xlab = "Variables",
-    ylab = "Values"
-)
-```
+\includegraphics{paper_files/figure-pdf/unnamed-chunk-2-1.pdf}
 
-As is obvious from the summary statistics and the boxplot, there is a difference between both groups, namely that the bids in the multiple group seem to be higher on average than those in the fraction group.
-To investigate this hypothesis, I conducted a t-test of a difference in means between the groups, specifically a Welch Two Sample t-test.
-The null hypothesis is that the difference in means is equal to 0 (or, alternatively, that the means are the same) and the alternative hypothesis is that this difference is not equal to 0 (or, alternatively, that the means are not the same):
+As is obvious from the summary statistics and the boxplot, there is a
+difference between both groups, namely that the bids in the multiple
+group seem to be higher on average than those in the fraction group. To
+investigate this hypothesis, I conducted a t-test of a difference in
+means between the groups, specifically a Welch Two Sample t-test. The
+null hypothesis is that the difference in means is equal to 0 (or,
+alternatively, that the means are the same) and the alternative
+hypothesis is that this difference is not equal to 0 (or, alternatively,
+that the means are not the same):
 
-$$h_0: µ_1 = µ_2$$
-$$h_1: µ_1 ≠ µ_2$$
+\[h_0: µ_1 = µ_2\] \[h_1: µ_1 ≠ µ_2\]
 
@@
 
-```{r}
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data_formatted.csv")
+\begin{verbatim}
 
-# Perform a t-test to compare the means of the two groups
-t.test(
-    experiment_data$group_fraction_bid_in_pounds,
-    experiment_data$group_multiple_bid_in_pounds
-)
-```
+    Welch Two Sample t-test
 
-The t-value of -1.2323 suggests that there is a difference in the means between the groups and, since it is negative, that the mean of the fraction group is lower.
-However, the p-value is 0.2252, which is quite high.
-If we take the typical significance level of $α = 0.05$ we find that the p-value is higher than this value, and thus fail to reject the null hypothesis at the 5% significance level.
-Further, the 95% confidence interval is $[-15.401901, 3.740092]$ which includes 0, providing further evidence that the difference in means between the groups is not statistically significant.
-Thus, we must conclude that while there seems to be a difference in means based on the sample data, this difference is not statistically significant for this sample size.
+data:  experiment_data$group_fraction_bid_in_pounds and experiment_data$group_multiple_bid_in_pounds
+t = -1.2323, df = 38.999, p-value = 0.2252
+alternative hypothesis: true difference in means is not equal to 0
+95 percent confidence interval:
+ -15.401901   3.740092
+sample estimates:
+mean of x mean of y 
+  19.7381   25.5690 
+\end{verbatim}
 
-To investigate this further, I have conducted a power analysis in order to determine the power of the t-test, which refers to the likelihood of the test detecting a true positive when an effect actually exists [@cite].
-High power would indicate that this likelihood is high and vice versa.
-To conduct the analysis, we first need to find the effect size, or Cohen's D and then implement the power analysis.
-Further, I will also conduct an analysis that investigates how big the sample size should have been to get a power of 80%.
+The t-value of -1.2323 suggests that there is a difference in the means
+between the groups and, since it is negative, that the mean of the
+fraction group is lower. However, the p-value is 0.2252, which is quite
+high. If we take the typical significance level of \(α = 0.05\) we find
+that the p-value is higher than this value, and thus fail to reject the
+null hypothesis at the 5\% significance level. Further, the 95\%
+confidence interval is \([-15.401901, 3.740092]\) which includes 0,
+providing further evidence that the difference in means between the
+groups is not statistically significant. Thus, we must conclude that
+while there seems to be a difference in means based on the sample data,
+this difference is not statistically significant for this sample size.
 
-```{r}
-# Load the required libraries
-library(pwr)
-library(lsr)
+To investigate this further, I have conducted a power analysis in order
+to determine the power of the t-test, which refers to the likelihood of
+the test detecting a true positive when an effect actually exists
+(\textbf{cite?}). High power would indicate that this likelihood is high
+and vice versa. To conduct the analysis, we first need to find the
+effect size, or Cohen's D and then implement the power analysis.
+Further, I will also conduct an analysis that investigates how big the
+sample size should have been to get a power of 80\%.
 
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data_formatted.csv")
+\begin{verbatim}
 
-# Calculate the effect size (Cohens D)
-effect_size <- cohensD(
-    experiment_data$group_fraction_bid_in_pounds,
-    experiment_data$group_multiple_bid_in_pounds
-)
+     t test power calculation
 
-# Find the power of the t test conducted above
-pwr.t2n.test(n1 = 21, n2 = 20, d = effect_size, sig.level = 0.05)
+             n1 = 21
+             n2 = 20
+              d = 0.3845806
+      sig.level = 0.05
+          power = 0.2246363
+    alternative = two.sided
+\end{verbatim}
 
-# Find the sample size required to achieve a power of 0.8 (80%)
-pwr.t.test(power = 0.8, d = effect_size, sig.level = 0.05)
+\begin{verbatim}
 
-```
+     Two-sample t test power calculation
 
-Based on the first test with the same significance level of 0.05, we can see that the power is 0.2246363 or 22%, which means that there is only a 22% likelihood of detecting a true positive if an effect actually exists.
-In other words, the likelihood of detecting a true difference in means between the two groups, when this difference exists, is only 22%, which is far below the usual value of 80%.
-The second test takes in this power of 80% and calculates the required sample size at the observed effect size.
-The result is $n = 107$ where the sample size is $2n$ or 214.
-Hence, using a sample size of 214 and observing the same effect, this t-test would yield a power of 80% at the 5% significance level.
+              n = 107.1047
+              d = 0.3845806
+      sig.level = 0.05
+          power = 0.8
+    alternative = two.sided
 
-Finally, I conducted a regression of the demographic values collected in the fourth part of the experiment on the bids of each group.
-This is done in order to determine whether there is any correlation between the demographic variables and the bid amount, which would suggest that randomisation did not occur correctly, which could have been exacerbated by the small sample size.
-The regression yields the following outcomes:
+NOTE: n is number in *each* group
+\end{verbatim}
 
-```{r}
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data_formatted.csv")
+Based on the first test with the same significance level of 0.05, we can
+see that the power is 0.2246363 or 22\%, which means that there is only
+a 22\% likelihood of detecting a true positive if an effect actually
+exists. In other words, the likelihood of detecting a true difference in
+means between the two groups, when this difference exists, is only 22\%,
+which is far below the usual value of 80\%. The second test takes in
+this power of 80\% and calculates the required sample size at the
+observed effect size. The result is \(n = 107\) where the sample size is
+\(2n\) or 214. Hence, using a sample size of 214 and observing the same
+effect, this t-test would yield a power of 80\% at the 5\% significance
+level.
 
-# Conduct a regression analysis to examine the relationship between
-# the bid amounts and the demographic variables
-model_group_fraction <-
-    lm(
-        group_fraction_bid_in_pounds ~ lived_abroad +
-            travel_frequency + expenditure,
-        data = experiment_data
-    )
-summary(model_group_fraction)
+Finally, I conducted a regression of the demographic values collected in
+the fourth part of the experiment on the bids of each group. This is
+done in order to determine whether there is any correlation between the
+demographic variables and the bid amount, which would suggest that
+randomisation did not occur correctly, which could have been exacerbated
+by the small sample size. The regression yields the following outcomes:
 
-model_group_multiple <-
-    lm(
-        group_multiple_bid_in_pounds ~ lived_abroad +
-            travel_frequency + expenditure,
-        data = experiment_data
-    )
-summary(model_group_multiple)
-```
+\begin{verbatim}
 
-Based on this regression, there are no statistically significant correlations at the 5% significance level or lower.
-However, there is one correlation that is significant at the 10% significance level, namely of `expenditure£551-£700` on the multiple group.
-The coefficient of -43.487 suggests that people whose usual expenditure is between £551 and £700 per month bid lower than the group overall.
-However, given that this is only significant at the 10% level and not at any lower ones, it is likely that this correlation is due to the low sample size rather than representing a true correlation between these variables.
+Call:
+lm(formula = group_fraction_bid_in_pounds ~ lived_abroad + travel_frequency + 
+    expenditure, data = experiment_data)
 
-# Discussion
+Residuals:
+    Min      1Q  Median      3Q     Max 
+-20.744 -10.085   0.000   7.481  33.333
 
-The study conducted found that the fraction group bid less on average than the multiple group.
-The difference in the means across the two groups is around £6, or over 10% of the budget, signifying that this difference occurs due to a systematic difference in how each group calculated their value in the foreign currency BlueCoin.
-The only difference between the groups was the exchange rate of BlueCoin to the Pound and, as a result, the nominal values of the budget and the bids.
-This would suggest that this difference in bids occurs based on whether the foreign currency is a fraction or multiple of the home currency.
+Coefficients: (2 not defined because of singularities)
+                                           Estimate Std. Error t value Pr(>|t|)
+(Intercept)                                  16.667     11.144   1.496    0.169
+lived_abroadNo                               16.883     34.290   0.492    0.634
+lived_abroadYes                               4.651     28.453   0.163    0.874
+travel_frequencyLess than once per 5 years   12.768     31.087   0.411    0.691
+travel_frequencyOnce per 1-2 years           -4.952     27.679  -0.179    0.862
+travel_frequencyOnce per 2-5 months           5.085     23.987   0.212    0.837
+travel_frequencyOnce per 3-5 years          -18.005     42.079  -0.428    0.679
+travel_frequencyOnce per 6-11 months         -6.488     24.395  -0.266    0.796
+travel_frequencyOnce per month or more           NA         NA      NA       NA
+expenditure£251-£400                         -6.317     17.686  -0.357    0.729
+expenditure£401-£550                         -5.544     19.548  -0.284    0.783
+expenditure£551-£700                         -8.884     20.685  -0.429    0.678
+expenditureAbove £1000                      -13.549     37.738  -0.359    0.728
+expenditureBelow £250                            NA         NA      NA       NA
 
-Above, I outlined the three models for how consumers value goods in a foreign currency that have been suggested by previous research.
-The standard model would have predicted that both groups would on average bid the same, the model proposed by RAS would have predicted that the fraction group would on average bid more than the multiple group and the model proposed by WER would have predicted the opposite, namely that the fraction group would on average bid less than the multiple group.
-Hence, the third model would have made the most accurate prediction for the study conducted.
+Residual standard error: 19.3 on 9 degrees of freedom
+  (20 observations deleted due to missingness)
+Multiple R-squared:  0.3013,    Adjusted R-squared:  -0.5528 
+F-statistic: 0.3527 on 11 and 9 DF,  p-value: 0.9466
+\end{verbatim}
 
-WER [@Wertenbroch2007] argue that this systematic difference in valuations and spending behaviour occurs because consumers are biased by the nominal difference between their budget and the product valuation in the foreign currency and thus anchor on this value when converting amounts between their home currency and foreign currency.
-In the context of the study, this would entail that the fraction group calculated the difference between their budget and their bid in BlueCoin and adjusted their bid downwards based on it, since this difference will be small (< 10) in nominal terms.
-The multiple group, on the other hand, would have calculated this difference and received a larger amount of surplus for the same product valuation in real terms (25 times as large as the fraction group).
-Hence, the multiple group would have adjusted their bid upwards, leading to a higher average bid in real (and nominal) terms.
+\begin{verbatim}
 
-However, there might be alternative explanations that would be consistent with one or more of the other models outlined above.
-One explanation would be that consumers are biased by only the nominal value of their budget in the foreign currency and not by the difference between their budget and their valuation of a product in the foreign currency.
-While this alternative hypothesis would be hard to prove, it would not change the prediction for how the difference in product valuations across groups that use either a fraction or multiple currency.
-Indeed, it would predict the exact same result and is this consistent with the model proposed by WER, even though it differs in explaining the internal work that individuals would do to come to that conclusion.
+Call:
+lm(formula = group_multiple_bid_in_pounds ~ lived_abroad + travel_frequency + 
+    expenditure, data = experiment_data)
 
-Another explanation might be that people are simply worse at dividing than multiplying (or the reverse), which could explain the perceived differences between the groups.
-On this explanation, even when consumers have the same valuation in real terms, one group will systematically fail to accurately convert this value into the foreign currency.
-However, this explanation is unlikely for several reasons.
-First, this claim assumes that a significant amount of people are significantly worse at performing one of the operations across all numbers.
-From experience, it seems that when considering most numbers, one of these operations is more difficult to do but it is not always the same one.
-Secondly, this assumes that people are unaware enough of their difficulties (even when they are very significant) that they do not use a calculator even when one is easily accessible, such as when completing the survey for this study online.
-For these reasons, this explanation seems unlikely to be accurate.
+Residuals:
+    Min      1Q  Median      3Q     Max 
+-15.667  -4.550   0.000   5.383  17.200
 
-A third contending explanation could be that individuals simply prefer whole numbers over fractions or decimals, leading consumers to make less granular valuation choices when considering a currency with a low face value.
-Because of this, there can be differences in groups of individuals if, for example, many participants choose to round down.
-For example, it could have been the case that the average valuation of the good in the fraction group was 24 but if a significant amount of participants rounded this down to the nearest whole number in BlueCoin (4), then this average valuation would now be 20.
-This explanation can be supported empirically, given that only 3 bids out of 41 were decimal numbers.
-One might also claim that this behaviour of preferring whole numbers is rational, given that it requires less mental effort, especially when multiplying and dividing these numbers.
-Further research is required to determine whether this hypothesis could explain the observed behaviour, either entirely or in conjunction with one of the models proposed above.
+Coefficients: (2 not defined because of singularities)
+                                       Estimate Std. Error t value Pr(>|t|)  
+(Intercept)                              20.000     13.715   1.458   0.1788  
+lived_abroadNo                           -0.600     17.250  -0.035   0.9730  
+lived_abroadYes                          17.600     17.250   1.020   0.3342  
+travel_frequencyOnce per 1-2 years        4.600     21.843   0.211   0.8379  
+travel_frequencyOnce per 2-5 months      12.400     17.250   0.719   0.4905  
+travel_frequencyOnce per 6-11 months      7.267     19.717   0.369   0.7210  
+travel_frequencyOnce per month or more       NA         NA      NA       NA  
+expenditure£251-£400                     -5.000     18.025  -0.277   0.7877  
+expenditure£401-£550                    -17.200     15.801  -1.089   0.3046  
+expenditure£551-£700                    -43.487     21.461  -2.026   0.0734 .
+expenditure£701-£850                     -8.400     17.250  -0.487   0.6379  
+expenditureAbove £1000                  -25.000     19.396  -1.289   0.2296  
+expenditureBelow £250                        NA         NA      NA       NA  
+---
+Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
 
-The former two of these alternative explanations seem unlikely, but the latter seems like it could be accurate at least to some extent.
-Nonetheless, it seems like the model proposed by WER is the most accurate in predicting and explaining the perceived behaviour when formulating valuations of goods in different foreign currencies.
+Residual standard error: 13.72 on 9 degrees of freedom
+  (21 observations deleted due to missingness)
+Multiple R-squared:  0.5937,    Adjusted R-squared:  0.1422 
+F-statistic: 1.315 on 10 and 9 DF,  p-value: 0.3456
+\end{verbatim}
 
-## Limitations, Theoretical Implications and Future Research
+Based on this regression, there are no statistically significant
+correlations at the 5\% significance level or lower. However, there is
+one correlation that is significant at the 10\% significance level,
+namely of \texttt{expenditure£551-£700} on the multiple group. The
+coefficient of -43.487 suggests that people whose usual expenditure is
+between £551 and £700 per month bid lower than the group overall.
+However, given that this is only significant at the 10\% level and not
+at any lower ones, it is likely that this correlation is due to the low
+sample size rather than representing a true correlation between these
+variables.
 
-The main limitation of the study conducted is that due to small sample size, the results are not statistically significant at the 5% level and the power of the t-test for a difference in means is only 22%.
-Hence, even though the observations line up with the model proposed by WER, it could be the case that this result is due to random chance.
-In repeating this study, it would be useful to get a sample size of at least 200 participants to roughly achieve a power of 80% and likely also statistical significance in conducting the t-test.
-The second major limitation is that the BDM mechanism was implemented incorrectly, entailing that the dominant strategy for participants was not to reveal their true valuations on the good.
-In a redo, this mistake could be fixed relatively easily by adjusting the experiment instructions.
+\chapter{Discussion}\label{discussion}
 
-Apart from the limitations, the major theoretical implication of this paper is the finding that the model proposed by WER [@Wertenbroch2007] seems to be most accurate in predicting and explaining consumer behaviour when eliciting a WTP on a good.
-In line with these authors, this conclusion contradicts the findings of the "face value effect" by RAS [@Raghubir2002] and subsequently by Fang [@Fang2019].
-Further, this conclusion implies that, contrary to traditional consumption theory, individuals formulate their WTP in relation to the difference between their budget and the valuation of a good rather than its' ratio.
+The study conducted found that the fraction group bid less on average
+than the multiple group. The difference in the means across the two
+groups is around £6, or over 10\% of the budget, signifying that this
+difference occurs due to a systematic difference in how each group
+calculated their value in the foreign currency BlueCoin. The only
+difference between the groups was the exchange rate of BlueCoin to the
+Pound and, as a result, the nominal values of the budget and the bids.
+This would suggest that this difference in bids occurs based on whether
+the foreign currency is a fraction or multiple of the home currency.
 
-Future research could build on this study and its' findings in several important ways: first, it would make sense to conduct a similar or identical study with the BDM mechanism implemented correctly and a greater sample size.
-This would allow for greater certainty that the effect observed is statistically significant and reproducible.
-Further, it would be interesting to investigate the third alternative hypothesis formulated above in order to gain a better understanding into the exact process that leads individuals to systematically under- or overspend when using foreign currencies.
+Above, I outlined the three models for how consumers value goods in a
+foreign currency that have been suggested by previous research. The
+standard model would have predicted that both groups would on average
+bid the same, the model proposed by RAS would have predicted that the
+fraction group would on average bid more than the multiple group and the
+model proposed by WER would have predicted the opposite, namely that the
+fraction group would on average bid less than the multiple group. Hence,
+the third model would have made the most accurate prediction for the
+study conducted.
 
-# References
-::: {#refs}
-:::
+WER (Wertenbroch, Soman, and Chattopadhyay 2007) argue that this
+systematic difference in valuations and spending behaviour occurs
+because consumers are biased by the nominal difference between their
+budget and the product valuation in the foreign currency and thus anchor
+on this value when converting amounts between their home currency and
+foreign currency. In the context of the study, this would entail that
+the fraction group calculated the difference between their budget and
+their bid in BlueCoin and adjusted their bid downwards based on it,
+since this difference will be small (\textless{} 10) in nominal terms.
+The multiple group, on the other hand, would have calculated this
+difference and received a larger amount of surplus for the same product
+valuation in real terms (25 times as large as the fraction group).
+Hence, the multiple group would have adjusted their bid upwards, leading
+to a higher average bid in real (and nominal) terms.
 
-# Appendix {.appendix}
+However, there might be alternative explanations that would be
+consistent with one or more of the other models outlined above. One
+explanation would be that consumers are biased by only the nominal value
+of their budget in the foreign currency and not by the difference
+between their budget and their valuation of a product in the foreign
+currency. While this alternative hypothesis would be hard to prove, it
+would not change the prediction for how the difference in product
+valuations across groups that use either a fraction or multiple
+currency. Indeed, it would predict the exact same result and is this
+consistent with the model proposed by WER, even though it differs in
+explaining the internal work that individuals would do to come to that
+conclusion.
 
-## Experiment Instructions
+Another explanation might be that people are simply worse at dividing
+than multiplying (or the reverse), which could explain the perceived
+differences between the groups. On this explanation, even when consumers
+have the same valuation in real terms, one group will systematically
+fail to accurately convert this value into the foreign currency.
+However, this explanation is unlikely for several reasons. First, this
+claim assumes that a significant amount of people are significantly
+worse at performing one of the operations across all numbers. From
+experience, it seems that when considering most numbers, one of these
+operations is more difficult to do but it is not always the same one.
+Secondly, this assumes that people are unaware enough of their
+difficulties (even when they are very significant) that they do not use
+a calculator even when one is easily accessible, such as when completing
+the survey for this study online. For these reasons, this explanation
+seems unlikely to be accurate.
 
-The full experiment instructions can be found as screenshots at [https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions](https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions).
+A third contending explanation could be that individuals simply prefer
+whole numbers over fractions or decimals, leading consumers to make less
+granular valuation choices when considering a currency with a low face
+value. Because of this, there can be differences in groups of
+individuals if, for example, many participants choose to round down. For
+example, it could have been the case that the average valuation of the
+good in the fraction group was 24 but if a significant amount of
+participants rounded this down to the nearest whole number in BlueCoin
+(4), then this average valuation would now be 20. This explanation can
+be supported empirically, given that only 3 bids out of 41 were decimal
+numbers. One might also claim that this behaviour of preferring whole
+numbers is rational, given that it requires less mental effort,
+especially when multiplying and dividing these numbers. Further research
+is required to determine whether this hypothesis could explain the
+observed behaviour, either entirely or in conjunction with one of the
+models proposed above.
 
-## Source Code
+The former two of these alternative explanations seem unlikely, but the
+latter seems like it could be accurate at least to some extent.
+Nonetheless, it seems like the model proposed by WER is the most
+accurate in predicting and explaining the perceived behaviour when
+formulating valuations of goods in different foreign currencies.
 
-The full source code of the paper and the data analysis can be found at [https://github.com/kopy-kat/virtual-currencies-paper](https://github.com/kopy-kat/virtual-currencies-paper).
+\section{Limitations, Theoretical Implications and Future
+Research}\label{limitations-theoretical-implications-and-future-research}
+
+The main limitation of the study conducted is that due to small sample
+size, the results are not statistically significant at the 5\% level and
+the power of the t-test for a difference in means is only 22\%. Hence,
+even though the observations line up with the model proposed by WER, it
+could be the case that this result is due to random chance. In repeating
+this study, it would be useful to get a sample size of at least 200
+participants to roughly achieve a power of 80\% and likely also
+statistical significance in conducting the t-test. The second major
+limitation is that the BDM mechanism was implemented incorrectly,
+entailing that the dominant strategy for participants was not to reveal
+their true valuations on the good. In a redo, this mistake could be
+fixed relatively easily by adjusting the experiment instructions.
+
+Apart from the limitations, the major theoretical implication of this
+paper is the finding that the model proposed by WER (Wertenbroch, Soman,
+and Chattopadhyay 2007) seems to be most accurate in predicting and
+explaining consumer behaviour when eliciting a WTP on a good. In line
+with these authors, this conclusion contradicts the findings of the
+``face value effect'' by RAS (Raghubir and Srivastava 2002) and
+subsequently by Fang (Fang 2019). Further, this conclusion implies that,
+contrary to traditional consumption theory, individuals formulate their
+WTP in relation to the difference between their budget and the valuation
+of a good rather than its' ratio.
+
+Future research could build on this study and its' findings in several
+important ways: first, it would make sense to conduct a similar or
+identical study with the BDM mechanism implemented correctly and a
+greater sample size. This would allow for greater certainty that the
+effect observed is statistically significant and reproducible. Further,
+it would be interesting to investigate the third alternative hypothesis
+formulated above in order to gain a better understanding into the exact
+process that leads individuals to systematically under- or overspend
+when using foreign currencies.
+
+\chapter{References}\label{references}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-Fang2019}
+Fang, Justin. 2019. {`In-Game Currency Design and Consumer Spending
+Behavior'}. Bachelor\textquotesingle s Thesis, Ross School of Business,
+University of Michigan.
+\url{https://deepblue.lib.umich.edu/bitstream/handle/2027.42/155343/Justin\%20Fang_BA\%20480\%20Written\%20Report.pdf}.
+
+\bibitem[\citeproctext]{ref-Raghubir2002}
+Raghubir, Priya, and Joydeep Srivastava. 2002. {`{Effect of Face Value
+on Product Valuation in Foreign Currencies}'}. \emph{Journal of Consumer
+Research} 29 (3): 335--47. \url{https://doi.org/10.1086/344430}.
+
+\bibitem[\citeproctext]{ref-Wertenbroch2007}
+Wertenbroch, Klaus, Dilip Soman, and Amitava Chattopadhyay. 2007. {`{On
+the Perceived Value of Money: The Reference Dependence of Currency
+Numerosity Effects}'}. \emph{Journal of Consumer Research} 34 (1):
+1--10. \url{https://doi.org/10.1086/513041}.
+
+\end{CSLReferences}
+
+\chapter{Appendix}\label{appendix}
+
+\section{Experiment Instructions}\label{experiment-instructions}
+
+The full experiment instructions can be found as screenshots at
+\url{https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions}.
+
+\section{Source Code}\label{source-code}
+
+The full source code of the paper and the data analysis can be found at
+\url{https://github.com/kopy-kat/virtual-currencies-paper}.
+
+\end{document}

### 2024-04-16 data-analysis/model.R

@@ -32,22 +32,29 @@ t.test(
 # Conduct a regression analysis to examine the relationship between
 # the bid amounts and the demographic variables
 model_group_fraction <-
-  lm(group_fraction_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+  lm(
+    group_fraction_bid_in_pounds ~ lived_abroad +
+      travel_frequency + expenditure,
     data = experiment_data
   )
 summary(model_group_fraction)
 
 model_group_multiple <-
-  lm(group_multiple_bid_in_pounds ~ lived_abroad + travel_frequency + expenditure,
+  lm(
+    group_multiple_bid_in_pounds ~ lived_abroad +
+      travel_frequency + expenditure,
     data = experiment_data
   )
 summary(model_group_multiple)
 
-# Conduct a power analysis to determine the power of the t test and
-# sample size required for a power of 0.8 (80%)
+# Calculate the effect size (Cohens D)
 effect_size <- cohensD(
   experiment_data$group_fraction_bid_in_pounds,
   experiment_data$group_multiple_bid_in_pounds
 )
+
+# Find the power of the t test conducted above
 pwr.t2n.test(n1 = 21, n2 = 20, d = effect_size, sig.level = 0.05)
+
+# Find the sample size required to achieve a power of 0.8 (80%)
 pwr.t.test(power = 0.8, d = effect_size, sig.level = 0.05)

### 2024-04-17 paper.qmd
final draft

@@
 It finds that individuals tend to underspend when the foreign currency is less numerous than (a fraction of) the home currency and overspend when the opposite is the case.
+The paper discusses which model is most accurate at predicting and explaining this effect and considers limitations as well as opportunities for future research.
 license: "CC0"
@@
 
-Past experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them.
-Previous research, such as the "money illusion" effect suggests that individuals are biased towards the nominal (or face value) of prices.
-Past research has investigated whether a systemic effect
+Experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them.
+Previous research, such as the "money illusion" effect [@cite] suggests that individuals are biased towards the nominal (or face value) of prices.
+This bias has also been explored in the context foreign currencies, with research finding systematic effects that arise based on the numerousity of values in a foreign currency compared to individuals' home currencies.
+However, previous research is split on how and why this effect occurs.
 
-RAS [@Raghubir2002] examined the effect of using foreign currencies on consumption behaviour and argue that there is a systematic difference in spending behaviour based on the exchange rate of the foreign currency to an individuals' home currency.
+Raghubir and Srivastava [@Raghubir2002] examined the effect of using foreign currencies on consumption behaviour and argue that there is a systematic difference in spending behaviour based on the exchange rate of the foreign currency to an individuals' home currency.
 Specifically, they showed that when a foreign currency is a fraction of the home currency (e.g.
@@
 On the other hand, when the foreign currency is a multiple of the home currency (e.g.
-1 unit in home currency is 5 units in foreign currency) consumers tend to underspend in real terms.^[For consistency, I will use the terms fraction and multiple currencies throughout this paper as defined here.] RAS argue that this effect arises because individuals are anchored on the face value of the foreign currency which influences the exchange rate calculations from and to their home currencies.
-Hence, RAS term the result of this inadequate adjustment the face value effect.
+1 unit in home currency is 5 units in foreign currency) consumers tend to underspend in real terms.^[For consistency, I will use the terms fraction and multiple currencies throughout this paper as defined here.] Raghubir and Srivastava argue that this effect arises because individuals are anchored on the face value of the foreign currency which influences the exchange rate calculations from and to their home currencies.
+Hence, Raghubir and Srivastava term the result of this inadequate adjustment the "face value effect".
 
-WER [@Wertenbroch2007] consider the findings by RAS and reiterate their conclusion that individuals inadequately calculate the values of goods between differnet currencies, leading to systematic differences in spending behaviour based on the exchange rate between the foreign and home currencies.
-However, WER argue that the process of adjustment occurs differently, namely that individuals calculate their valuations of goods based on salient reference points, such as budget constraints.
-Contrary to standard theory, WER argue that consumers care about the difference between a valuation and their budget rather than the ratio of the two.
+Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] consider the findings by Raghubir and Srivastava and reiterate their conclusion that individuals inadequately calculate the values of goods between differnet currencies, leading to systematic differences in spending behaviour based on the exchange rate between the foreign and home currencies.
+However, Wertenbroch, Soman and Chattopadhyay argue that the process of adjustment occurs differently, namely that individuals calculate their valuations of goods based on salient reference points, such as budget constraints.
+Contrary to standard theory, Wertenbroch, Soman and Chattopadhyay argue that consumers care about the difference between a valuation and their budget rather than the ratio of the two.
 In the context of foreign currencies, the nominal value of this difference will diverge, leading to systematic differences in spending behaviour.
-However, the direction of this bias is the exact opposite of the one shown by RAS.
-Specifically, WER show that consumers underspend when the foreign currency is a fraction of the home currency and overspend in the opposite case.
+However, the direction of this bias is the exact opposite of the one shown by Raghubir and Srivastava.
+Specifically, Wertenbroch, Soman and Chattopadhyay show that consumers underspend when the foreign currency is a fraction of the home currency and overspend in the opposite case.
 
-Fang [@Fang2019] further builds on top of the research by RAS and aims to extend it to the domain of "virtual" currencies, which refers to non-fiat currencies that are digital in nature and not controlled and issued by a central bank.
+Fang [@Fang2019] further builds on top of the research by Raghubir and Srivastava and aims to extend it to the domain of "virtual" currencies, which refers to non-fiat currencies that are digital in nature and not controlled or issued by a central bank.
 Examples of virtual currencies include video game (or in-game) currencies, rewards points, airmiles, cryptocurrencies and more to the extent that these are at least somewhat liquid.
 Investigating in-game currencies specifically, Fang shows that consumer valuations systematically deviate when using these currencies relative to the home currency.
-Fang's findings correspond with those of RAS and the face value effect.
+Fang's findings correspond with those of Raghubir and Srivastava and the face value effect.
 
@@
 These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@cite].
-Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] RAS [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
+Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] Raghubir and Srivastava [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
 For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation".
 Similarly, Fang [@Fang2019] noted that implementing the BDM mechanism was infeasible for the study he conducted but that future research should focus on using something like it to elicit WTP.
-Finally, this paper aims to extend the previous literature on the effects of using virtual currencies specifically, due to their increasing rise in importance when transacting or making purchasing decisions online.
+Finally, this paper aims to extend the previous literature on the effects of using virtual currencies specifically, due to their increasing rise in importance when transacting or making purchasing decisions online, and determine whether spending behaviour differs when using them.
 
-First, I present the theoretical frameworks that have been outlined by previous research in a way that makes it easy to compare and contrast them.
-These frameworks are the standard model described in consumer choice theory, the model suggested by RAS and the model suggested by WER.
+First, I present the theoretical frameworks that have been outlined by previous research in a standard form that makes it easy to compare and contrast them.
+These frameworks are the standard model described in consumer choice theory, the model suggested by Raghubir and Srivastava and the model suggested by Wertenbroch, Soman and Chattopadhyay.
 Then, I consider what each of these frameworks would predict in a concrete case and show that all three models come to different and mutually exclusive conclusions.
-In order to test which of these frameworks is most accurate in predicting observed behaviour, I conduct a study in which two groups each formulate their WTP for a specific good in an incentive compatible way, with the only difference between the groups being the exchange rate of the currency used to their home currency and, as a result, the face values of their budget and bid.
-Analysing the study, I find that consumers tend to underspend when the foreign currency is a fraction and overspend when the foreign currency is a multiple, which is predicted by the module proposed by WER.
-However, due to the limited sample size of the study, this result is not statistically significant and does not have significant power.
-Finally, in the discussion, I will evaluate the implications of the findings for the theoretical frameworks outlined, consider alternative explanations for the perceived effect and argue that the model proposed by WER is the most accurate in predicting and describing consumer behaviour when using foreign currencies.
+In order to test which of these frameworks is most accurate in predicting observed behaviour, I conduct a study in which two groups each formulate their WTP for a specific good in an incentive compatible way, with the only difference between the groups being the exchange rate of the currency used to their home currency and, as a result, the numerousity of the values of their budget and bid.
+Analysing the study, I find that consumers tend to underspend when the foreign currency is a fraction and overspend when the foreign currency is a multiple, which is predicted by the model proposed by Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007].
+However, due to the limited sample size of the study, this result is not statistically significant and does not have significant statistical power.
+In the discussion, I evaluate the implications of the findings for the theoretical frameworks outlined, consider alternative explanations for the perceived effect and argue that the model proposed by Wertenbroch, Soman and Chattopadhyay is the most accurate in predicting and describing consumer behaviour when using foreign currencies.
+Finally, I will consider the limitations of this paper and opportunities for further research.
 
@@
 Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@cite].
-Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio with the budget in order to determine what proportion of their spending power is required to purchase the good.
-To formaulate valuations of goods in a different currency, consumers would first determine the value of the good in their home currency and subsequently apply the exchange rate to get their valuation in the foreign currency.
+Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio to their budget in order to determine what proportion of their spending power is required to purchase the good.
+To formulate valuations of goods in a different currency, consumers would first determine the value of the good in their home currency and subsequently apply the exchange rate to get their valuation in the foreign currency.
 Hence, the model follows a two step process:
 
-1. Formaulate valuation of good as ratio to budget in home currency
+1. Formulate valuation of good as ratio to budget in home currency
 2. Convert the valuation into foreign currency
@@
 
-where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_n$ is the budget in the home currency, X is the exchange rate and $f(x)$ is some function that uses a valuation relative to the budget in order to compute $V_n$.
+where V is the valuation of the good in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_n$ is the budget in the home currency, X is the exchange rate and $f(x)$ is some function that uses a valuation relative to the budget in order to compute $V_n$.
+Note that $V_r$ is simply $V_n$ multiplied by the exchange rate, whereas V need not always be identical to $V_r$.
 
@@
 For example, when exchange rates fluctuate it might not be worth the effort of a consumer to always use the most up-to-date exchange rate, but rather to use some approximate value.
-Further, when an individual needs to do these exchange rate calculations in their head, it might not be worth the mental effort to calculate the amount in the foreign currency perfectly, but an approximation might be fine.
+Further, when an individual needs to do these exchange rate calculations in their head, it might not be worth the mental effort to calculate the amount in the foreign currency perfectly, but an approximation might suffice.
 For example, it would be rational to multiply an amount in home currency by 1.2 if the real exchange rate is 1.2113248 and the effort required is significant, such as when attempting to calculate it in one's hand.
@@
 
-RAS [@Raghubir2002] put forth a different model for how consumers formulate their valuation of a good in a foreign currency based on their studies conducted.
+Raghubir and Srivastava [@Raghubir2002] put forth a different model for how consumers formulate their valuation of a good in a foreign currency based on their studies conducted.
 Specifically, they pose that a consumer will first formulate a valuation of a good in their home currency, before converting that amount into the foreign currency using the exchange rate.
@@
 
-where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency and α is a weighting parameter such that $α ∈[0,1]$.
-Importantly, RAS [@Raghubir2002] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $V_n$.
+where α is a weighting parameter such that $α ∈[0,1]$. Importantly, Raghubir and Srivastava [@Raghubir2002] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $V_n$.
 
@@
 
-WER [@Wertenbroch2007] build on top of RAS, but put forth a different model that they argue is more representative of the behaviour of actual consumers.
-Specifically, they agree with the standard model that valuations are made in relation to salient reference points, such as a consumers' budget, and argue that the model put forth by RAS fails to account for this.
+Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] build on top of Raghubir and Srivastava, but put forth a different model that they argue is more representative of the behaviour of actual consumers.
+Specifically, they agree with the standard model that valuations are made in relation to salient reference points, such as a consumers' budget, and argue that the model put forth by Raghubir and Srivastava fails to account for this.
 However, they disagree with the standard model that valuations use a ratio of price to budget, but instead argue that consumers think in terms of differences.
 Hence, instead of considering what fraction of their purchasing power is required to buy a good, consumers consider how much of their budget is left over.
-However, WER argue that consumers inadequately adjust this difference to the exchange rate and are thus biased when considering goods in different currencies since the nominal differences between price and budget will differ when considering different currencies.
+However, Wertenbroch, Soman and Chattopadhyay argue that consumers inadequately adjust this difference to the exchange rate and are thus biased when considering goods in different currencies since the nominal differences between price and budget will differ when considering different currencies.
 This model can be formulated as follows:
 
-1. Formaulate valuation of good as difference to budget in home currency
+1. Formulate valuation of good as difference to budget in home currency
 2. Convert the valuation into foreign currency
@@
 
-where V is the valuation in the foreign currency, $V_n$ is the valuation of the good in the home currency (nominal), $V_r$ is the valuation of the good in the foreign currency, $M_r$ is the budget in the foreign currency (real) and α is a weighting parameter such that $α ∈[0,1]$.
-Importantly, WER [@Wertenbroch2007] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $M_r - V_r$.
+where $M_r$ is the budget in the foreign currency (real).
+Importantly, Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] argue that $α > 0$ and that V is hence not equal to $V_r$ but is biased towards $M_r - V_r$.
 
@@
 
-The three different models laid out above would each generate a different prediction in the following scenario, considering fraction and multiple exchange rates (the latter in brackets): a consumer values a good at £25 and needs to express this valuation in BlueCoin.
+The three different models laid out above would each generate a different prediction in the following scenario, considering fraction and multiple exchange rates (the latter in brackets): a consumer values a good at £25 and needs to express this valuation in BlueCoin, a fictional currency.
 The exchange rate of Pounds to BlueCoin is 1 BlueCoin = £5 (1 BlueCoin = £0.2) and their budget is 10 (250) BlueCoin.
@@
 - Perceived value of money model: $V_r < 5 (> 125) BlueCoin$
-
-where $V_r$ is the valuation of the good in the foreign currency.
 
@@
 
-In other words, the standard model would expect the valuations to be the same across both exchange rates, the face value effect model would expect the consumer to overspend when presented with the fraction exchange rate and the perceived value of money model would expect the consumer to underspend when presented with the fraction exchange rate.
+In other words, the standard model would expect the valuations to be the same across both exchange rates, the face value effect model would expect the consumer to overspend when presented with the fraction exchange rate (and vice-versa) and the perceived value of money model would expect the consumer to underspend when presented with the fraction exchange rate (and vice-versa).
 
@@
 
-There were 41 participants of the study, most of them current undergraduate students at the University of Oxford, but some participants were also recent graduates and postgraduate students.
+To test which model is most accurate in predicting and explaining consumption behaviour, I conducted an online study.
+There were 41 participants in the study, most of them current undergraduate students at the University of Oxford, but some participants were also recent graduates and postgraduate students.
 The study took place online, using Qualtrics, and students were incentivised to participate by taking part in a lottery, which will be explained in further detail below.
@@
 
-The study itself was split into four parts: Consent Form, Introduction, Auction and Follow-Up Questions.
+The study itself was a survey split into four parts: consent, introduction, auction and follow-up Questions.
 The entire experiment instructions can be found in the Experiment Instructions section of the Appendix.
@@
 In the introductory section, the BDM mechanism was explained to participants and they were asked to complete four question that tested their understanding of the mechanism.
-The aim of this section was to ensure that participants properly understood how the mechanism worked in order to elicit their real WTP during the main part of the study.
+The aim of this section was to ensure that participants properly understood how the mechanism worked in order to elicit their true WTP during the main part of the study.
 
-The auction was the main part of the study, with the aim of eliciting the participants' WTP on a specific item and comparing these across different currencies used.
+The auction was the main part of the study, with the aim of eliciting the participants' WTP on a specific item and comparing these across different exchange rates used.
 In this section, participants were randomly split into two groups with almost-identical instructions.
-The participants were instructed to bid on the item shown below, a tabletop airhockey table, using the virtual currency "BlueCoin".
-The auction was explained to follow the BDM mechanism and it was also stated that three participants of the experiment would be randomly selected, their auction would be simulated and they would receive the outcome.
+The participants were instructed to bid on an item shown below, a tabletop airhockey table, using the virtual currency "BlueCoin".
+The auction was explained to follow the BDM mechanism and it was also stated that three participants of the experiment would be randomly selected for their auction to be simulated and to receive the outcome (either their budget in Pounds or the item and remaining budget).
 The only difference between the groups was the exchange rate between BlueCoin and the British Pound (£) and the endowment that the participants received in BlueCoin.
@@
 
-Since the aim of the study was to determine whether there were any systematic differences in WTP between consumers when the only differing factor is the currency used, we decided to not include a control group that bid on the item using Pounds, which was the design of some of the experiments run by RAS [@Raghubir2002].
+Since the aim of the study was to determine whether there were any systematic differences in WTP between consumers when the only differing factor is the numerousity of the currency used, I decided to not include a control group that bid on the item using Pounds, which was the design of some of the experiments run by Raghubir and Srivastava [@Raghubir2002].
 This allowed for a simpler design and more power given the same sample size.
-Further, unlike the studies run by RAS [@Raghubir2002] and WER [@Wertenbroch2007], we did not use a fiat currency or mix of fiat and fictional currencies, but used only one fictional currency for both groups.
+Further, unlike the studies run by Raghubir and Srivastava [@Raghubir2002] and Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007], I did not use a fiat currency or mix of fiat and virtual currencies, but used only one virtual currency for both groups.
 On the one hand, this simplification was due to a focus of wether the effects described in previous papers also held in similar ways for virtual currencies.
-On the other hand, it also allowed us to preclude any biases or previous experience that participants might have had towards or with certain currencies.
-RAS [@Raghubir2002] acknowledge that "the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency ...
+On the other hand, it also allowed me to preclude any biases or previous experience that participants might have had towards or with certain currencies.
+Raghubir and Srivastava [@Raghubir2002] acknowledge that "the face value effect is due to the accessibility and perceptual salience of the face value of the foreign currency ...
 [which] is likely to depend on the extent to which an individual has the opportunity or the time available to process exchange rate information and/or has experience in using a particular foreign currency".
-To bias participants the least, we chose the relatively nondescript name for a fictional, virtual currency: BlueCoin.
+Further, Alter and Oppenheimer [@Alter2008] show that people use "familiarity and fluency" when valuing goods in different currencies.
+To bias participants the least, I chose the relatively nondescript name for a fictional, virtual currency: BlueCoin.
 
 Another important decision in the design of the experiment was which item to select that a majority of participants would have a non-zero WTP.
-This is important since if the majority or even the entirety of participants were to bid zero on the item, then we would only learn that this was the participants' WTP for that good, but not whether there are any systematic differences in the WTP when using different currencies.
-Hence, we selected a tabletop airhockey table, something that few enough people have so that they won't want another one, but enough people want with a non-zero WTP, especially among a student population.
-In fact, only six participants of the experiment stated a WTP of 0.
+This is important since if the majority or even the entirety of participants were to bid zero on the item, then I would only learn that this was the participants' WTP for that good, but not whether there are any systematic differences in the WTP when using different currencies.
+Hence, I selected a tabletop airhockey table, something that few enough people have so that they would not not want another one, but enough people want with a non-zero WTP, especially among a student population.
+This turned out to be a good choice, since only six participants of the experiment stated a WTP of 0.
 
-In designing the main part of the experiment, we chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP.
+In designing the main part of the experiment, I chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP.
 The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@cite].
-As mentioned above, the studies conducted by RAS [@Raghubir2002], WER [@Wertenbroch2007] (with the exception of one permutation of one of the studies) and Fang [@Fang2019] did not implement incentive-compatible methods of eliciting the participants' preferences, making this experiment and important addition to these previous studies in examining whether the effects describe still hold when a more accurate way of eliciting WTP is used.
-In order to incentivise the participants even further, we ran a lottery that paid out three randomly-chosen participants based on their actual choices made in the auction and by simulating the BDM mechanism using a random number generator.
-Due to budget constraints, we were only able to play this lottery for three people, but given that the sample size of the experiment was relatively small, the potential to receive one's outcome is likely to have helped in eliciting the participants' true WTP.
+The BDM is essentially a sealed-bid, second price auction that is, in its' most common variant, played against a computer drawing a bid from a known distribution.
+If the players' bid is greater than or equal to the computers' bid, they win and pay the computers' bid, otherwise they lose.
+As mentioned above, the studies conducted by Raghubir and Srivastava [@Raghubir2002], Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] (with the exception of one permutation of one of the studies) and Fang [@Fang2019] did not implement incentive-compatible methods of eliciting the participants' preferences, making this experiment an important addition to these previous studies in examining whether the effects described still hold when a more truthful way of eliciting WTP is used.
+In order to incentivise the participants to participate, I ran a lottery that paid out three randomly-chosen participants based on their actual choices made in the auction and by simulating the BDM mechanism using a random number generator.
+Due to budget constraints, I was only able to play this lottery for three people, but given that the sample size of the experiment was relatively small, the potential to receive one's outcome is likely to have helped in eliciting the participants' true WTP.
 
-Finally, given our budget, we were able to give participants an endowment of £50 each, which was around double of what the item costs to buy.
-Assuming that the item is priced roughly around the average WTP (which turned out to be correct), this endowment was chosen to leave enough room for people with higher WTP to make their bid and for us to capture this in the data.
-This is important for the goals of the experiment, since if we had, for example, chosen an endowment of £20, the majority of participants might have bid their maximum amount, hindering our ability to meaningfully compare WTP across the two groups.
-We chose relatively simple exchange rates of 5 and $1/5$ so that the exchange rate calculations would be relatively easy to make, allowing us to be more confident that differences between groups were not due to the mental effort required to do calculations but due to something else.
-RAS [@Raghubir2002] acknowledge that "the reliance on face value may be a function of the ease with which the foreign money can be converted.
+Finally, given the budget, I was able to give participants an endowment of £50 each, which was around double of what the item costs to buy.
+Assuming that the item is priced roughly around the average WTP (which turned out to be correct), this endowment was chosen to leave enough room for people with higher WTP to make their bid and to capture this in the data.
+This is important for the goals of the experiment, since if I had, for example, chosen an endowment of £20, the majority of participants might have bid their maximum amount, hindering my ability to meaningfully compare WTP across the two groups.
+I chose relatively simple exchange rates of 5 and $1/5$ so that the exchange rate calculations would be relatively easy to make, allowing me to be more confident that differences between groups were not due to the mental effort required to do calculations but due to something else.
+Raghubir and Srivastava [@Raghubir2002] acknowledge that "the reliance on face value may be a function of the ease with which the foreign money can be converted.
 ...
 Future research should examine the asymmetric and nonlinear nature of this effect".
-Since the goal of this study is to investigate that an effect exists that is not solely based on a high difficulty or large mental effort required when doing specific, difficult calculations, we aimed to make the calculations as easy as possible in order to isolate the effect of the exchange rate and nominal value of the foreign currency.
+Since the goal of this study is to investigate that an effect exists that is not solely based on a high difficulty or large mental effort required when doing specific, difficult calculations, I aimed to make the calculations as easy as possible in order to isolate the effect of the exchange rate and nominal value of the foreign currency.
+Further, since the study was conducted online, participants were easily able to and allowed to use calculators for any part.
 
@@
 
-In setting up the experiment, we incorrectly used the BDM mechanism.
+In setting up the experiment, I incorrectly used the BDM mechanism.
 Instead of explaining it as a sealed-bid second-price auction, the experiment instructions explained it as a sealed-bid first-price auction.
-Unlike in a second-price auction, the participants of a first price auction do not have a dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@cite].
-[@todo]
+Unlike in a second-price auction, the participants of a first price auction do not have a (weakly) dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@cite].
+This is true even in this auction in which participants knew that they were bidding against a computer agent who would randomly draw a bid from a uniform distribution from 0-50, with an expected bid of 25.
+Indeed, the optimal strategy by participants was to choose their bid b by maximising their payoff p:
+
+$$\frac{b}{50} * u(x = 1, 50 - b) + (1 - \frac{b}{50}) * u(x = 0, 50)$$
+
+where u(x, m) is their utility function, x is a binary variable where x = 1 signifies owning the good (and vice-versa) and m = 50 is their budget (in Pounds).
+As is obvious, the value of b depends on the participants' utility function.
+Hence, while players in this auction need not necessarily have the optimal strategy of telling their true valuation, sufficient randomisation should ensure that the utility functions of agents in each group should be evenly distributed.
+This would entail that we can nonetheless compare bids across both groups.
 
@@
 High power would indicate that this likelihood is high and vice versa.
-To conduct the analysis, we first need to find the effect size, or Cohen's D and then implement the power analysis.
-Further, I will also conduct an analysis that investigates how big the sample size should have been to get a power of 80%.
+To conduct the analysis, we first need to find the effect size, or Cohen's D, and then implement the power analysis.
+Further, I will also conduct an analysis that investigates how big the sample size should have been to get a power of 80%, which is a generally accepted threshold for significant power.
 
@@
 The coefficient of -43.487 suggests that people whose usual expenditure is between £551 and £700 per month bid lower than the group overall.
-However, given that this is only significant at the 10% level and not at any lower ones, it is likely that this correlation is due to the low sample size rather than representing a true correlation between these variables.
+However, given that this is only significant at the 10% level and not at any lower ones, it is likely that this correlation is due to the low sample size rather than it representing a true correlation between these variables.
 
@@
 The study conducted found that the fraction group bid less on average than the multiple group.
-The difference in the means across the two groups is around £6, or over 10% of the budget, signifying that this difference occurs due to a systematic difference in how each group calculated their value in the foreign currency BlueCoin.
-The only difference between the groups was the exchange rate of BlueCoin to the Pound and, as a result, the nominal values of the budget and the bids.
+The difference in the means across the two groups is around £6, or over 10% of the budget, signifying that this difference occurs due to a systematic difference in how each group calculated their value in the foreign currency BlueCoin rather than random chance.
+The only difference between the groups was the exchange rate of BlueCoin to the Pound and, as a result, the numerousity of the nominal values of the budget and the bids.
 This would suggest that this difference in bids occurs based on whether the foreign currency is a fraction or multiple of the home currency.
@@
 Above, I outlined the three models for how consumers value goods in a foreign currency that have been suggested by previous research.
-The standard model would have predicted that both groups would on average bid the same, the model proposed by RAS would have predicted that the fraction group would on average bid more than the multiple group and the model proposed by WER would have predicted the opposite, namely that the fraction group would on average bid less than the multiple group.
+The standard model would have predicted that both groups would on average bid the same, the model proposed by Raghubir and Srivastava [@Raghubir2002] would have predicted that the fraction group would on average bid more than the multiple group and the model proposed by Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] would have predicted the opposite, namely that the fraction group would on average bid less than the multiple group.
 Hence, the third model would have made the most accurate prediction for the study conducted.
 
-WER [@Wertenbroch2007] argue that this systematic difference in valuations and spending behaviour occurs because consumers are biased by the nominal difference between their budget and the product valuation in the foreign currency and thus anchor on this value when converting amounts between their home currency and foreign currency.
+Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] argue that this systematic difference in valuations and spending behaviour occurs because consumers are biased by the nominal difference between their budget and the product valuation in the foreign currency and thus anchor on this value when converting amounts between their home currency and foreign currency.
 In the context of the study, this would entail that the fraction group calculated the difference between their budget and their bid in BlueCoin and adjusted their bid downwards based on it, since this difference will be small (< 10) in nominal terms.
@@
 While this alternative hypothesis would be hard to prove, it would not change the prediction for how the difference in product valuations across groups that use either a fraction or multiple currency.
-Indeed, it would predict the exact same result and is this consistent with the model proposed by WER, even though it differs in explaining the internal work that individuals would do to come to that conclusion.
+Indeed, it would predict the exact same result and is thus consistent with the model proposed by Wertenbroch, Soman and Chattopadhyay, even though it differs in explaining the internal work that individuals would do to come to that conclusion.
 
@@
 However, this explanation is unlikely for several reasons.
-First, this claim assumes that a significant amount of people are significantly worse at performing one of the operations across all numbers.
+First, it assumes that a significant amount of people are significantly worse at performing one of the operations across all numbers.
 From experience, it seems that when considering most numbers, one of these operations is more difficult to do but it is not always the same one.
@@
 
-A third contending explanation could be that individuals simply prefer whole numbers over fractions or decimals, leading consumers to make less granular valuation choices when considering a currency with a low face value.
-Because of this, there can be differences in groups of individuals if, for example, many participants choose to round down.
-For example, it could have been the case that the average valuation of the good in the fraction group was 24 but if a significant amount of participants rounded this down to the nearest whole number in BlueCoin (4), then this average valuation would now be 20.
+A third contending explanation could be that individuals simply prefer to use whole numbers over fractions or decimals, leading consumers to make less granular valuation choices when considering a currency with a low face value.
+Because of this, there can be differences in groups of individuals if, for example, many participants in the same group choose to round down.
+For example, it could have been the case that the average valuation of the good in the fraction group was £24 but if a significant amount of participants rounded this down to the nearest whole number in BlueCoin (4), then this average valuation would now be 20.
 This explanation can be supported empirically, given that only 3 bids out of 41 were decimal numbers.
@@
 The former two of these alternative explanations seem unlikely, but the latter seems like it could be accurate at least to some extent.
-Nonetheless, it seems like the model proposed by WER is the most accurate in predicting and explaining the perceived behaviour when formulating valuations of goods in different foreign currencies.
+Without further research, however, it seems like the model proposed by Wertenbroch, Soman and Chattopadhyay is the most accurate in predicting and explaining the perceived behaviour when formulating valuations of goods in different foreign currencies.
 
@@
 The main limitation of the study conducted is that due to small sample size, the results are not statistically significant at the 5% level and the power of the t-test for a difference in means is only 22%.
-Hence, even though the observations line up with the model proposed by WER, it could be the case that this result is due to random chance.
+Hence, even though the observations line up with the model proposed by Wertenbroch, Soman and Chattopadhyay, it could be the case that this result is due to random chance.
 In repeating this study, it would be useful to get a sample size of at least 200 participants to roughly achieve a power of 80% and likely also statistical significance in conducting the t-test.
-The second major limitation is that the BDM mechanism was implemented incorrectly, entailing that the dominant strategy for participants was not to reveal their true valuations on the good.
+The second major limitation is that the BDM mechanism was implemented incorrectly, entailing that there was no dominant strategy for participants to reveal their true valuations on the good.
 In a redo, this mistake could be fixed relatively easily by adjusting the experiment instructions.
 
-Apart from the limitations, the major theoretical implication of this paper is the finding that the model proposed by WER [@Wertenbroch2007] seems to be most accurate in predicting and explaining consumer behaviour when eliciting a WTP on a good.
-In line with these authors, this conclusion contradicts the findings of the "face value effect" by RAS [@Raghubir2002] and subsequently by Fang [@Fang2019].
-Further, this conclusion implies that, contrary to traditional consumption theory, individuals formulate their WTP in relation to the difference between their budget and the valuation of a good rather than its' ratio.
+Apart from the limitations, the major theoretical implication of this paper is the finding that the model proposed by Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] seems to be most accurate in predicting and explaining consumer behaviour when eliciting a WTP on a good in a foreign currncy.
+In line with these authors, this conclusion contradicts the findings of the "face value effect" by Raghubir and Srivastava [@Raghubir2002] and subsequently by Fang [@Fang2019].
+Further, this conclusion also implies that, contrary to traditional consumption theory, individuals formulate their WTP in relation to the difference between their budget and the valuation of a good rather than its' ratio.
 
@@
 Further, it would be interesting to investigate the third alternative hypothesis formulated above in order to gain a better understanding into the exact process that leads individuals to systematically under- or overspend when using foreign currencies.
+It might, however, be difficult to conduct an adequate study to accurately test that claim.
 
@@
 
-The full experiment instructions can be found as screenshots at [https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions](https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions).
+![Consent](experiment_instructions/consent.png)
+
+![Instructions](experiment_instructions/instructions.png)
+
+![Auction: Fraction Group](experiment_instructions/auction_fraction.png)
+
+![Auction: Multiple Group](experiment_instructions/auction_multiple.png)
+
+![Follow up](experiment_instructions/follow_up.png)
 
@@
 
-The full source code of the paper and the data analysis can be found at [https://github.com/kopy-kat/virtual-currencies-paper](https://github.com/kopy-kat/virtual-currencies-paper).
+The full source code of the data analysis is follows:
+
+```r
+# Load the required libraries
+library(pwr)
+library(lsr)
+
+# Load the experiment data
+experiment_data <-
+  read.csv("virtual-currencies-paper/data/experiment_data_formatted.csv")
+
+# Summary statistics for the bid columns
+summary(experiment_data$group_fraction_bid_in_pounds)
+sd(experiment_data$group_fraction_bid_in_pounds, na.rm = TRUE)
+
+summary(experiment_data$group_multiple_bid_in_pounds)
+sd(experiment_data$group_multiple_bid_in_pounds, na.rm = TRUE)
+
+# Plot a boxplot for the bid columns
+boxplot(
+  experiment_data$group_fraction_bid_in_pounds,
+  experiment_data$group_multiple_bid_in_pounds,
+  main = "Boxplot of fraction and multiple group bids (in Pounds)",
+  names = c("Group Fraction", "Group Multiple"),
+  xlab = "Variables",
+  ylab = "Values"
+)
+
+# Perform a t-test to compare the means of the two groups
+t.test(
+  experiment_data$group_fraction_bid_in_pounds,
+  experiment_data$group_multiple_bid_in_pounds
+)
+
+# Conduct a regression analysis to examine the relationship between
+# the bid amounts and the demographic variables
+model_group_fraction <-
+  lm(
+    group_fraction_bid_in_pounds ~ lived_abroad +
+      travel_frequency + expenditure,
+    data = experiment_data
+  )
+summary(model_group_fraction)
+
+model_group_multiple <-
+  lm(
+    group_multiple_bid_in_pounds ~ lived_abroad +
+      travel_frequency + expenditure,
+    data = experiment_data
+  )
+summary(model_group_multiple)
+
+# Calculate the effect size (Cohens D)
+effect_size <- cohensD(
+  experiment_data$group_fraction_bid_in_pounds,
+  experiment_data$group_multiple_bid_in_pounds
+)
+
+# Find the power of the t test conducted above
+pwr.t2n.test(n1 = 21, n2 = 20, d = effect_size, sig.level = 0.05)
+
+# Find the sample size required to achieve a power of 0.8 (80%)
+pwr.t.test(power = 0.8, d = effect_size, sig.level = 0.05)
+```

### 2024-04-17 paper.tex
final draft

@@
 \fi
+
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{241,243,245}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
+\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
 
@@
 numerous than (a fraction of) the home currency and overspend when the
-opposite is the case.
+opposite is the case. The paper discusses which model is most accurate
+at predicting and explaining this effect and considers limitations as
+well as opportunities for future research.
 \end{abstract}
@@
 
-Past experience suggests that we treat foreign currencies differently to
-our home currency and have difficulty adjusting to them. Previous
-research, such as the ``money illusion'' effect suggests that
+Experience suggests that we treat foreign currencies differently to our
+home currency and have difficulty adjusting to them. Previous research,
+such as the ``money illusion'' effect (\textbf{cite?}) suggests that
 individuals are biased towards the nominal (or face value) of prices.
-Past research has investigated whether a systemic effect
-
-RAS (Raghubir and Srivastava 2002) examined the effect of using foreign
-currencies on consumption behaviour and argue that there is a systematic
-difference in spending behaviour based on the exchange rate of the
-foreign currency to an individuals' home currency. Specifically, they
-showed that when a foreign currency is a fraction of the home currency
-(e.g.~1 unit in home currency is 0.2 units in foreign currency)
-consumers tend to overspend in real terms relative to their home
-currency. On the other hand, when the foreign currency is a multiple of
-the home currency (e.g.~1 unit in home currency is 5 units in foreign
-currency) consumers tend to underspend in real terms.\footnote{For
-  consistency, I will use the terms fraction and multiple currencies
-  throughout this paper as defined here.} RAS argue that this effect
-arises because individuals are anchored on the face value of the foreign
-currency which influences the exchange rate calculations from and to
-their home currencies. Hence, RAS term the result of this inadequate
-adjustment the face value effect.
-
-WER (Wertenbroch, Soman, and Chattopadhyay 2007) consider the findings
-by RAS and reiterate their conclusion that individuals inadequately
-calculate the values of goods between differnet currencies, leading to
-systematic differences in spending behaviour based on the exchange rate
-between the foreign and home currencies. However, WER argue that the
-process of adjustment occurs differently, namely that individuals
-calculate their valuations of goods based on salient reference points,
-such as budget constraints. Contrary to standard theory, WER argue that
+This bias has also been explored in the context foreign currencies, with
+research finding systematic effects that arise based on the numerousity
+of values in a foreign currency compared to individuals' home
+currencies. However, previous research is split on how and why this
+effect occurs.
+
+Raghubir and Srivastava (Raghubir and Srivastava 2002) examined the
+effect of using foreign currencies on consumption behaviour and argue
+that there is a systematic difference in spending behaviour based on the
+exchange rate of the foreign currency to an individuals' home currency.
+Specifically, they showed that when a foreign currency is a fraction of
+the home currency (e.g.~1 unit in home currency is 0.2 units in foreign
+currency) consumers tend to overspend in real terms relative to their
+home currency. On the other hand, when the foreign currency is a
+multiple of the home currency (e.g.~1 unit in home currency is 5 units
+in foreign currency) consumers tend to underspend in real
+terms.\footnote{For consistency, I will use the terms fraction and
+  multiple currencies throughout this paper as defined here.} Raghubir
+and Srivastava argue that this effect arises because individuals are
+anchored on the face value of the foreign currency which influences the
+exchange rate calculations from and to their home currencies. Hence,
+Raghubir and Srivastava term the result of this inadequate adjustment
+the ``face value effect''.
+
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) consider the findings by Raghubir and Srivastava and
+reiterate their conclusion that individuals inadequately calculate the
+values of goods between differnet currencies, leading to systematic
+differences in spending behaviour based on the exchange rate between the
+foreign and home currencies. However, Wertenbroch, Soman and
+Chattopadhyay argue that the process of adjustment occurs differently,
+namely that individuals calculate their valuations of goods based on
+salient reference points, such as budget constraints. Contrary to
+standard theory, Wertenbroch, Soman and Chattopadhyay argue that
 consumers care about the difference between a valuation and their budget
@@
 differences in spending behaviour. However, the direction of this bias
-is the exact opposite of the one shown by RAS. Specifically, WER show
-that consumers underspend when the foreign currency is a fraction of the
-home currency and overspend in the opposite case.
-
-Fang (Fang 2019) further builds on top of the research by RAS and aims
-to extend it to the domain of ``virtual'' currencies, which refers to
-non-fiat currencies that are digital in nature and not controlled and
-issued by a central bank. Examples of virtual currencies include video
-game (or in-game) currencies, rewards points, airmiles, cryptocurrencies
-and more to the extent that these are at least somewhat liquid.
-Investigating in-game currencies specifically, Fang shows that consumer
-valuations systematically deviate when using these currencies relative
-to the home currency. Fang's findings correspond with those of RAS and
-the face value effect.
+is the exact opposite of the one shown by Raghubir and Srivastava.
+Specifically, Wertenbroch, Soman and Chattopadhyay show that consumers
+underspend when the foreign currency is a fraction of the home currency
+and overspend in the opposite case.
+
+Fang (Fang 2019) further builds on top of the research by Raghubir and
+Srivastava and aims to extend it to the domain of ``virtual''
+currencies, which refers to non-fiat currencies that are digital in
+nature and not controlled or issued by a central bank. Examples of
+virtual currencies include video game (or in-game) currencies, rewards
+points, airmiles, cryptocurrencies and more to the extent that these are
+at least somewhat liquid. Investigating in-game currencies specifically,
+Fang shows that consumer valuations systematically deviate when using
+these currencies relative to the home currency. Fang's findings
+correspond with those of Raghubir and Srivastava and the face value
+effect.
 
@@
 will be defined and explained in more detail in the Methodology section
-below.{]} RAS (Raghubir and Srivastava 2002) expressed the concern that
-``despite attempts to make the tasks as realistic as possible, the
-studies reported were laboratory experiments, and issues of
-generalizability when real money is on the line do arise. For instance,
-when people actually exchange foreign currency they may feel richer or
-poorer depending on the exchange rate, and the differences in
-perceptions of wealth may affect product valuation''. Similarly, Fang
-(Fang 2019) noted that implementing the BDM mechanism was infeasible for
-the study he conducted but that future research should focus on using
-something like it to elicit WTP. Finally, this paper aims to extend the
-previous literature on the effects of using virtual currencies
-specifically, due to their increasing rise in importance when
-transacting or making purchasing decisions online.
+below.{]} Raghubir and Srivastava (Raghubir and Srivastava 2002)
+expressed the concern that ``despite attempts to make the tasks as
+realistic as possible, the studies reported were laboratory experiments,
+and issues of generalizability when real money is on the line do arise.
+For instance, when people actually exchange foreign currency they may
+feel richer or poorer depending on the exchange rate, and the
+differences in perceptions of wealth may affect product valuation''.
+Similarly, Fang (Fang 2019) noted that implementing the BDM mechanism
+was infeasible for the study he conducted but that future research
+should focus on using something like it to elicit WTP. Finally, this
+paper aims to extend the previous literature on the effects of using
+virtual currencies specifically, due to their increasing rise in
+importance when transacting or making purchasing decisions online, and
+determine whether spending behaviour differs when using them.
 
 First, I present the theoretical frameworks that have been outlined by
-previous research in a way that makes it easy to compare and contrast
-them. These frameworks are the standard model described in consumer
-choice theory, the model suggested by RAS and the model suggested by
-WER. Then, I consider what each of these frameworks would predict in a
-concrete case and show that all three models come to different and
-mutually exclusive conclusions. In order to test which of these
-frameworks is most accurate in predicting observed behaviour, I conduct
-a study in which two groups each formulate their WTP for a specific good
-in an incentive compatible way, with the only difference between the
-groups being the exchange rate of the currency used to their home
-currency and, as a result, the face values of their budget and bid.
-Analysing the study, I find that consumers tend to underspend when the
-foreign currency is a fraction and overspend when the foreign currency
-is a multiple, which is predicted by the module proposed by WER.
-However, due to the limited sample size of the study, this result is not
-statistically significant and does not have significant power. Finally,
-in the discussion, I will evaluate the implications of the findings for
-the theoretical frameworks outlined, consider alternative explanations
-for the perceived effect and argue that the model proposed by WER is the
-most accurate in predicting and describing consumer behaviour when using
-foreign currencies.
+previous research in a standard form that makes it easy to compare and
+contrast them. These frameworks are the standard model described in
+consumer choice theory, the model suggested by Raghubir and Srivastava
+and the model suggested by Wertenbroch, Soman and Chattopadhyay. Then, I
+consider what each of these frameworks would predict in a concrete case
+and show that all three models come to different and mutually exclusive
+conclusions. In order to test which of these frameworks is most accurate
+in predicting observed behaviour, I conduct a study in which two groups
+each formulate their WTP for a specific good in an incentive compatible
+way, with the only difference between the groups being the exchange rate
+of the currency used to their home currency and, as a result, the
+numerousity of the values of their budget and bid. Analysing the study,
+I find that consumers tend to underspend when the foreign currency is a
+fraction and overspend when the foreign currency is a multiple, which is
+predicted by the model proposed by Wertenbroch, Soman and Chattopadhyay
+(Wertenbroch, Soman, and Chattopadhyay 2007). However, due to the
+limited sample size of the study, this result is not statistically
+significant and does not have significant statistical power. In the
+discussion, I evaluate the implications of the findings for the
+theoretical frameworks outlined, consider alternative explanations for
+the perceived effect and argue that the model proposed by Wertenbroch,
+Soman and Chattopadhyay is the most accurate in predicting and
+describing consumer behaviour when using foreign currencies. Finally, I
+will consider the limitations of this paper and opportunities for
+further research.
 
@@
 budget (\textbf{cite?}). Specifically, standard theory poses that
-consumers evaluate their valuation for a good as a ratio with the budget
+consumers evaluate their valuation for a good as a ratio to their budget
 in order to determine what proportion of their spending power is
-required to purchase the good. To formaulate valuations of goods in a
+required to purchase the good. To formulate valuations of goods in a
 different currency, consumers would first determine the value of the
@@
 \item
-  Formaulate valuation of good as ratio to budget in home currency
+  Formulate valuation of good as ratio to budget in home currency
 \item
@@
 
-where V is the valuation in the foreign currency, \(V_n\) is the
-valuation of the good in the home currency (nominal), \(V_r\) is the
+where V is the valuation of the good in the foreign currency, \(V_n\) is
+the valuation of the good in the home currency (nominal), \(V_r\) is the
 valuation of the good in the foreign currency, \(M_n\) is the budget in
@@
 that uses a valuation relative to the budget in order to compute
-\(V_n\).
+\(V_n\). Note that \(V_r\) is simply \(V_n\) multiplied by the exchange
+rate, whereas V need not always be identical to \(V_r\).
 
@@
 it might not be worth the mental effort to calculate the amount in the
-foreign currency perfectly, but an approximation might be fine. For
+foreign currency perfectly, but an approximation might suffice. For
 example, it would be rational to multiply an amount in home currency by
@@
 
-RAS (Raghubir and Srivastava 2002) put forth a different model for how
-consumers formulate their valuation of a good in a foreign currency
-based on their studies conducted. Specifically, they pose that a
-consumer will first formulate a valuation of a good in their home
-currency, before converting that amount into the foreign currency using
-the exchange rate. However, they argue that this calculation is biased
-by the nominal value of the good in the home currency (in cases where a
-consumer does not determine their valuation but observes a price, this
-calculation would be biased by the nominal value of the good in the
-foreign currency). This model may be formulated as follows:
+Raghubir and Srivastava (Raghubir and Srivastava 2002) put forth a
+different model for how consumers formulate their valuation of a good in
+a foreign currency based on their studies conducted. Specifically, they
+pose that a consumer will first formulate a valuation of a good in their
+home currency, before converting that amount into the foreign currency
+using the exchange rate. However, they argue that this calculation is
+biased by the nominal value of the good in the home currency (in cases
+where a consumer does not determine their valuation but observes a
+price, this calculation would be biased by the nominal value of the good
+in the foreign currency). This model may be formulated as follows:
 
@@
 
-where V is the valuation in the foreign currency, \(V_n\) is the
-valuation of the good in the home currency (nominal), \(V_r\) is the
-valuation of the good in the foreign currency and α is a weighting
-parameter such that \(α ∈[0,1]\). Importantly, RAS (Raghubir and
-Srivastava 2002) argue that \(α > 0\) and that V is hence not equal to
-\(V_r\) but is biased towards \(V_n\).
+where α is a weighting parameter such that \(α ∈[0,1]\). Importantly,
+Raghubir and Srivastava (Raghubir and Srivastava 2002) argue that
+\(α > 0\) and that V is hence not equal to \(V_r\) but is biased towards
+\(V_n\).
 
@@
 
-WER (Wertenbroch, Soman, and Chattopadhyay 2007) build on top of RAS,
-but put forth a different model that they argue is more representative
-of the behaviour of actual consumers. Specifically, they agree with the
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) build on top of Raghubir and Srivastava, but put
+forth a different model that they argue is more representative of the
+behaviour of actual consumers. Specifically, they agree with the
 standard model that valuations are made in relation to salient reference
 points, such as a consumers' budget, and argue that the model put forth
-by RAS fails to account for this. However, they disagree with the
-standard model that valuations use a ratio of price to budget, but
-instead argue that consumers think in terms of differences. Hence,
-instead of considering what fraction of their purchasing power is
+by Raghubir and Srivastava fails to account for this. However, they
+disagree with the standard model that valuations use a ratio of price to
+budget, but instead argue that consumers think in terms of differences.
+Hence, instead of considering what fraction of their purchasing power is
 required to buy a good, consumers consider how much of their budget is
-left over. However, WER argue that consumers inadequately adjust this
-difference to the exchange rate and are thus biased when considering
-goods in different currencies since the nominal differences between
-price and budget will differ when considering different currencies. This
-model can be formulated as follows:
+left over. However, Wertenbroch, Soman and Chattopadhyay argue that
+consumers inadequately adjust this difference to the exchange rate and
+are thus biased when considering goods in different currencies since the
+nominal differences between price and budget will differ when
+considering different currencies. This model can be formulated as
+follows:
 
@@
 \item
-  Formaulate valuation of good as difference to budget in home currency
+  Formulate valuation of good as difference to budget in home currency
 \item
@@
 
-where V is the valuation in the foreign currency, \(V_n\) is the
-valuation of the good in the home currency (nominal), \(V_r\) is the
-valuation of the good in the foreign currency, \(M_r\) is the budget in
-the foreign currency (real) and α is a weighting parameter such that
-\(α ∈[0,1]\). Importantly, WER (Wertenbroch, Soman, and Chattopadhyay
-2007) argue that \(α > 0\) and that V is hence not equal to \(V_r\) but
-is biased towards \(M_r - V_r\).
+where \(M_r\) is the budget in the foreign currency (real). Importantly,
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) argue that \(α > 0\) and that V is hence not equal
+to \(V_r\) but is biased towards \(M_r - V_r\).
 
@@
 multiple exchange rates (the latter in brackets): a consumer values a
-good at £25 and needs to express this valuation in BlueCoin. The
-exchange rate of Pounds to BlueCoin is 1 BlueCoin = £5 (1 BlueCoin =
-£0.2) and their budget is 10 (250) BlueCoin. The models above would make
-the following predictions:
+good at £25 and needs to express this valuation in BlueCoin, a fictional
+currency. The exchange rate of Pounds to BlueCoin is 1 BlueCoin = £5 (1
+BlueCoin = £0.2) and their budget is 10 (250) BlueCoin. The models above
+would make the following predictions:
 
@@
 \end{itemize}
-
-where \(V_r\) is the valuation of the good in the foreign currency.
 
@@
 expect the consumer to overspend when presented with the fraction
-exchange rate and the perceived value of money model would expect the
-consumer to underspend when presented with the fraction exchange rate.
+exchange rate (and vice-versa) and the perceived value of money model
+would expect the consumer to underspend when presented with the fraction
+exchange rate (and vice-versa).
 
@@
 
-There were 41 participants of the study, most of them current
-undergraduate students at the University of Oxford, but some
-participants were also recent graduates and postgraduate students. The
-study took place online, using Qualtrics, and students were incentivised
-to participate by taking part in a lottery, which will be explained in
-further detail below.
+To test which model is most accurate in predicting and explaining
+consumption behaviour, I conducted an online study. There were 41
+participants in the study, most of them current undergraduate students
+at the University of Oxford, but some participants were also recent
+graduates and postgraduate students. The study took place online, using
+Qualtrics, and students were incentivised to participate by taking part
+in a lottery, which will be explained in further detail below.
 
@@
 
-The study itself was split into four parts: Consent Form, Introduction,
-Auction and Follow-Up Questions. The entire experiment instructions can
-be found in the Experiment Instructions section of the Appendix. The
-first section asked participants to read through and sign the consent
-form in order to ensure that they were informed about the study and what
-data would be collected. In the introductory section, the BDM mechanism
-was explained to participants and they were asked to complete four
-question that tested their understanding of the mechanism. The aim of
-this section was to ensure that participants properly understood how the
-mechanism worked in order to elicit their real WTP during the main part
-of the study.
+The study itself was a survey split into four parts: consent,
+introduction, auction and follow-up Questions. The entire experiment
+instructions can be found in the Experiment Instructions section of the
+Appendix. The first section asked participants to read through and sign
+the consent form in order to ensure that they were informed about the
+study and what data would be collected. In the introductory section, the
+BDM mechanism was explained to participants and they were asked to
+complete four question that tested their understanding of the mechanism.
+The aim of this section was to ensure that participants properly
+understood how the mechanism worked in order to elicit their true WTP
+during the main part of the study.
 
@@
 the participants' WTP on a specific item and comparing these across
-different currencies used. In this section, participants were randomly
-split into two groups with almost-identical instructions. The
-participants were instructed to bid on the item shown below, a tabletop
+different exchange rates used. In this section, participants were
+randomly split into two groups with almost-identical instructions. The
+participants were instructed to bid on an item shown below, a tabletop
 airhockey table, using the virtual currency ``BlueCoin''. The auction
 was explained to follow the BDM mechanism and it was also stated that
-three participants of the experiment would be randomly selected, their
-auction would be simulated and they would receive the outcome. The only
-difference between the groups was the exchange rate between BlueCoin and
-the British Pound (£) and the endowment that the participants received
-in BlueCoin. The first group received an endowment of 10 BlueCoin where
-1 BlueCoin equals £5 and the second group received an endowment of 250
+three participants of the experiment would be randomly selected for
+their auction to be simulated and to receive the outcome (either their
+budget in Pounds or the item and remaining budget). The only difference
+between the groups was the exchange rate between BlueCoin and the
+British Pound (£) and the endowment that the participants received in
+BlueCoin. The first group received an endowment of 10 BlueCoin where 1
+BlueCoin equals £5 and the second group received an endowment of 250
 BlueCoin where 1 BlueCoin equals £0.2. To complete the auction,
@@
 systematic differences in WTP between consumers when the only differing
-factor is the currency used, we decided to not include a control group
-that bid on the item using Pounds, which was the design of some of the
-experiments run by RAS (Raghubir and Srivastava 2002). This allowed for
-a simpler design and more power given the same sample size. Further,
-unlike the studies run by RAS (Raghubir and Srivastava 2002) and WER
-(Wertenbroch, Soman, and Chattopadhyay 2007), we did not use a fiat
-currency or mix of fiat and fictional currencies, but used only one
-fictional currency for both groups. On the one hand, this simplification
-was due to a focus of wether the effects described in previous papers
-also held in similar ways for virtual currencies. On the other hand, it
-also allowed us to preclude any biases or previous experience that
-participants might have had towards or with certain currencies. RAS
-(Raghubir and Srivastava 2002) acknowledge that ``the face value effect
-is due to the accessibility and perceptual salience of the face value of
-the foreign currency \ldots{} {[}which{]} is likely to depend on the
-extent to which an individual has the opportunity or the time available
-to process exchange rate information and/or has experience in using a
-particular foreign currency''. To bias participants the least, we chose
-the relatively nondescript name for a fictional, virtual currency:
-BlueCoin.
+factor is the numerousity of the currency used, I decided to not include
+a control group that bid on the item using Pounds, which was the design
+of some of the experiments run by Raghubir and Srivastava (Raghubir and
+Srivastava 2002). This allowed for a simpler design and more power given
+the same sample size. Further, unlike the studies run by Raghubir and
+Srivastava (Raghubir and Srivastava 2002) and Wertenbroch, Soman and
+Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007), I did not
+use a fiat currency or mix of fiat and virtual currencies, but used only
+one virtual currency for both groups. On the one hand, this
+simplification was due to a focus of wether the effects described in
+previous papers also held in similar ways for virtual currencies. On the
+other hand, it also allowed me to preclude any biases or previous
+experience that participants might have had towards or with certain
+currencies. Raghubir and Srivastava (Raghubir and Srivastava 2002)
+acknowledge that ``the face value effect is due to the accessibility and
+perceptual salience of the face value of the foreign currency \ldots{}
+{[}which{]} is likely to depend on the extent to which an individual has
+the opportunity or the time available to process exchange rate
+information and/or has experience in using a particular foreign
+currency''. Further, Alter and Oppenheimer (Alter and Oppenheimer 2008)
+show that people use ``familiarity and fluency'' when valuing goods in
+different currencies. To bias participants the least, I chose the
+relatively nondescript name for a fictional, virtual currency: BlueCoin.
 
@@
 WTP. This is important since if the majority or even the entirety of
-participants were to bid zero on the item, then we would only learn that
+participants were to bid zero on the item, then I would only learn that
 this was the participants' WTP for that good, but not whether there are
 any systematic differences in the WTP when using different currencies.
-Hence, we selected a tabletop airhockey table, something that few enough
-people have so that they won't want another one, but enough people want
-with a non-zero WTP, especially among a student population. In fact,
-only six participants of the experiment stated a WTP of 0.
-
-In designing the main part of the experiment, we chose to conduct an
+Hence, I selected a tabletop airhockey table, something that few enough
+people have so that they would not not want another one, but enough
+people want with a non-zero WTP, especially among a student population.
+This turned out to be a good choice, since only six participants of the
+experiment stated a WTP of 0.
+
+In designing the main part of the experiment, I chose to conduct an
 auction, specifically using the BDM mechanism, in order to have an
@@
 phenomenon that is superior to using participants' stated preferences
-(\textbf{cite?}). As mentioned above, the studies conducted by RAS
-(Raghubir and Srivastava 2002), WER (Wertenbroch, Soman, and
-Chattopadhyay 2007) (with the exception of one permutation of one of the
-studies) and Fang (Fang 2019) did not implement incentive-compatible
-methods of eliciting the participants' preferences, making this
-experiment and important addition to these previous studies in examining
-whether the effects describe still hold when a more accurate way of
-eliciting WTP is used. In order to incentivise the participants even
-further, we ran a lottery that paid out three randomly-chosen
-participants based on their actual choices made in the auction and by
-simulating the BDM mechanism using a random number generator. Due to
-budget constraints, we were only able to play this lottery for three
-people, but given that the sample size of the experiment was relatively
-small, the potential to receive one's outcome is likely to have helped
-in eliciting the participants' true WTP.
-
-Finally, given our budget, we were able to give participants an
-endowment of £50 each, which was around double of what the item costs to
-buy. Assuming that the item is priced roughly around the average WTP
-(which turned out to be correct), this endowment was chosen to leave
-enough room for people with higher WTP to make their bid and for us to
-capture this in the data. This is important for the goals of the
-experiment, since if we had, for example, chosen an endowment of £20,
-the majority of participants might have bid their maximum amount,
-hindering our ability to meaningfully compare WTP across the two groups.
-We chose relatively simple exchange rates of 5 and \(1/5\) so that the
-exchange rate calculations would be relatively easy to make, allowing us
-to be more confident that differences between groups were not due to the
-mental effort required to do calculations but due to something else. RAS
-(Raghubir and Srivastava 2002) acknowledge that ``the reliance on face
-value may be a function of the ease with which the foreign money can be
-converted. \ldots{} Future research should examine the asymmetric and
-nonlinear nature of this effect''. Since the goal of this study is to
-investigate that an effect exists that is not solely based on a high
-difficulty or large mental effort required when doing specific,
-difficult calculations, we aimed to make the calculations as easy as
-possible in order to isolate the effect of the exchange rate and nominal
-value of the foreign currency.
+(\textbf{cite?}). The BDM is essentially a sealed-bid, second price
+auction that is, in its' most common variant, played against a computer
+drawing a bid from a known distribution. If the players' bid is greater
+than or equal to the computers' bid, they win and pay the computers'
+bid, otherwise they lose. As mentioned above, the studies conducted by
+Raghubir and Srivastava (Raghubir and Srivastava 2002), Wertenbroch,
+Soman and Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007)
+(with the exception of one permutation of one of the studies) and Fang
+(Fang 2019) did not implement incentive-compatible methods of eliciting
+the participants' preferences, making this experiment an important
+addition to these previous studies in examining whether the effects
+described still hold when a more truthful way of eliciting WTP is used.
+In order to incentivise the participants to participate, I ran a lottery
+that paid out three randomly-chosen participants based on their actual
+choices made in the auction and by simulating the BDM mechanism using a
+random number generator. Due to budget constraints, I was only able to
+play this lottery for three people, but given that the sample size of
+the experiment was relatively small, the potential to receive one's
+outcome is likely to have helped in eliciting the participants' true
+WTP.
+
+Finally, given the budget, I was able to give participants an endowment
+of £50 each, which was around double of what the item costs to buy.
+Assuming that the item is priced roughly around the average WTP (which
+turned out to be correct), this endowment was chosen to leave enough
+room for people with higher WTP to make their bid and to capture this in
+the data. This is important for the goals of the experiment, since if I
+had, for example, chosen an endowment of £20, the majority of
+participants might have bid their maximum amount, hindering my ability
+to meaningfully compare WTP across the two groups. I chose relatively
+simple exchange rates of 5 and \(1/5\) so that the exchange rate
+calculations would be relatively easy to make, allowing me to be more
+confident that differences between groups were not due to the mental
+effort required to do calculations but due to something else. Raghubir
+and Srivastava (Raghubir and Srivastava 2002) acknowledge that ``the
+reliance on face value may be a function of the ease with which the
+foreign money can be converted. \ldots{} Future research should examine
+the asymmetric and nonlinear nature of this effect''. Since the goal of
+this study is to investigate that an effect exists that is not solely
+based on a high difficulty or large mental effort required when doing
+specific, difficult calculations, I aimed to make the calculations as
+easy as possible in order to isolate the effect of the exchange rate and
+nominal value of the foreign currency. Further, since the study was
+conducted online, participants were easily able to and allowed to use
+calculators for any part.
 
@@
 
-In setting up the experiment, we incorrectly used the BDM mechanism.
+In setting up the experiment, I incorrectly used the BDM mechanism.
 Instead of explaining it as a sealed-bid second-price auction, the
@@
 auction. Unlike in a second-price auction, the participants of a first
-price auction do not have a dominant strategy to bid their true
+price auction do not have a (weakly) dominant strategy to bid their true
 valuations, in fact there generally is no dominant strategy in such an
-auction (\textbf{cite?}). (\textbf{todo?})
+auction (\textbf{cite?}). This is true even in this auction in which
+participants knew that they were bidding against a computer agent who
+would randomly draw a bid from a uniform distribution from 0-50, with an
+expected bid of 25. Indeed, the optimal strategy by participants was to
+choose their bid b by maximising their payoff p:
+
+\[\frac{b}{50} * u(x = 1, 50 - b) + (1 - \frac{b}{50}) * u(x = 0, 50)\]
+
+where u(x, m) is their utility function, x is a binary variable where x
+= 1 signifies owning the good (and vice-versa) and m = 50 is their
+budget (in Pounds). As is obvious, the value of b depends on the
+participants' utility function. Hence, while players in this auction
+need not necessarily have the optimal strategy of telling their true
+valuation, sufficient randomisation should ensure that the utility
+functions of agents in each group should be evenly distributed. This
+would entail that we can nonetheless compare bids across both groups.
 
@@
 and vice versa. To conduct the analysis, we first need to find the
-effect size, or Cohen's D and then implement the power analysis.
+effect size, or Cohen's D, and then implement the power analysis.
 Further, I will also conduct an analysis that investigates how big the
-sample size should have been to get a power of 80\%.
+sample size should have been to get a power of 80\%, which is a
+generally accepted threshold for significant power.
 
@@
 at any lower ones, it is likely that this correlation is due to the low
-sample size rather than representing a true correlation between these
+sample size rather than it representing a true correlation between these
 variables.
@@
 difference occurs due to a systematic difference in how each group
-calculated their value in the foreign currency BlueCoin. The only
-difference between the groups was the exchange rate of BlueCoin to the
-Pound and, as a result, the nominal values of the budget and the bids.
-This would suggest that this difference in bids occurs based on whether
-the foreign currency is a fraction or multiple of the home currency.
+calculated their value in the foreign currency BlueCoin rather than
+random chance. The only difference between the groups was the exchange
+rate of BlueCoin to the Pound and, as a result, the numerousity of the
+nominal values of the budget and the bids. This would suggest that this
+difference in bids occurs based on whether the foreign currency is a
+fraction or multiple of the home currency.
 
@@
 standard model would have predicted that both groups would on average
-bid the same, the model proposed by RAS would have predicted that the
-fraction group would on average bid more than the multiple group and the
-model proposed by WER would have predicted the opposite, namely that the
+bid the same, the model proposed by Raghubir and Srivastava (Raghubir
+and Srivastava 2002) would have predicted that the fraction group would
+on average bid more than the multiple group and the model proposed by
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) would have predicted the opposite, namely that the
 fraction group would on average bid less than the multiple group. Hence,
@@
 
-WER (Wertenbroch, Soman, and Chattopadhyay 2007) argue that this
-systematic difference in valuations and spending behaviour occurs
-because consumers are biased by the nominal difference between their
-budget and the product valuation in the foreign currency and thus anchor
-on this value when converting amounts between their home currency and
-foreign currency. In the context of the study, this would entail that
-the fraction group calculated the difference between their budget and
-their bid in BlueCoin and adjusted their bid downwards based on it,
-since this difference will be small (\textless{} 10) in nominal terms.
-The multiple group, on the other hand, would have calculated this
-difference and received a larger amount of surplus for the same product
-valuation in real terms (25 times as large as the fraction group).
-Hence, the multiple group would have adjusted their bid upwards, leading
-to a higher average bid in real (and nominal) terms.
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) argue that this systematic difference in valuations
+and spending behaviour occurs because consumers are biased by the
+nominal difference between their budget and the product valuation in the
+foreign currency and thus anchor on this value when converting amounts
+between their home currency and foreign currency. In the context of the
+study, this would entail that the fraction group calculated the
+difference between their budget and their bid in BlueCoin and adjusted
+their bid downwards based on it, since this difference will be small
+(\textless{} 10) in nominal terms. The multiple group, on the other
+hand, would have calculated this difference and received a larger amount
+of surplus for the same product valuation in real terms (25 times as
+large as the fraction group). Hence, the multiple group would have
+adjusted their bid upwards, leading to a higher average bid in real (and
+nominal) terms.
 
@@
 valuations across groups that use either a fraction or multiple
-currency. Indeed, it would predict the exact same result and is this
-consistent with the model proposed by WER, even though it differs in
-explaining the internal work that individuals would do to come to that
-conclusion.
+currency. Indeed, it would predict the exact same result and is thus
+consistent with the model proposed by Wertenbroch, Soman and
+Chattopadhyay, even though it differs in explaining the internal work
+that individuals would do to come to that conclusion.
 
@@
 fail to accurately convert this value into the foreign currency.
-However, this explanation is unlikely for several reasons. First, this
-claim assumes that a significant amount of people are significantly
-worse at performing one of the operations across all numbers. From
-experience, it seems that when considering most numbers, one of these
-operations is more difficult to do but it is not always the same one.
-Secondly, this assumes that people are unaware enough of their
-difficulties (even when they are very significant) that they do not use
-a calculator even when one is easily accessible, such as when completing
-the survey for this study online. For these reasons, this explanation
-seems unlikely to be accurate.
+However, this explanation is unlikely for several reasons. First, it
+assumes that a significant amount of people are significantly worse at
+performing one of the operations across all numbers. From experience, it
+seems that when considering most numbers, one of these operations is
+more difficult to do but it is not always the same one. Secondly, this
+assumes that people are unaware enough of their difficulties (even when
+they are very significant) that they do not use a calculator even when
+one is easily accessible, such as when completing the survey for this
+study online. For these reasons, this explanation seems unlikely to be
+accurate.
 
 A third contending explanation could be that individuals simply prefer
-whole numbers over fractions or decimals, leading consumers to make less
-granular valuation choices when considering a currency with a low face
-value. Because of this, there can be differences in groups of
-individuals if, for example, many participants choose to round down. For
-example, it could have been the case that the average valuation of the
-good in the fraction group was 24 but if a significant amount of
-participants rounded this down to the nearest whole number in BlueCoin
-(4), then this average valuation would now be 20. This explanation can
-be supported empirically, given that only 3 bids out of 41 were decimal
-numbers. One might also claim that this behaviour of preferring whole
-numbers is rational, given that it requires less mental effort,
-especially when multiplying and dividing these numbers. Further research
-is required to determine whether this hypothesis could explain the
-observed behaviour, either entirely or in conjunction with one of the
-models proposed above.
+to use whole numbers over fractions or decimals, leading consumers to
+make less granular valuation choices when considering a currency with a
+low face value. Because of this, there can be differences in groups of
+individuals if, for example, many participants in the same group choose
+to round down. For example, it could have been the case that the average
+valuation of the good in the fraction group was £24 but if a significant
+amount of participants rounded this down to the nearest whole number in
+BlueCoin (4), then this average valuation would now be 20. This
+explanation can be supported empirically, given that only 3 bids out of
+41 were decimal numbers. One might also claim that this behaviour of
+preferring whole numbers is rational, given that it requires less mental
+effort, especially when multiplying and dividing these numbers. Further
+research is required to determine whether this hypothesis could explain
+the observed behaviour, either entirely or in conjunction with one of
+the models proposed above.
 
 The former two of these alternative explanations seem unlikely, but the
-latter seems like it could be accurate at least to some extent.
-Nonetheless, it seems like the model proposed by WER is the most
-accurate in predicting and explaining the perceived behaviour when
-formulating valuations of goods in different foreign currencies.
+latter seems like it could be accurate at least to some extent. Without
+further research, however, it seems like the model proposed by
+Wertenbroch, Soman and Chattopadhyay is the most accurate in predicting
+and explaining the perceived behaviour when formulating valuations of
+goods in different foreign currencies.
 
@@
 the power of the t-test for a difference in means is only 22\%. Hence,
-even though the observations line up with the model proposed by WER, it
-could be the case that this result is due to random chance. In repeating
-this study, it would be useful to get a sample size of at least 200
-participants to roughly achieve a power of 80\% and likely also
-statistical significance in conducting the t-test. The second major
-limitation is that the BDM mechanism was implemented incorrectly,
-entailing that the dominant strategy for participants was not to reveal
-their true valuations on the good. In a redo, this mistake could be
-fixed relatively easily by adjusting the experiment instructions.
+even though the observations line up with the model proposed by
+Wertenbroch, Soman and Chattopadhyay, it could be the case that this
+result is due to random chance. In repeating this study, it would be
+useful to get a sample size of at least 200 participants to roughly
+achieve a power of 80\% and likely also statistical significance in
+conducting the t-test. The second major limitation is that the BDM
+mechanism was implemented incorrectly, entailing that there was no
+dominant strategy for participants to reveal their true valuations on
+the good. In a redo, this mistake could be fixed relatively easily by
+adjusting the experiment instructions.
 
 Apart from the limitations, the major theoretical implication of this
-paper is the finding that the model proposed by WER (Wertenbroch, Soman,
-and Chattopadhyay 2007) seems to be most accurate in predicting and
-explaining consumer behaviour when eliciting a WTP on a good. In line
-with these authors, this conclusion contradicts the findings of the
-``face value effect'' by RAS (Raghubir and Srivastava 2002) and
-subsequently by Fang (Fang 2019). Further, this conclusion implies that,
-contrary to traditional consumption theory, individuals formulate their
-WTP in relation to the difference between their budget and the valuation
-of a good rather than its' ratio.
+paper is the finding that the model proposed by Wertenbroch, Soman and
+Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007) seems to be
+most accurate in predicting and explaining consumer behaviour when
+eliciting a WTP on a good in a foreign currncy. In line with these
+authors, this conclusion contradicts the findings of the ``face value
+effect'' by Raghubir and Srivastava (Raghubir and Srivastava 2002) and
+subsequently by Fang (Fang 2019). Further, this conclusion also implies
+that, contrary to traditional consumption theory, individuals formulate
+their WTP in relation to the difference between their budget and the
+valuation of a good rather than its' ratio.
 
@@
 process that leads individuals to systematically under- or overspend
-when using foreign currencies.
+when using foreign currencies. It might, however, be difficult to
+conduct an adequate study to accurately test that claim.
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-Alter2008}
+Alter, Adam L., and Daniel M. Oppenheimer. 2008. {`Easy on the Mind,
+Easy on the Wallet: The Roles of Familiarity and Processing Fluency in
+Valuation Judgments'}. \emph{Psychonomic Bulletin {\&} Review} 15 (5):
+985--90. \url{https://doi.org/10.3758/PBR.15.5.985}.
+
 \bibitem[\citeproctext]{ref-Fang2019}
@@
 
-The full experiment instructions can be found as screenshots at
-\url{https://github.com/kopy-kat/virtual-currencies-paper/tree/main/experiment_instructions}.
+\begin{figure}[H]
+
+{\centering \includegraphics{experiment_instructions/consent.png}
+
+}
+
+\caption{Consent}
+
+\end{figure}%%
+\begin{figure}[H]
+
+{\centering \includegraphics{experiment_instructions/instructions.png}
+
+}
+
+\caption{Instructions}
+
+\end{figure}%%
+\begin{figure}[H]
+
+{\centering \includegraphics{experiment_instructions/auction_fraction.png}
+
+}
+
+\caption{Auction: Fraction Group}
+
+\end{figure}%%
+\begin{figure}[H]
+
+{\centering \includegraphics{experiment_instructions/auction_multiple.png}
+
+}
+
+\caption{Auction: Multiple Group}
+
+\end{figure}%%
+\begin{figure}[H]
+
+{\centering \includegraphics{experiment_instructions/follow_up.png}
+
+}
+
+\caption{Follow up}
+
+\end{figure}%
 
@@
 
-The full source code of the paper and the data analysis can be found at
-\url{https://github.com/kopy-kat/virtual-currencies-paper}.
+The full source code of data analysis is follows:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# Load the required libraries}
+\FunctionTok{library}\NormalTok{(pwr)}
+\FunctionTok{library}\NormalTok{(lsr)}
+
+\CommentTok{\# Load the experiment data}
+\NormalTok{experiment\_data }\OtherTok{\textless{}{-}}
+  \FunctionTok{read.csv}\NormalTok{(}\StringTok{"virtual{-}currencies{-}paper/data/experiment\_data\_formatted.csv"}\NormalTok{)}
+
+\CommentTok{\# Summary statistics for the bid columns}
+\FunctionTok{summary}\NormalTok{(experiment\_data}\SpecialCharTok{$}\NormalTok{group\_fraction\_bid\_in\_pounds)}
+\FunctionTok{sd}\NormalTok{(experiment\_data}\SpecialCharTok{$}\NormalTok{group\_fraction\_bid\_in\_pounds, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
+
+\FunctionTok{summary}\NormalTok{(experiment\_data}\SpecialCharTok{$}\NormalTok{group\_multiple\_bid\_in\_pounds)}
+\FunctionTok{sd}\NormalTok{(experiment\_data}\SpecialCharTok{$}\NormalTok{group\_multiple\_bid\_in\_pounds, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
+
+\CommentTok{\# Plot a boxplot for the bid columns}
+\FunctionTok{boxplot}\NormalTok{(}
+\NormalTok{  experiment\_data}\SpecialCharTok{$}\NormalTok{group\_fraction\_bid\_in\_pounds,}
+\NormalTok{  experiment\_data}\SpecialCharTok{$}\NormalTok{group\_multiple\_bid\_in\_pounds,}
+  \AttributeTok{main =} \StringTok{"Boxplot of fraction and multiple group bids (in Pounds)"}\NormalTok{,}
+  \AttributeTok{names =} \FunctionTok{c}\NormalTok{(}\StringTok{"Group Fraction"}\NormalTok{, }\StringTok{"Group Multiple"}\NormalTok{),}
+  \AttributeTok{xlab =} \StringTok{"Variables"}\NormalTok{,}
+  \AttributeTok{ylab =} \StringTok{"Values"}
+\NormalTok{)}
+
+\CommentTok{\# Perform a t{-}test to compare the means of the two groups}
+\FunctionTok{t.test}\NormalTok{(}
+\NormalTok{  experiment\_data}\SpecialCharTok{$}\NormalTok{group\_fraction\_bid\_in\_pounds,}
+\NormalTok{  experiment\_data}\SpecialCharTok{$}\NormalTok{group\_multiple\_bid\_in\_pounds}
+\NormalTok{)}
+
+\CommentTok{\# Conduct a regression analysis to examine the relationship between}
+\CommentTok{\# the bid amounts and the demographic variables}
+\NormalTok{model\_group\_fraction }\OtherTok{\textless{}{-}}
+  \FunctionTok{lm}\NormalTok{(}
+\NormalTok{    group\_fraction\_bid\_in\_pounds }\SpecialCharTok{\textasciitilde{}}\NormalTok{ lived\_abroad }\SpecialCharTok{+}
+\NormalTok{      travel\_frequency }\SpecialCharTok{+}\NormalTok{ expenditure,}
+    \AttributeTok{data =}\NormalTok{ experiment\_data}
+\NormalTok{  )}
+\FunctionTok{summary}\NormalTok{(model\_group\_fraction)}
+
+\NormalTok{model\_group\_multiple }\OtherTok{\textless{}{-}}
+  \FunctionTok{lm}\NormalTok{(}
+\NormalTok{    group\_multiple\_bid\_in\_pounds }\SpecialCharTok{\textasciitilde{}}\NormalTok{ lived\_abroad }\SpecialCharTok{+}
+\NormalTok{      travel\_frequency }\SpecialCharTok{+}\NormalTok{ expenditure,}
+    \AttributeTok{data =}\NormalTok{ experiment\_data}
+\NormalTok{  )}
+\FunctionTok{summary}\NormalTok{(model\_group\_multiple)}
+
+\CommentTok{\# Calculate the effect size (Cohens D)}
+\NormalTok{effect\_size }\OtherTok{\textless{}{-}} \FunctionTok{cohensD}\NormalTok{(}
+\NormalTok{  experiment\_data}\SpecialCharTok{$}\NormalTok{group\_fraction\_bid\_in\_pounds,}
+\NormalTok{  experiment\_data}\SpecialCharTok{$}\NormalTok{group\_multiple\_bid\_in\_pounds}
+\NormalTok{)}
+
+\CommentTok{\# Find the power of the t test conducted above}
+\FunctionTok{pwr.t2n.test}\NormalTok{(}\AttributeTok{n1 =} \DecValTok{21}\NormalTok{, }\AttributeTok{n2 =} \DecValTok{20}\NormalTok{, }\AttributeTok{d =}\NormalTok{ effect\_size, }\AttributeTok{sig.level =} \FloatTok{0.05}\NormalTok{)}
+
+\CommentTok{\# Find the sample size required to achieve a power of 0.8 (80\%)}
+\FunctionTok{pwr.t.test}\NormalTok{(}\AttributeTok{power =} \FloatTok{0.8}\NormalTok{, }\AttributeTok{d =}\NormalTok{ effect\_size, }\AttributeTok{sig.level =} \FloatTok{0.05}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 

### 2024-04-17 paper.qmd
final draft

@@
 Experience suggests that we treat foreign currencies differently to our home currency and have difficulty adjusting to them.
-Previous research, such as the "money illusion" effect [@cite] suggests that individuals are biased towards the nominal (or face value) of prices.
+Previous research, such as the "money illusion" effect [@Shafir1997] suggests that individuals are biased towards the nominal (or face value) of prices.
 This bias has also been explored in the context foreign currencies, with research finding systematic effects that arise based on the numerousity of values in a foreign currency compared to individuals' home currencies.
@@
 Second, previous research has only assigned minor significance to using incentive-compatible mechanisms to elicit true preferences of participants.
-These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@cite].
-Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).[^ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] Raghubir and Srivastava [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
+These mechanisms have been established to elicit more accurate responses from participants that are closer to their true preferences [@Burchardi2021].
+Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to elicit participants' willingness to pay (WTP).^[ The BDM mechanism will be defined and explained in more detail in the Methodology section below.] Raghubir and Srivastava [@Raghubir2002] expressed the concern that "despite attempts to make the tasks as realistic as possible, the studies reported were laboratory experiments, and issues of generalizability when real money is on the line do arise.
 For instance, when people actually exchange foreign currency they may feel richer or poorer depending on the exchange rate, and the differences in perceptions of wealth may affect product valuation".
@@
 
-Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@cite].
+Standard consumer choice theory suggests that individuals formulate valuations of goods in relation to reference points, such as their budget [@Deaton1980].
 Specifically, standard theory poses that consumers evaluate their valuation for a good as a ratio to their budget in order to determine what proportion of their spending power is required to purchase the good.
@@
 In designing the main part of the experiment, I chose to conduct an auction, specifically using the BDM mechanism, in order to have an incentive-compatible method of eliciting the participants' WTP.
-The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@cite].
+The BDM's incentive compatibility in eliciting WTP is a well-established phenomenon that is superior to using participants' stated preferences [@Burchardi2021].
 The BDM is essentially a sealed-bid, second price auction that is, in its' most common variant, played against a computer drawing a bid from a known distribution.
@@
 Instead of explaining it as a sealed-bid second-price auction, the experiment instructions explained it as a sealed-bid first-price auction.
-Unlike in a second-price auction, the participants of a first price auction do not have a (weakly) dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@cite].
+Unlike in a second-price auction, the participants of a first price auction do not have a (weakly) dominant strategy to bid their true valuations, in fact there generally is no dominant strategy in such an auction [@Noussair2004].
 This is true even in this auction in which participants knew that they were bidding against a computer agent who would randomly draw a bid from a uniform distribution from 0-50, with an expected bid of 25.
@@
 summary(experiment_data$group_fraction_bid_in_pounds)
-sd(experiment_data$group_fraction_bid_in_pounds, na.rm = TRUE)
 
 summary(experiment_data$group_multiple_bid_in_pounds)
-sd(experiment_data$group_multiple_bid_in_pounds, na.rm = TRUE)
 ```
@@
 # Perform a t-test to compare the means of the two groups
-t.test(
+t_test <- t.test(
     experiment_data$group_fraction_bid_in_pounds,
@@
 )
+cat(paste("t =", t_test$statistic, "\n"))
+cat(paste("p-value =", t_test$p.value))
+cat("95 percent confidence interval: \n")
+cat(paste(t_test$conf.int))
 ```
@@
 
-To investigate this further, I have conducted a power analysis in order to determine the power of the t-test, which refers to the likelihood of the test detecting a true positive when an effect actually exists [@cite].
+To investigate this further, I have conducted a power analysis in order to determine the power of the t-test, which refers to the likelihood of the test detecting a true positive when an effect actually exists.
 High power would indicate that this likelihood is high and vice versa.
@@
 Finally, I conducted a regression of the demographic values collected in the fourth part of the experiment on the bids of each group.
-This is done in order to determine whether there is any correlation between the demographic variables and the bid amount, which would suggest that randomisation did not occur correctly, which could have been exacerbated by the small sample size.
-The regression yields the following outcomes:
-
-```{r}
-# Load the experiment data
-experiment_data <-
-    read.csv("data/experiment_data_formatted.csv")
-
-# Conduct a regression analysis to examine the relationship between
-# the bid amounts and the demographic variables
-model_group_fraction <-
-    lm(
-        group_fraction_bid_in_pounds ~ lived_abroad +
-            travel_frequency + expenditure,
-        data = experiment_data
-    )
-summary(model_group_fraction)
-
-model_group_multiple <-
-    lm(
-        group_multiple_bid_in_pounds ~ lived_abroad +
-            travel_frequency + expenditure,
-        data = experiment_data
-    )
-summary(model_group_multiple)
-```
-
-Based on this regression, there are no statistically significant correlations at the 5% significance level or lower.
+This is done in order to determine whether there is any correlation between the demographic variables and the bid amount, which would suggest that randomisation did not occur correctly, which could have been exacerbated by the small sample size.^[ For brevity, the regression output has been moved into the appendix.] Based on this regression, there are no statistically significant correlations at the 5% significance level or lower.
 However, there is one correlation that is significant at the 10% significance level, namely of `expenditure£551-£700` on the multiple group.
@@
 
+## Regression output
+
+```{r}
+# Load the experiment data
+experiment_data <-
+    read.csv("data/experiment_data_formatted.csv")
+
+# Conduct a regression analysis to examine the relationship between
+# the bid amounts and the demographic variables
+model_group_fraction <-
+    lm(
+        group_fraction_bid_in_pounds ~ lived_abroad +
+            travel_frequency + expenditure,
+        data = experiment_data
+    )
+summary(model_group_fraction)
+
+model_group_multiple <-
+    lm(
+        group_multiple_bid_in_pounds ~ lived_abroad +
+            travel_frequency + expenditure,
+        data = experiment_data
+    )
+summary(model_group_multiple)
+```
+
 ## Experiment Instructions
 
-![Consent](experiment_instructions/consent.png)
+{{< pagebreak >}}
 

### 2024-04-17 paper.tex
final draft

@@
 home currency and have difficulty adjusting to them. Previous research,
-such as the ``money illusion'' effect (\textbf{cite?}) suggests that
-individuals are biased towards the nominal (or face value) of prices.
-This bias has also been explored in the context foreign currencies, with
-research finding systematic effects that arise based on the numerousity
-of values in a foreign currency compared to individuals' home
-currencies. However, previous research is split on how and why this
-effect occurs.
+such as the ``money illusion'' effect (Shafir, Diamond, and Tversky
+1997) suggests that individuals are biased towards the nominal (or face
+value) of prices. This bias has also been explored in the context
+foreign currencies, with research finding systematic effects that arise
+based on the numerousity of values in a foreign currency compared to
+individuals' home currencies. However, previous research is split on how
+and why this effect occurs.
 
@@
 have been established to elicit more accurate responses from
-participants that are closer to their true preferences (\textbf{cite?}).
-Hence, this study will use the Becker-DeGroot-Marshak (BDM) mechanism to
-elicit participants' willingness to pay (WTP).{[}\^{} The BDM mechanism
-will be defined and explained in more detail in the Methodology section
-below.{]} Raghubir and Srivastava (Raghubir and Srivastava 2002)
-expressed the concern that ``despite attempts to make the tasks as
-realistic as possible, the studies reported were laboratory experiments,
-and issues of generalizability when real money is on the line do arise.
-For instance, when people actually exchange foreign currency they may
-feel richer or poorer depending on the exchange rate, and the
-differences in perceptions of wealth may affect product valuation''.
-Similarly, Fang (Fang 2019) noted that implementing the BDM mechanism
-was infeasible for the study he conducted but that future research
-should focus on using something like it to elicit WTP. Finally, this
-paper aims to extend the previous literature on the effects of using
-virtual currencies specifically, due to their increasing rise in
+participants that are closer to their true preferences (Burchardi et al.
+2021). Hence, this study will use the Becker-DeGroot-Marshak (BDM)
+mechanism to elicit participants' willingness to pay (WTP).\footnote{
+  The BDM mechanism will be defined and explained in more detail in the
+  Methodology section below.} Raghubir and Srivastava (Raghubir and
+Srivastava 2002) expressed the concern that ``despite attempts to make
+the tasks as realistic as possible, the studies reported were laboratory
+experiments, and issues of generalizability when real money is on the
+line do arise. For instance, when people actually exchange foreign
+currency they may feel richer or poorer depending on the exchange rate,
+and the differences in perceptions of wealth may affect product
+valuation''. Similarly, Fang (Fang 2019) noted that implementing the BDM
+mechanism was infeasible for the study he conducted but that future
+research should focus on using something like it to elicit WTP. Finally,
+this paper aims to extend the previous literature on the effects of
+using virtual currencies specifically, due to their increasing rise in
 importance when transacting or making purchasing decisions online, and
@@
 valuations of goods in relation to reference points, such as their
-budget (\textbf{cite?}). Specifically, standard theory poses that
-consumers evaluate their valuation for a good as a ratio to their budget
-in order to determine what proportion of their spending power is
+budget (Deaton and Muellbauer 1980). Specifically, standard theory poses
+that consumers evaluate their valuation for a good as a ratio to their
+budget in order to determine what proportion of their spending power is
 required to purchase the good. To formulate valuations of goods in a
@@
 phenomenon that is superior to using participants' stated preferences
-(\textbf{cite?}). The BDM is essentially a sealed-bid, second price
-auction that is, in its' most common variant, played against a computer
-drawing a bid from a known distribution. If the players' bid is greater
-than or equal to the computers' bid, they win and pay the computers'
-bid, otherwise they lose. As mentioned above, the studies conducted by
-Raghubir and Srivastava (Raghubir and Srivastava 2002), Wertenbroch,
-Soman and Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007)
-(with the exception of one permutation of one of the studies) and Fang
-(Fang 2019) did not implement incentive-compatible methods of eliciting
-the participants' preferences, making this experiment an important
-addition to these previous studies in examining whether the effects
-described still hold when a more truthful way of eliciting WTP is used.
-In order to incentivise the participants to participate, I ran a lottery
-that paid out three randomly-chosen participants based on their actual
-choices made in the auction and by simulating the BDM mechanism using a
-random number generator. Due to budget constraints, I was only able to
-play this lottery for three people, but given that the sample size of
-the experiment was relatively small, the potential to receive one's
-outcome is likely to have helped in eliciting the participants' true
-WTP.
+(Burchardi et al. 2021). The BDM is essentially a sealed-bid, second
+price auction that is, in its' most common variant, played against a
+computer drawing a bid from a known distribution. If the players' bid is
+greater than or equal to the computers' bid, they win and pay the
+computers' bid, otherwise they lose. As mentioned above, the studies
+conducted by Raghubir and Srivastava (Raghubir and Srivastava 2002),
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) (with the exception of one permutation of one of the
+studies) and Fang (Fang 2019) did not implement incentive-compatible
+methods of eliciting the participants' preferences, making this
+experiment an important addition to these previous studies in examining
+whether the effects described still hold when a more truthful way of
+eliciting WTP is used. In order to incentivise the participants to
+participate, I ran a lottery that paid out three randomly-chosen
+participants based on their actual choices made in the auction and by
+simulating the BDM mechanism using a random number generator. Due to
+budget constraints, I was only able to play this lottery for three
+people, but given that the sample size of the experiment was relatively
+small, the potential to receive one's outcome is likely to have helped
+in eliciting the participants' true WTP.
 
@@
 valuations, in fact there generally is no dominant strategy in such an
-auction (\textbf{cite?}). This is true even in this auction in which
-participants knew that they were bidding against a computer agent who
-would randomly draw a bid from a uniform distribution from 0-50, with an
-expected bid of 25. Indeed, the optimal strategy by participants was to
-choose their bid b by maximising their payoff p:
+auction (Noussair, Robin, and Ruffieux 2004). This is true even in this
+auction in which participants knew that they were bidding against a
+computer agent who would randomly draw a bid from a uniform distribution
+from 0-50, with an expected bid of 25. Indeed, the optimal strategy by
+participants was to choose their bid b by maximising their payoff p:
 
@@
 \begin{verbatim}
-[1] 15.49001
-\end{verbatim}
-
-\begin{verbatim}
    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.    NA's 
    0.00   16.50   27.50   25.57   35.25   50.00      21 
-\end{verbatim}
-
-\begin{verbatim}
-[1] 14.8083
 \end{verbatim}
@@
 \begin{verbatim}
-
-    Welch Two Sample t-test
-
-data:  experiment_data$group_fraction_bid_in_pounds and experiment_data$group_multiple_bid_in_pounds
-t = -1.2323, df = 38.999, p-value = 0.2252
-alternative hypothesis: true difference in means is not equal to 0
+t = -1.23227791692727 
+\end{verbatim}
+
+\begin{verbatim}
+p-value = 0.225223137738591
+\end{verbatim}
+
+\begin{verbatim}
 95 percent confidence interval: 
- -15.401901   3.740092
-sample estimates:
-mean of x mean of y 
-  19.7381   25.5690 
+\end{verbatim}
+
+\begin{verbatim}
+-15.4019012943159 3.74009177050641
 \end{verbatim}
@@
 to determine the power of the t-test, which refers to the likelihood of
-the test detecting a true positive when an effect actually exists
-(\textbf{cite?}). High power would indicate that this likelihood is high
-and vice versa. To conduct the analysis, we first need to find the
-effect size, or Cohen's D, and then implement the power analysis.
-Further, I will also conduct an analysis that investigates how big the
-sample size should have been to get a power of 80\%, which is a
-generally accepted threshold for significant power.
+the test detecting a true positive when an effect actually exists. High
+power would indicate that this likelihood is high and vice versa. To
+conduct the analysis, we first need to find the effect size, or Cohen's
+D, and then implement the power analysis. Further, I will also conduct
+an analysis that investigates how big the sample size should have been
+to get a power of 80\%, which is a generally accepted threshold for
+significant power.
 
@@
 randomisation did not occur correctly, which could have been exacerbated
-by the small sample size. The regression yields the following outcomes:
+by the small sample size.\footnote{ For brevity, the regression output
+  has been moved into the appendix.} Based on this regression, there are
+no statistically significant correlations at the 5\% significance level
+or lower. However, there is one correlation that is significant at the
+10\% significance level, namely of \texttt{expenditure£551-£700} on the
+multiple group. The coefficient of -43.487 suggests that people whose
+usual expenditure is between £551 and £700 per month bid lower than the
+group overall. However, given that this is only significant at the 10\%
+level and not at any lower ones, it is likely that this correlation is
+due to the low sample size rather than it representing a true
+correlation between these variables.
+
+\chapter{Discussion}\label{discussion}
+
+The study conducted found that the fraction group bid less on average
+than the multiple group. The difference in the means across the two
+groups is around £6, or over 10\% of the budget, signifying that this
+difference occurs due to a systematic difference in how each group
+calculated their value in the foreign currency BlueCoin rather than
+random chance. The only difference between the groups was the exchange
+rate of BlueCoin to the Pound and, as a result, the numerousity of the
+nominal values of the budget and the bids. This would suggest that this
+difference in bids occurs based on whether the foreign currency is a
+fraction or multiple of the home currency.
+
+Above, I outlined the three models for how consumers value goods in a
+foreign currency that have been suggested by previous research. The
+standard model would have predicted that both groups would on average
+bid the same, the model proposed by Raghubir and Srivastava (Raghubir
+and Srivastava 2002) would have predicted that the fraction group would
+on average bid more than the multiple group and the model proposed by
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) would have predicted the opposite, namely that the
+fraction group would on average bid less than the multiple group. Hence,
+the third model would have made the most accurate prediction for the
+study conducted.
+
+Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
+Chattopadhyay 2007) argue that this systematic difference in valuations
+and spending behaviour occurs because consumers are biased by the
+nominal difference between their budget and the product valuation in the
+foreign currency and thus anchor on this value when converting amounts
+between their home currency and foreign currency. In the context of the
+study, this would entail that the fraction group calculated the
+difference between their budget and their bid in BlueCoin and adjusted
+their bid downwards based on it, since this difference will be small
+(\textless{} 10) in nominal terms. The multiple group, on the other
+hand, would have calculated this difference and received a larger amount
+of surplus for the same product valuation in real terms (25 times as
+large as the fraction group). Hence, the multiple group would have
+adjusted their bid upwards, leading to a higher average bid in real (and
+nominal) terms.
+
+However, there might be alternative explanations that would be
+consistent with one or more of the other models outlined above. One
+explanation would be that consumers are biased by only the nominal value
+of their budget in the foreign currency and not by the difference
+between their budget and their valuation of a product in the foreign
+currency. While this alternative hypothesis would be hard to prove, it
+would not change the prediction for how the difference in product
+valuations across groups that use either a fraction or multiple
+currency. Indeed, it would predict the exact same result and is thus
+consistent with the model proposed by Wertenbroch, Soman and
+Chattopadhyay, even though it differs in explaining the internal work
+that individuals would do to come to that conclusion.
+
+Another explanation might be that people are simply worse at dividing
+than multiplying (or the reverse), which could explain the perceived
+differences between the groups. On this explanation, even when consumers
+have the same valuation in real terms, one group will systematically
+fail to accurately convert this value into the foreign currency.
+However, this explanation is unlikely for several reasons. First, it
+assumes that a significant amount of people are significantly worse at
+performing one of the operations across all numbers. From experience, it
+seems that when considering most numbers, one of these operations is
+more difficult to do but it is not always the same one. Secondly, this
+assumes that people are unaware enough of their difficulties (even when
+they are very significant) that they do not use a calculator even when
+one is easily accessible, such as when completing the survey for this
+study online. For these reasons, this explanation seems unlikely to be
+accurate.
+
+A third contending explanation could be that individuals simply prefer
+to use whole numbers over fractions or decimals, leading consumers to
+make less granular valuation choices when considering a currency with a
+low face value. Because of this, there can be differences in groups of
+individuals if, for example, many participants in the same group choose
+to round down. For example, it could have been the case that the average
+valuation of the good in the fraction group was £24 but if a significant
+amount of participants rounded this down to the nearest whole number in
+BlueCoin (4), then this average valuation would now be 20. This
+explanation can be supported empirically, given that only 3 bids out of
+41 were decimal numbers. One might also claim that this behaviour of
+preferring whole numbers is rational, given that it requires less mental
+effort, especially when multiplying and dividing these numbers. Further
+research is required to determine whether this hypothesis could explain
+the observed behaviour, either entirely or in conjunction with one of
+the models proposed above.
+
+The former two of these alternative explanations seem unlikely, but the
+latter seems like it could be accurate at least to some extent. Without
+further research, however, it seems like the model proposed by
+Wertenbroch, Soman and Chattopadhyay is the most accurate in predicting
+and explaining the perceived behaviour when formulating valuations of
+goods in different foreign currencies.
+
+\section{Limitations, Theoretical Implications and Future
+Research}\label{limitations-theoretical-implications-and-future-research}
+
+The main limitation of the study conducted is that due to small sample
+size, the results are not statistically significant at the 5\% level and
+the power of the t-test for a difference in means is only 22\%. Hence,
+even though the observations line up with the model proposed by
+Wertenbroch, Soman and Chattopadhyay, it could be the case that this
+result is due to random chance. In repeating this study, it would be
+useful to get a sample size of at least 200 participants to roughly
+achieve a power of 80\% and likely also statistical significance in
+conducting the t-test. The second major limitation is that the BDM
+mechanism was implemented incorrectly, entailing that there was no
+dominant strategy for participants to reveal their true valuations on
+the good. In a redo, this mistake could be fixed relatively easily by
+adjusting the experiment instructions.
+
+Apart from the limitations, the major theoretical implication of this
+paper is the finding that the model proposed by Wertenbroch, Soman and
+Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007) seems to be
+most accurate in predicting and explaining consumer behaviour when
+eliciting a WTP on a good in a foreign currncy. In line with these
+authors, this conclusion contradicts the findings of the ``face value
+effect'' by Raghubir and Srivastava (Raghubir and Srivastava 2002) and
+subsequently by Fang (Fang 2019). Further, this conclusion also implies
+that, contrary to traditional consumption theory, individuals formulate
+their WTP in relation to the difference between their budget and the
+valuation of a good rather than its' ratio.
+
+Future research could build on this study and its' findings in several
+important ways: first, it would make sense to conduct a similar or
+identical study with the BDM mechanism implemented correctly and a
+greater sample size. This would allow for greater certainty that the
+effect observed is statistically significant and reproducible. Further,
+it would be interesting to investigate the third alternative hypothesis
+formulated above in order to gain a better understanding into the exact
+process that leads individuals to systematically under- or overspend
+when using foreign currencies. It might, however, be difficult to
+conduct an adequate study to accurately test that claim.
+
+\chapter{References}\label{references}
+
+\phantomsection\label{refs}
+\begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-Alter2008}
+Alter, Adam L., and Daniel M. Oppenheimer. 2008. {`Easy on the Mind,
+Easy on the Wallet: The Roles of Familiarity and Processing Fluency in
+Valuation Judgments'}. \emph{Psychonomic Bulletin {\&} Review} 15 (5):
+985--90. \url{https://doi.org/10.3758/PBR.15.5.985}.
+
+\bibitem[\citeproctext]{ref-Burchardi2021}
+Burchardi, Konrad B., Jonathan de Quidt, Selim Gulesci, Benedetta Lerva,
+and Stefano Tripodi. 2021. {`Testing Willingness to Pay Elicitation
+Mechanisms in the Field: Evidence from Uganda'}. \emph{Journal of
+Development Economics} 152: 102701.
+https://doi.org/\url{https://doi.org/10.1016/j.jdeveco.2021.102701}.
+
+\bibitem[\citeproctext]{ref-Deaton1980}
+Deaton, Angus, and John Muellbauer. 1980. \emph{Economics and Consumer
+Behavior}. Cambridge University Press.
+
+\bibitem[\citeproctext]{ref-Fang2019}
+Fang, Justin. 2019. {`In-Game Currency Design and Consumer Spending
+Behavior'}. Bachelor\textquotesingle s Thesis, Ross School of Business,
+University of Michigan.
+\url{https://deepblue.lib.umich.edu/bitstream/handle/2027.42/155343/Justin\%20Fang_BA\%20480\%20Written\%20Report.pdf}.
+
+\bibitem[\citeproctext]{ref-Noussair2004}
+Noussair, Charles, Stephane Robin, and Bernard Ruffieux. 2004.
+{`Revealing Consumers' Willingness-to-Pay: A Comparison of the BDM
+Mechanism and the Vickrey Auction'}. \emph{Journal of Economic
+Psychology} 25 (6): 725--41.
+https://doi.org/\url{https://doi.org/10.1016/j.joep.2003.06.004}.
+
+\bibitem[\citeproctext]{ref-Raghubir2002}
+Raghubir, Priya, and Joydeep Srivastava. 2002. {`{Effect of Face Value
+on Product Valuation in Foreign Currencies}'}. \emph{Journal of Consumer
+Research} 29 (3): 335--47. \url{https://doi.org/10.1086/344430}.
+
+\bibitem[\citeproctext]{ref-Shafir1997}
+Shafir, Eldar, Peter Diamond, and Amos Tversky. 1997. {`Money
+Illusion'}. \emph{The Quarterly Journal of Economics} 112 (2): 341--74.
+\url{http://www.jstor.org/stable/2951239}.
+
+\bibitem[\citeproctext]{ref-Wertenbroch2007}
+Wertenbroch, Klaus, Dilip Soman, and Amitava Chattopadhyay. 2007. {`{On
+the Perceived Value of Money: The Reference Dependence of Currency
+Numerosity Effects}'}. \emph{Journal of Consumer Research} 34 (1):
+1--10. \url{https://doi.org/10.1086/513041}.
+
+\end{CSLReferences}
+
+\chapter{Appendix}\label{appendix}
+
+\section{Regression output}\label{regression-output}
 
@@
 
-Based on this regression, there are no statistically significant
-correlations at the 5\% significance level or lower. However, there is
-one correlation that is significant at the 10\% significance level,
-namely of \texttt{expenditure£551-£700} on the multiple group. The
-coefficient of -43.487 suggests that people whose usual expenditure is
-between £551 and £700 per month bid lower than the group overall.
-However, given that this is only significant at the 10\% level and not
-at any lower ones, it is likely that this correlation is due to the low
-sample size rather than it representing a true correlation between these
-variables.
-
-\chapter{Discussion}\label{discussion}
-
-The study conducted found that the fraction group bid less on average
-than the multiple group. The difference in the means across the two
-groups is around £6, or over 10\% of the budget, signifying that this
-difference occurs due to a systematic difference in how each group
-calculated their value in the foreign currency BlueCoin rather than
-random chance. The only difference between the groups was the exchange
-rate of BlueCoin to the Pound and, as a result, the numerousity of the
-nominal values of the budget and the bids. This would suggest that this
-difference in bids occurs based on whether the foreign currency is a
-fraction or multiple of the home currency.
-
-Above, I outlined the three models for how consumers value goods in a
-foreign currency that have been suggested by previous research. The
-standard model would have predicted that both groups would on average
-bid the same, the model proposed by Raghubir and Srivastava (Raghubir
-and Srivastava 2002) would have predicted that the fraction group would
-on average bid more than the multiple group and the model proposed by
-Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
-Chattopadhyay 2007) would have predicted the opposite, namely that the
-fraction group would on average bid less than the multiple group. Hence,
-the third model would have made the most accurate prediction for the
-study conducted.
-
-Wertenbroch, Soman and Chattopadhyay (Wertenbroch, Soman, and
-Chattopadhyay 2007) argue that this systematic difference in valuations
-and spending behaviour occurs because consumers are biased by the
-nominal difference between their budget and the product valuation in the
-foreign currency and thus anchor on this value when converting amounts
-between their home currency and foreign currency. In the context of the
-study, this would entail that the fraction group calculated the
-difference between their budget and their bid in BlueCoin and adjusted
-their bid downwards based on it, since this difference will be small
-(\textless{} 10) in nominal terms. The multiple group, on the other
-hand, would have calculated this difference and received a larger amount
-of surplus for the same product valuation in real terms (25 times as
-large as the fraction group). Hence, the multiple group would have
-adjusted their bid upwards, leading to a higher average bid in real (and
-nominal) terms.
-
-However, there might be alternative explanations that would be
-consistent with one or more of the other models outlined above. One
-explanation would be that consumers are biased by only the nominal value
-of their budget in the foreign currency and not by the difference
-between their budget and their valuation of a product in the foreign
-currency. While this alternative hypothesis would be hard to prove, it
-would not change the prediction for how the difference in product
-valuations across groups that use either a fraction or multiple
-currency. Indeed, it would predict the exact same result and is thus
-consistent with the model proposed by Wertenbroch, Soman and
-Chattopadhyay, even though it differs in explaining the internal work
-that individuals would do to come to that conclusion.
-
-Another explanation might be that people are simply worse at dividing
-than multiplying (or the reverse), which could explain the perceived
-differences between the groups. On this explanation, even when consumers
-have the same valuation in real terms, one group will systematically
-fail to accurately convert this value into the foreign currency.
-However, this explanation is unlikely for several reasons. First, it
-assumes that a significant amount of people are significantly worse at
-performing one of the operations across all numbers. From experience, it
-seems that when considering most numbers, one of these operations is
-more difficult to do but it is not always the same one. Secondly, this
-assumes that people are unaware enough of their difficulties (even when
-they are very significant) that they do not use a calculator even when
-one is easily accessible, such as when completing the survey for this
-study online. For these reasons, this explanation seems unlikely to be
-accurate.
-
-A third contending explanation could be that individuals simply prefer
-to use whole numbers over fractions or decimals, leading consumers to
-make less granular valuation choices when considering a currency with a
-low face value. Because of this, there can be differences in groups of
-individuals if, for example, many participants in the same group choose
-to round down. For example, it could have been the case that the average
-valuation of the good in the fraction group was £24 but if a significant
-amount of participants rounded this down to the nearest whole number in
-BlueCoin (4), then this average valuation would now be 20. This
-explanation can be supported empirically, given that only 3 bids out of
-41 were decimal numbers. One might also claim that this behaviour of
-preferring whole numbers is rational, given that it requires less mental
-effort, especially when multiplying and dividing these numbers. Further
-research is required to determine whether this hypothesis could explain
-the observed behaviour, either entirely or in conjunction with one of
-the models proposed above.
-
-The former two of these alternative explanations seem unlikely, but the
-latter seems like it could be accurate at least to some extent. Without
-further research, however, it seems like the model proposed by
-Wertenbroch, Soman and Chattopadhyay is the most accurate in predicting
-and explaining the perceived behaviour when formulating valuations of
-goods in different foreign currencies.
-
-\section{Limitations, Theoretical Implications and Future
-Research}\label{limitations-theoretical-implications-and-future-research}
-
-The main limitation of the study conducted is that due to small sample
-size, the results are not statistically significant at the 5\% level and
-the power of the t-test for a difference in means is only 22\%. Hence,
-even though the observations line up with the model proposed by
-Wertenbroch, Soman and Chattopadhyay, it could be the case that this
-result is due to random chance. In repeating this study, it would be
-useful to get a sample size of at least 200 participants to roughly
-achieve a power of 80\% and likely also statistical significance in
-conducting the t-test. The second major limitation is that the BDM
-mechanism was implemented incorrectly, entailing that there was no
-dominant strategy for participants to reveal their true valuations on
-the good. In a redo, this mistake could be fixed relatively easily by
-adjusting the experiment instructions.
-
-Apart from the limitations, the major theoretical implication of this
-paper is the finding that the model proposed by Wertenbroch, Soman and
-Chattopadhyay (Wertenbroch, Soman, and Chattopadhyay 2007) seems to be
-most accurate in predicting and explaining consumer behaviour when
-eliciting a WTP on a good in a foreign currncy. In line with these
-authors, this conclusion contradicts the findings of the ``face value
-effect'' by Raghubir and Srivastava (Raghubir and Srivastava 2002) and
-subsequently by Fang (Fang 2019). Further, this conclusion also implies
-that, contrary to traditional consumption theory, individuals formulate
-their WTP in relation to the difference between their budget and the
-valuation of a good rather than its' ratio.
-
-Future research could build on this study and its' findings in several
-important ways: first, it would make sense to conduct a similar or
-identical study with the BDM mechanism implemented correctly and a
-greater sample size. This would allow for greater certainty that the
-effect observed is statistically significant and reproducible. Further,
-it would be interesting to investigate the third alternative hypothesis
-formulated above in order to gain a better understanding into the exact
-process that leads individuals to systematically under- or overspend
-when using foreign currencies. It might, however, be difficult to
-conduct an adequate study to accurately test that claim.
-
-\chapter{References}\label{references}
-
-\phantomsection\label{refs}
-\begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-Alter2008}
-Alter, Adam L., and Daniel M. Oppenheimer. 2008. {`Easy on the Mind,
-Easy on the Wallet: The Roles of Familiarity and Processing Fluency in
-Valuation Judgments'}. \emph{Psychonomic Bulletin {\&} Review} 15 (5):
-985--90. \url{https://doi.org/10.3758/PBR.15.5.985}.
-
-\bibitem[\citeproctext]{ref-Fang2019}
-Fang, Justin. 2019. {`In-Game Currency Design and Consumer Spending
-Behavior'}. Bachelor\textquotesingle s Thesis, Ross School of Business,
-University of Michigan.
-\url{https://deepblue.lib.umich.edu/bitstream/handle/2027.42/155343/Justin\%20Fang_BA\%20480\%20Written\%20Report.pdf}.
-
-\bibitem[\citeproctext]{ref-Raghubir2002}
-Raghubir, Priya, and Joydeep Srivastava. 2002. {`{Effect of Face Value
-on Product Valuation in Foreign Currencies}'}. \emph{Journal of Consumer
-Research} 29 (3): 335--47. \url{https://doi.org/10.1086/344430}.
-
-\bibitem[\citeproctext]{ref-Wertenbroch2007}
-Wertenbroch, Klaus, Dilip Soman, and Amitava Chattopadhyay. 2007. {`{On
-the Perceived Value of Money: The Reference Dependence of Currency
-Numerosity Effects}'}. \emph{Journal of Consumer Research} 34 (1):
-1--10. \url{https://doi.org/10.1086/513041}.
-
-\end{CSLReferences}
-
-\chapter{Appendix}\label{appendix}
-
 \section{Experiment Instructions}\label{experiment-instructions}
 
+\newpage{}
+
 \begin{figure}[H]
 
-{\centering \includegraphics{experiment_instructions/consent.png}
+{\centering \includegraphics{experiment_instructions/instructions.png}
 
@@
 
-\caption{Consent}
+\caption{Instructions}
 
@@
 
-{\centering \includegraphics{experiment_instructions/instructions.png}
+{\centering \includegraphics{experiment_instructions/auction_fraction.png}
 
@@
 
-\caption{Instructions}
+\caption{Auction: Fraction Group}
 
@@
 
-{\centering \includegraphics{experiment_instructions/auction_fraction.png}
+{\centering \includegraphics{experiment_instructions/auction_multiple.png}
 
@@
 
-\caption{Auction: Fraction Group}
+\caption{Auction: Multiple Group}
 
@@
 
-{\centering \includegraphics{experiment_instructions/auction_multiple.png}
+{\centering \includegraphics{experiment_instructions/follow_up.png}
 
@@
 
-\caption{Auction: Multiple Group}
-
-\end{figure}%%
-\begin{figure}[H]
-
-{\centering \includegraphics{experiment_instructions/follow_up.png}
-
-}
-
 \caption{Follow up}
@@
 
-The full source code of data analysis is follows:
+The full source code of the data analysis is follows:
 

### 2024-04-17 paper.qmd
done

@@
 ---
-title: "Effect of the Nominal Value of Foreign Currencies in valuing a good"
+title: "Coinfluence: The Role of Currency Numerosity in Consumer Decision Making"
 date: 2024-04-16
@@
   - name: Konrad Kopp
-    email: konrad.kopp@stcatz.ox.ac.uk
     affiliation: 
@@
 license: "CC0"
-copyright: 
-  holder: Konrad Kopp
-  year: 2024
 keywords:
@@
 Previous research, such as the "money illusion" effect [@Shafir1997] suggests that individuals are biased towards the nominal (or face value) of prices.
-This bias has also been explored in the context foreign currencies, with research finding systematic effects that arise based on the numerousity of values in a foreign currency compared to individuals' home currencies.
+This bias has also been explored in the context foreign currencies, with research finding systematic effects that arise based on the numerosity of values in a foreign currency compared to individuals' home currencies.
 However, previous research is split on how and why this effect occurs.
@@
 Then, I consider what each of these frameworks would predict in a concrete case and show that all three models come to different and mutually exclusive conclusions.
-In order to test which of these frameworks is most accurate in predicting observed behaviour, I conduct a study in which two groups each formulate their WTP for a specific good in an incentive compatible way, with the only difference between the groups being the exchange rate of the currency used to their home currency and, as a result, the numerousity of the values of their budget and bid.
+In order to test which of these frameworks is most accurate in predicting observed behaviour, I conduct a study in which two groups each formulate their WTP for a specific good in an incentive compatible way, with the only difference between the groups being the exchange rate of the currency used to their home currency and, as a result, the numerosity of the values of their budget and bid.
 Analysing the study, I find that consumers tend to underspend when the foreign currency is a fraction and overspend when the foreign currency is a multiple, which is predicted by the model proposed by Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007].
@@
 
-Since the aim of the study was to determine whether there were any systematic differences in WTP between consumers when the only differing factor is the numerousity of the currency used, I decided to not include a control group that bid on the item using Pounds, which was the design of some of the experiments run by Raghubir and Srivastava [@Raghubir2002].
+Since the aim of the study was to determine whether there were any systematic differences in WTP between consumers when the only differing factor is the numerosity of the currency used, I decided to not include a control group that bid on the item using Pounds, which was the design of some of the experiments run by Raghubir and Srivastava [@Raghubir2002].
 This allowed for a simpler design and more power given the same sample size.
@@
 The difference in the means across the two groups is around £6, or over 10% of the budget, signifying that this difference occurs due to a systematic difference in how each group calculated their value in the foreign currency BlueCoin rather than random chance.
-The only difference between the groups was the exchange rate of BlueCoin to the Pound and, as a result, the numerousity of the nominal values of the budget and the bids.
+The only difference between the groups was the exchange rate of BlueCoin to the Pound and, as a result, the numerosity of the nominal values of the budget and the bids.
 This would suggest that this difference in bids occurs based on whether the foreign currency is a fraction or multiple of the home currency.
@@
 
-Apart from the limitations, the major theoretical implication of this paper is the finding that the model proposed by Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] seems to be most accurate in predicting and explaining consumer behaviour when eliciting a WTP on a good in a foreign currncy.
+Apart from the limitations, the major theoretical implication of this paper is the finding that the model proposed by Wertenbroch, Soman and Chattopadhyay [@Wertenbroch2007] seems to be most accurate in predicting and explaining consumer behaviour when eliciting a WTP on a good in a foreign currency.
 In line with these authors, this conclusion contradicts the findings of the "face value effect" by Raghubir and Srivastava [@Raghubir2002] and subsequently by Fang [@Fang2019].

### 2024-04-17 paper.tex
done

@@
 \hypersetup{
-  pdftitle={Effect of the Nominal Value of Foreign Currencies in valuing a good},
-  pdfauthor={Konrad Kopp},
+  pdftitle={Coinfluence: The Role of Currency Numerosity in Consumer Decision Making},
   pdflang={en-GB},
@@
 
-\title{Effect of the Nominal Value of Foreign Currencies in valuing a
-good}
-
-  \author{Konrad Kopp}
+\title{Coinfluence: The Role of Currency Numerosity in Consumer Decision
+Making}
+
+  \author{1054398}
             \affil{%
@@
 foreign currencies, with research finding systematic effects that arise
-based on the numerousity of values in a foreign currency compared to
+based on the numerosity of values in a foreign currency compared to
 individuals' home currencies. However, previous research is split on how
@@
 of the currency used to their home currency and, as a result, the
-numerousity of the values of their budget and bid. Analysing the study,
-I find that consumers tend to underspend when the foreign currency is a
+numerosity of the values of their budget and bid. Analysing the study, I
+find that consumers tend to underspend when the foreign currency is a
 fraction and overspend when the foreign currency is a multiple, which is
@@
 systematic differences in WTP between consumers when the only differing
-factor is the numerousity of the currency used, I decided to not include
+factor is the numerosity of the currency used, I decided to not include
 a control group that bid on the item using Pounds, which was the design
@@
 random chance. The only difference between the groups was the exchange
-rate of BlueCoin to the Pound and, as a result, the numerousity of the
+rate of BlueCoin to the Pound and, as a result, the numerosity of the
 nominal values of the budget and the bids. This would suggest that this
@@
 most accurate in predicting and explaining consumer behaviour when
-eliciting a WTP on a good in a foreign currncy. In line with these
+eliciting a WTP on a good in a foreign currency. In line with these
 authors, this conclusion contradicts the findings of the ``face value

### 2024-12-21 paper.tex
feat: update paper to final version

@@
   pdftitle={Coinfluence: The Role of Currency Numerosity in Consumer Decision Making},
+  pdfauthor={Konrad Kopp},
   pdflang={en-GB},
@@
 
-  \author{1054398}
+  \author{Konrad Kopp}
             \affil{%
